---
title: "Missouri Ice Cream Sales Retailer Test"
output: github_document
---

Load packages. 
```{r}
library(tidyverse)
library(microsynth)
library(lubridate)
```

Load in the data for Missouri Ice Cream category.  
```{r}
load(here::here("..", "mo_ice_cream_clean.RData"))
```

Assign the manfacturer (Private Label, General Mills, Kellogs) for each brand. Convert store code to be a numeric. Organize data by retailer, stores and date, then sum sales across UPCs, giving us weekly sales for each manufacturer in each store in each retailer.
```{r}
mo_data <- mo_data %>%
  filter(manuf_name %in% c("DRE", "HAA", "BEN", "TAL", "BRE", "UNI", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == "DRE", "nestle", 
                        if_else(manuf_name=="HAA", "nestle", 
                        if_else(manuf_name=="BEN", "unilever", 
                        if_else(manuf_name=="TAL", "unilever", 
                        if_else(manuf_name=="BRE", "unilever", 
                        if_else(manuf_name=="UNI", "unilever", "CTL"))))))) %>%
  mutate(store_code_uc=as.numeric(store_code_uc))

mo_data <- mo_data %>% 
  group_by(retailer_code, store_code_uc, actual_manuf, week_end) %>% 
  summarize(sales=sum(sales)) %>%
  arrange(store_code_uc, week_end) 
```

Check store codes to see how many weeks they have. Stores with less than 157 weeks of observations are dropped from the data. Then we arrange by `store_code_uc` and `week_end`, then create a `n_week_end` variable to represent the date numerically. Change manufacter variable to be numeric. 
```{r}
weeks <- unique(mo_data$week_end)

codes <- unique(mo_data$store_code_uc)

drops <- c()

for (i in seq_along(codes)) {
  
  single_store <- mo_data %>% filter(store_code_uc==codes[i])
  
  single_store_vec <- unique(single_store$week_end)
  
  if (length(single_store_vec) < length(weeks)) {
    
    drops <- c(drops, codes[i])
    
  }

}

mo_data <- mo_data %>% 
  filter(!store_code_uc %in% drops) %>% 
  arrange(retailer_code, store_code_uc, week_end) %>%
  mutate(n_week_end=as.numeric(week_end))

mo_data <- mo_data %>% 
  mutate(manuf=if_else(actual_manuf=="CTL", 1, 
               if_else(actual_manuf=="unilever", 2, 3)))
```

Aggregate sales across stores. Check for retailers that only have one store, as this produces as error in Microsynth.  
```{r, message=FALSE, warning=FALSE}
mo_store_data <- mo_data %>% group_by(retailer_code, store_code_uc, n_week_end) %>% summarise(sales=sum(sales))

retailers <- unique(mo_store_data$retailer_code)
small_rets <- c()
n_stores <- c()

for (i in seq_along(retailers)) {
  
  single_retailer <- mo_store_data %>%
    filter(retailer_code == retailers[i])
  
  n_stores <- c(n_stores, length(unique(single_retailer$store_code_uc)))
    
}

(num_stores <- tibble(
  Number_Stores = n_stores,
  Retailer = retailers
))
```

Create `ret_code_combo` that pairs each retailer with each other retailer, giving each the possibility to be the treated retailer code. Use `mo_store_data` which is aggregated across stores. Empty the the results, pvals, and effects. 
```{r}
ret_codes <- unique(mo_store_data$retailer_code)

ret_code_combo <- as_tibble(expand.grid(treat=ret_codes, control=ret_codes)) %>% filter(treat!=control)
```

Create a loop that runs microsynth for each retailer combination by row from `ret_code_combo`. Collect p-values and treatment effects for each store in each retailer combination. 
```{r, message=FALSE, warning=FALSE}
msynth_results <- tibble()
loop_results <- tibble()

for (i in 1:nrow(ret_code_combo)) {
  msynth_pvals <- c()
  msynth_effects <- c()
  loop_rets <- ret_code_combo %>% filter(row_number()==i) %>% as_vector()
  t_stores <- mo_store_data %>% filter(retailer_code==unname(loop_rets[1])) 
  c_stores <- mo_store_data %>% filter(retailer_code==unname(loop_rets[2])) %>% mutate(type=0) 
  t_store_codes <- unique(t_stores$store_code_uc)
  for (j in seq_along(t_store_codes)) {
    store <- t_stores %>% filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = 1)
    store_data <- bind_rows(store, c_stores)
         msynth <- microsynth(data = as.data.frame(store_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15430, 
                           end.post = 16067,
                           match.out = "sales",
                           match.out.min = "sales",
                           result.var="sales", 
                           omnibus.var="sales", 
                           test="twosided", 
                           use.survey = FALSE,
                           use.backup = TRUE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = paste0(unname(loop_rets[1]), ",", unname(loop_rets[2]))
  )
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plot the treatment effects for synthetic controls created from every combination of retailers, but only plot the treatment effects that are statistically significant.
```{r fig.width=9, fig.height=7}
msynth_results %>%
  filter(pval < 0.05) %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) +
  labs(x = 'Effect',
       y = 'Count',
       title = 'Treatment Effects for Retailer Combinations at Store Level: MO Ice Cream',
       subtitle = 'Statistically Significant Effects')
```

Based on this analysis the treated retailer in Missouri seems to be 62. 
