---
title: "Bayesian Synthetic Control Method with a Horseshoe Prior"
author: "Morgan Bale"
output: 
  github_document:
    toc: true
---

The purpose of this file to simulate data and replicate a Bayesian synthetic control method that we might use. The model comes from the web index of the Gupta paper, part B.1 BSCM-Horseshoe. We explore two parameterizations: (1) a centered parameterization from the paper, and (2) a non-centered parameterization from their web appendix code. The non-centered parameterization works better for this model. 

```{r opts, echo=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(gtools)

rstan_options(auto_write=TRUE) # writes a compiled Stan program to the disk to avoid recompiling
options(mc.cores = parallel::detectCores()) # uses multiple cores for stan

knitr::opts_chunk$set(
  fig.path = "../Figures/bscm/"
)
```

# Data

Function for making synthetic data.

```{r}
gen_b1_data <- function(N_train=40,     #num of obs in pre treatment
                        N_test=40,      #num of obs in post treatment 
                        p=5,            #num of control units
                        tau=0.01,        #global shrinkage 
                        mu=c(15, 35, 10, 20, 30)
                        ) {
  
  # data for control units
  X_train <- matrix(NA, nrow = N_train, ncol = p)
  
  X_test <- matrix(NA, nrow=N_test, ncol=p)            #control unit matrix in post treatment 
  
  for(j in 1:p) {
    X_train[,j] <- rnorm(N_train, mean=mu[j], sd=10)     #control unit matrix in pre treatment
    X_test[, j] <- rnorm(N_test, mean=mu[j], sd=10)
  }
  
  beta <- c(.2, .8, 0, 0, 0) 
  
  #model 
  epsilon <- rnorm(N_train, mean=0, sd=1)
  y_train <- X_train%*%beta + epsilon

  #make a list for stan
  list(N_train=N_train, N_test=N_test, p=p, tau=tau, X_train=X_train, X_test=X_test, beta=beta, y_train=as.vector(y_train))}
```

Now we can simulate data.

```{r}
set.seed(2020)
b1_data <- gen_b1_data()
```

# MODEL: CENTERED PARAMETERIZATION 

Run model using `bcsm_b1_p1.stan`

```{r}
b1_model_p1 <- stan_model(file = here::here("Code", "Model", "bscm_b1_p1.stan"))
print(b1_model_p1)

draws <- sampling(b1_model_p1, data=b1_data, seed=2020, cores=4)

#try adapt delta
#draws <- stan("bscm_b1.stan", data=b1_data, seed=2020, cores=3, control=list(adapt_delta=.9))
```

# RESULTS: CENTERED PARAMETERIZATION 

Check results: this parameterization results in 811 divergent transitions, the traceplots do not converge well. 

```{r horseshoe-recovery-p1}
#traceplots
traceplot(draws, pars="beta")
traceplot(draws, pars="sigma")

mcmc_recover_hist(As.mcmc.list(draws, pars="beta"), true=as.vector(t(b1_data$beta)))
```

Fitted Synthetic Control for pre-treatment.

```{r}
#synthetic control for pre treatment
y_fit <- summary(draws, pars="y_fit")

sc_pre <- tibble(y_fit[[1]][,1])

lower <- y_fit[[1]][,4]
upper <- y_fit[[1]][,8]

sc_pre <- sc_pre %>% bind_cols(lower, upper)

sc_pre <- sc_pre %>% mutate(week=rep(1:b1_data$N_train))

names(sc_pre) <- c("synthetic_control","lower", "upper", "week")

#sc_pre %>% ggplot(aes(x=week, y=synthetic_control))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Pre Treatment") + labs(x="Week", y="Control Observations") 
```

Treated unit in the pre treatment

```{r horseshoe-pre-treatment-p1}
y_train <- b1_data$y_train

sc_data <- sc_pre %>% bind_cols(y_train)

names(sc_data)[5] <- "treatment_group"

#sc_data %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") + 
  #labs(x="Week", y="Pre Treatment Value") + ggtitle("Pre Treatment Synthetic Control (blue) vs Treatment Group (red)") 
```

Predicted Synthetic Control for post treatment

```{r}
y_test <- summary(draws, pars="y_test")

sc_post <- tibble(y_test[[1]][,1])

lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)

sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

names(sc_post) <- c("synthetic_control", "lower", "upper", "week")

#sc_post %>% ggplot(aes(x=week, y=synthetic_control)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Post Treatment") + labs(x="Week", y="Control Value")
#gray is 95% CI 
```

Make treatment data for post period

```{r horseshoe-post-period-p1}
y_post <- y_train + 15
y_post <- y_post[1:b1_data$N_test]

y_post <- as_tibble(y_post) %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

sc_post <- sc_post %>% left_join(y_post, by="week")

names(sc_post)[5] <- "treatment_group"

total_sc_data <- sc_data %>% bind_rows(sc_post)

total_sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (blue) vs Treatment Group (red)") + geom_vline(xintercept=b1_data$N_train) 
```

# MODEL: NON-CENTERED PARAMETERIZATION

Run model using `bcsm_b1_p2.stan`

```{r}
b1_model_p2 <- stan_model(file = here::here("Code", "Model", "bscm_b1_p2.stan"))
print(b1_model_p2)

draws <- sampling(b1_model_p2, data=b1_data, seed=2020, cores=4)

#try adapt delta
#draws <- stan("bscm_b1.stan", data=b1_data, seed=2020, cores=3, control=list(adapt_delta=.9))
```

# RESULTS: NON-CENTERED PARAMETERIZATION 

Check results: this parameterizations results in 100ish divergent transitions, the traceplots converge, and the model recovers our parameters. 

```{r horseshoe-recovery-p2}
#traceplots
traceplot(draws, pars="beta")
traceplot(draws, pars="sigma")
traceplot(draws, pars="lambda")

mcmc_recover_hist(As.mcmc.list(draws, pars="beta"), true=as.vector(t(b1_data$beta)))
```

Fitted Synthetic Control for pre-treatment.

```{r}
#synthetic control for pre treatment
y_fit <- summary(draws, pars="y_fit")

sc_pre <- tibble(y_fit[[1]][,1])

lower <- y_fit[[1]][,4]
upper <- y_fit[[1]][,8]

sc_pre <- sc_pre %>% bind_cols(lower, upper)

sc_pre <- sc_pre %>% mutate(week=rep(1:b1_data$N_train))

names(sc_pre) <- c("synthetic_control","lower", "upper", "week")

#sc_pre %>% ggplot(aes(x=week, y=synthetic_control))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Pre Treatment") + labs(x="Week", y="Control Observations") 
```

Treated unit in the pre treatment

```{r horseshoe-pre-treatment-p2}
y_train <- b1_data$y_train

sc_data <- sc_pre %>% bind_cols(y_train)

names(sc_data)[5] <- "treatment_group"

#sc_data %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") + 
  #labs(x="Week", y="Pre Treatment Value") + ggtitle("Pre Treatment Synthetic Control (blue) vs Treatment Group (red)") 
```

Predicted Synthetic Control for post treatment

```{r}
y_test <- summary(draws, pars="y_test")

sc_post <- tibble(y_test[[1]][,1])

lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)

sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

names(sc_post) <- c("synthetic_control", "lower", "upper", "week")

#sc_post %>% ggplot(aes(x=week, y=synthetic_control)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Post Treatment") + labs(x="Week", y="Control Value")
#gray is 95% CI 
```

Make treatment data for post period

```{r horseshoe-post-period-p2}
y_post <- y_train + 15
y_post <- y_post[1:b1_data$N_test]

y_post <- as_tibble(y_post) %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

sc_post <- sc_post %>% left_join(y_post, by="week")

names(sc_post)[5] <- "treatment_group"

total_sc_data <- sc_data %>% bind_rows(sc_post)

total_sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (blue) vs Treatment Group (red)") + geom_vline(xintercept=b1_data$N_train) 
```

# MN Cereal 

Test parameterization 2 with Minnesota Cereal.
Target reset date: Jan 1st 2012, Data years: 2011-2012, CC: General Mills, Validator: Kellogg, State: MN, Treated Retailer: 221

Load and clean data: there are 57 control stores and 43 treated stores. 
```{r}
load("../Data/mn_cereal_clean.RData")
#select columns we want
mn_cereal <- mn_cereal %>% dplyr::select(store_code_uc, upc, week_end, units, price, year, upc_ver_uc, parent_code, retailer_code, sales, manufacturer, tot_unit_vol)
```

There are 53 weeks in 2011 and 52 weeks in 2012. CC is implemented around Jan 1st, 2012. We will use 2012-01-07 as the first post treatment period. Find distinct weeks and order by date. Make treatment and post variable. 
```{r}
weeks <- mn_cereal %>% dplyr::select(week_end) %>% distinct()

weeks <- weeks[order(as.Date(weeks$week_end, format="%d/%m/%Y")),]

weeks <- weeks %>% mutate(week_num=rep(1:nrow(weeks)))

mn_cereal <- mn_cereal %>% left_join(weeks, by="week_end")

mn_cereal <- mn_cereal %>% mutate(treat=if_else(retailer_code==221, 1, 0))

#separate data out by CC, validator, PL, other and treated versus control 
# cc_treat <- mn_cereal %>% filter(manufacturer=="GM", treat==1)
# cc_control <- mn_cereal %>% filter(manufacturer=="GM", treat==0)
# 
# cc_control_sales <- cc_control %>% group_by(store_code_uc, week_num) %>% summarise(total_sales=sum(sales)) #5985 obs, 105 weeks for each of 57 stores
# 
# #add store numbers
# treat_stores <- unique(cc_treat$store_code_uc)
# cc_treat <- cc_treat %>% mutate(store_num=0)
# k=1
# for(i in treat_stores) {
#   cc_treat <- cc_treat %>% mutate(store_num=if_else(store_code_uc==i, k, store_num))
#   k=k+1
# }
# 
# #aggregate sales to store level instead of UPC level 
# cc_treat_sales <- cc_treat %>% group_by(store_num, week_num) %>% summarise(total_sales=sum(sales)) #4515 obs, 105 weeks for each of 43 stores
# 
# #try sample of treated stores so it will run faster 
# cc_treat_sales <- cc_treat_sales %>% filter(store_num==4)

# pl_treat <- mn_cereal %>% filter(manufacturer=="PL", treat==1)
# pl_control <- mn_cereal %>% filter(manufacturer=="PL", treat==0)
# 
# #aggregate sales to store level instead of UPC level 
# pl_control_sales <- pl_control %>% group_by(store_code_uc, week_num) %>% summarise(total_sales=sum(sales)) #5985 obs, 105 weeks for each of 57 stores
# 
# #add store numbers
# treat_stores <- unique(pl_treat$store_code_uc)
# pl_treat <- pl_treat %>% mutate(store_num=0)
# k=1
# for(i in treat_stores) {
#   pl_treat <- pl_treat %>% mutate(store_num=if_else(store_code_uc==i, k, store_num))
#   k=k+1
# }
# 
# #aggregate sales to store level instead of UPC level 
# pl_treat_sales <- pl_treat %>% group_by(store_num, week_num) %>% summarise(total_sales=sum(sales)) #4515 obs, 105 weeks for each of 43 stores
# 
# #try sample of treated stores so it will run faster 
# pl_treat_sales <- pl_treat_sales %>% filter(store_num==4)

#separate data out by CC, validator, PL, other and treated versus control 
val_treat <- mn_cereal %>% filter(manufacturer=="K", treat==1)
val_control <- mn_cereal %>% filter(manufacturer=="K", treat==0)

#try with highest selling UPC in treated --> 003800000820
#val_treat %>% group_by(upc) %>% summarise(total_ounces=sum(tot_unit_vol)) %>% arrange(desc(total_ounces))

val_control_sales <- val_control %>% group_by(store_code_uc, week_num) %>% summarise(total_ounces=sum(tot_unit_vol)) #5985 obs, 105 weeks for each of 57 stores

#val_control_sales <- val_control %>% filter(upc=="003800000820") %>% group_by(store_code_uc, week_num) %>% summarise(total_ounces=sum(tot_unit_vol))

#add store numbers
treat_stores <- unique(val_treat$store_code_uc)
val_treat <- val_treat %>% mutate(store_num=0)
k=1
for(i in treat_stores) {
  val_treat <- val_treat %>% mutate(store_num=if_else(store_code_uc==i, k, store_num))
  k=k+1
}

#aggregate sales to store level instead of UPC level 
val_treat_sales <- val_treat %>% group_by(store_num, week_num) %>% summarise(total_ounces=sum(tot_unit_vol)) #4515 obs, 105 weeks for each of 43 stores

#val_treat_sales <- val_treat %>% filter(upc=="003800000820") %>% group_by(store_num, week_num) %>% summarise(total_ounces=sum(tot_unit_vol))

#try sample of treated stores so it will run faster 
val_treat_sales <- val_treat_sales %>% filter(store_num==1)
```

Collect data & test with PL first 
```{r}
N_train <- 53
N_test <- nrow(weeks) - N_train
p <- length(unique(val_control_sales$store_code_uc))

#treated unit in the pre treatment
y_train  <- val_treat_sales %>% filter(week_num %in% c(1:N_train)) %>% pull(total_ounces)  

#y_train <- log(y_train)

X <- matrix(NA, nrow=nrow(weeks), ncol=p)
control_stores <- unique(val_control_sales$store_code_uc)
k=1
for(c in control_stores) {
    X[,k] <- val_control_sales %>% filter(store_code_uc==c) %>% pull(total_ounces)
    k=k+1
}

#try log sales
#X=log(X)

X_train <- X[1:N_train,]
X_test <- X[(N_train+1):nrow(weeks),]

b1_data <- list(p=p, N_test=N_test, N_train=N_train, y_train=y_train, X_train=X_train, X_test=X_test) #data list for stan
```

There are many divergent transitions 
```{r, echo=FALSE}
b1_model_p2 <- stan_model(file = here::here("Code", "Model", "bscm_b1_p2.stan"))
print(b1_model_p2)

draws <- sampling(b1_model_p2, data=b1_data, seed=2020, cores=4)
```

Check results
```{r hierarchy-recovery-MN, echo=FALSE, message=FALSE}
#traceplots
traceplot(draws, pars=c("beta[1]", "beta[2]", "beta[3]", "beta[4]", "beta[5]", "beta[6]", "beta[7]", "beta[8]", "beta[9]", "beta[10]")) #length p
traceplot(draws, pars="sigma")
traceplot(draws, pars=c("lambda[1]", "lambda[2]", "lambda[3]", "lambda[4]", "lambda[5]", "lambda[6]", "lambda[7]", "lambda[8]", "lambda[9]", "lambda[10]"))
traceplot(draws, pars="tau")
```

Look at synthetic control vs Y 
```{r intercept-p2-MN-SC}
#pre sc
y_fit <- summary(draws, pars="y_fit")
sc_pre <- tibble(y_fit[[1]][,1])
lower <- y_fit[[1]][,4]
upper <- y_fit[[1]][,8]

sc_pre <- sc_pre %>% bind_cols(lower, upper)

sc_pre <- sc_pre %>% mutate(week=rep(1:b1_data$N_train))
names(sc_pre) <- c("synthetic_control","lower", "upper", "week")

#post sc
y_test <- summary(draws, pars="y_test")
sc_post <- tibble(y_test[[1]][,1])
lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)
sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))
names(sc_post) <- c("synthetic_control", "lower", "upper", "week")

sc_data <- sc_pre %>% bind_rows(sc_post)

y <- val_treat_sales %>% filter(store_num==1)  %>% ungroup() %>% dplyr::select(-store_num)
#y <- pl_treat_sales %>% ungroup() %>% dplyr::select(-store_code_uc)
names(y)[1] <- "week"

sc_data <- sc_data %>% left_join(y, by="week")

#sc_data$total_ounces <- log(sc_data$total_ounces)

sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=total_ounces), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") + labs(x="Week", y="Value") + ggtitle("Synthetic Control (blue) vs Treatment Group (red): Val Store 1") + geom_vline(xintercept=b1_data$N_train) 
```

