---
title: "Bayesian Synthetic Control Method with a Horseshoe Prior and Intercept and Levels"
author: "Morgan Bale"
output: github_document
---

The purpose of this file to use synthetic data to test the bayesian synthetic control model with data at the store, brand, and time level. The model comes from the web index of the Gupta paper, part B.1 BSCM-Horseshoe. This file begins to customize the model to our paper, e.g. changing index and variable names and is built off of the file `02_bscm-intercept`. We use two different versions of the model: (1) centered from their paper, and (2) non-centered from the code in their web appendix. The centered parameterization works best for this model. 

```{r opts, echo=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(gtools)
library(reshape2)

rstan_options(auto_write=TRUE) # writes a compiled Stan program to the disk to avoid recompiling
options(mc.cores = parallel::detectCores()) # uses multiple cores for stan

knitr::opts_chunk$set(
  fig.path = "../Figures/bscm/"
)
```

##### DATA #######

Function for making synthetic data: incorporate brand and store level data across multiple time periods. Assume brands are nested within stores. 

```{r}
gen_b1_data <- function(N_train=40,     #num of obs in pre treatment
                        N_test=40,      #num of obs in post treatment 
                        S=2,            #num of control stores
                        B=3,            #num of brands within each store
                        beta_0=5,       #intercept
                        mu=c(15, 35, 10)  #means for X matrices (brands?)
                        ) {


  X_train <- array(NA, dim=c(B, N_train, S))         #control unit matrix pre treatment 

  X_test <- array(NA, dim=c(B, N_test, S))         #control unit matrix post treatment 
  
  for(b in 1:B) {
    X_train[b,,] <- matrix(rnorm(N_train*S, mean=mu[b], sd=10), nrow=N_train, ncol=S)     #control unit matrix in pre treatment
    X_test[b,,] <- matrix(rnorm(N_test*S, mean=mu[b], sd=10), nrow=N_test, ncol=S)
  }
  
  beta <- matrix(c(-.5, 2, 0, -.5, 2, 0), nrow=S, ncol=B)
  
  X_beta <- array(NA, dim=c(N_train, B))
  
  for(b in 1:B) {
    X_beta[,b] <- beta_0 + X_train[b,,] %*% beta[,b]
  }
  
  epsilon <- matrix(rnorm(N_train*B, mean=0, sd=1), nrow=N_train, ncol=B) 
  y_train <- matrix(NA, nrow=N_train, ncol=B)
  for(b in 1:B) {
    y_train[,b] <- X_beta[,b] + epsilon[,b]
  }
  
  #make a list for stan
  list(N_train=N_train, N_test=N_test, S=S, B=B, beta_0=beta_0, X_train=X_train, X_test=X_test,
       beta=beta, X_beta=X_beta, y_train=y_train, epsilon=epsilon)
}
```

Create synthetic data

```{r}
set.seed(2020)
b1_data <- gen_b1_data()

save(b1_data, file="b1_data.RData")
```

###### MODEL: CENTERED PARAMETERIZATION ########

Run model using `bscm_level1_p1.stan`.

```{r}
b1_model_p1 <- stan_model(file = here::here("Code", "Model", "bscm_level1_p1.stan"))
print(b1_model_p1)

draws <- sampling(b1_model_p1, data=b1_data, seed=2020)
```

###### RESULTS: CENTERED PARAMETERIZATION ######

Check results: there are no divergent transitions, the traceplots converge, and the model recovers our parameters. 

```{r levels-recovery-p1}
#traceplots
traceplot(draws, pars="beta_0")
traceplot(draws, pars="beta") #(S,B)
traceplot(draws, pars="sigma")
traceplot(draws, pars="lambda") #(S,B)
traceplot(draws, pars="tau")

mcmc_recover_hist(As.mcmc.list(draws, pars="beta"), true=as.vector(t(b1_data$beta)))
mcmc_recover_hist(As.mcmc.list(draws, pars="beta_0"), true=as.vector(t(b1_data$beta_0)))
```

Fitted Synthetic Control for pre treatment

```{r}
#synthetic control for pre treatment
y_fit <- summary(draws, pars="y_fit")  #(N_train, B)

sc_pre <- tibble(y_fit[[1]][,1])

lower <- y_fit[[1]][,4]
upper <- y_fit[[1]][,8]

sc_pre <- sc_pre %>% bind_cols(lower, upper)

sc_pre <- sc_pre %>% mutate(week=rep(1:b1_data$N_train, each=b1_data$B), brand=rep(1:b1_data$B, times=b1_data$N_train))

names(sc_pre) <- c("synthetic_control","lower", "upper", "week", "brand")
```

Treated unit in the pre treatment

```{r levels-pre-treatment-p1}
y_train <- b1_data$y_train

y_train <-y_train %>% melt(id.vars=c("V1", "V2", "V3"), value.name="treated")

names(y_train) <- c("week", "brand", "treated")

sc_data <- sc_pre %>% left_join(y_train, by=c("week", "brand"))

#sc_data %>% ggplot(aes(x=week)) + geom_line(aes(y=treated, color=as.factor(brand))) + geom_line(aes(y=synthetic_control, color=as.factor(brand)), linetype="dashed") + scale_color_manual(values=c("navyblue", "darkred", "steelblue")) + 
  #labs(x="Week", y="Pre Treatment Value", color="Brand") + ggtitle("Pre Treatment Synthetic Control (dashed) vs Treatment Group (solid)") 
```

Predicted Synthetic Control for post treatment

```{r}
y_test <- summary(draws, pars="y_test") #(N_test, B)

sc_post <- tibble(y_test[[1]][,1])

lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)

sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test), each=b1_data$B), brand=rep(1:b1_data$B, times=b1_data$N_test))

names(sc_post) <- c("synthetic_control", "lower", "upper", "week", "brand")

save(sc_post, file="sc_post.RData")
```

Make treatment data for post period

```{r levels-post-period-p1}
y_post <- y_train %>% mutate(treated=treated+10, week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test), times=b1_data$B))

sc_post <- sc_post %>% left_join(y_post, by=c("week", "brand"))

total_sc_data <- sc_data %>% bind_rows(sc_post)

total_sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated, color=as.factor(brand))) + geom_line(aes(y=synthetic_control,  color=as.factor(brand)), linetype="dashed") +
  labs(x="Week", y="Value", color="Brand") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid)") + geom_vline(xintercept=b1_data$N_train) + scale_color_manual(values=c("navyblue", "darkred", "steelblue"))
```

Plot by brand to be able to see post period better:

BRAND 1

```{r levels-brand-01-p1}
total_sc_data %>% filter(brand==1) %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated), color="navyblue") + geom_line(aes(y=synthetic_control),color="navyblue", linetype="dashed") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid): Brand 1") + geom_vline(xintercept=b1_data$N_train)
```

BRAND 2

```{r levels-brand-02-p1}
total_sc_data %>% filter(brand==2) %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated), color="darkred") + geom_line(aes(y=synthetic_control),color="darkred", linetype="dashed") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid): Brand 2") + geom_vline(xintercept=b1_data$N_train)
```

BRAND 3

```{r levels-brand-03-p1}
total_sc_data %>% filter(brand==3) %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated), color="steelblue") + geom_line(aes(y=synthetic_control),color="steelblue", linetype="dashed") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid): Brand 3") + geom_vline(xintercept=b1_data$N_train)
```

###### MODEL: NON-CENTERED PARAMETERIZATION ########

Run model using `bscm_level1_p2.stan`.

```{r}
b1_model_p2 <- stan_model(file = here::here("Code", "Model", "bscm_level1_p2.stan"))
print(b1_model_p2)

draws <- sampling(b1_model_p2, data=b1_data, seed=2020, cores=3)
```

###### RESULTS ######

Check results: there are divergent transitions and the traceplots look okay. 

```{r levels-recovery-p2}
#traceplots
traceplot(draws, pars="beta_0")
traceplot(draws, pars="beta") #(S,B)
traceplot(draws, pars="sigma")
traceplot(draws, pars="lambda") #(S,B)
traceplot(draws, pars="tau")

mcmc_recover_hist(As.mcmc.list(draws, pars="beta"), true=as.vector(t(b1_data$beta)))
mcmc_recover_hist(As.mcmc.list(draws, pars="beta_0"), true=as.vector(t(b1_data$beta_0)))
```

Fitted Synthetic Control for pre treatment

```{r}
#synthetic control for pre treatment
y_fit <- summary(draws, pars="y_fit")  #(N_train, B)

sc_pre <- tibble(y_fit[[1]][,1])

lower <- y_fit[[1]][,4]
upper <- y_fit[[1]][,8]

sc_pre <- sc_pre %>% bind_cols(lower, upper)

sc_pre <- sc_pre %>% mutate(week=rep(1:b1_data$N_train, each=b1_data$B), brand=rep(1:b1_data$B, times=b1_data$N_train))

names(sc_pre) <- c("synthetic_control","lower", "upper", "week", "brand")
```

Treated unit in the pre treatment

```{r levels-pre-treatment-p2}
y_train <- b1_data$y_train

y_train <-y_train %>% melt(id.vars=c("V1", "V2", "V3"), value.name="treated")

names(y_train) <- c("week", "brand", "treated")

sc_data <- sc_pre %>% left_join(y_train, by=c("week", "brand"))

#sc_data %>% ggplot(aes(x=week)) + geom_line(aes(y=treated, color=as.factor(brand))) + geom_line(aes(y=synthetic_control, color=as.factor(brand)), linetype="dashed") + scale_color_manual(values=c("navyblue", "darkred", "steelblue")) + 
  #labs(x="Week", y="Pre Treatment Value", color="Brand") + ggtitle("Pre Treatment Synthetic Control (dashed) vs Treatment Group (solid)") 
```

Predicted Synthetic Control for post treatment

```{r}
y_test <- summary(draws, pars="y_test") #(N_test, B)

sc_post <- tibble(y_test[[1]][,1])

lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)

sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test), each=b1_data$B), brand=rep(1:b1_data$B, times=b1_data$N_test))

names(sc_post) <- c("synthetic_control", "lower", "upper", "week", "brand")
```

Make treatment data for post period

```{r levels-post-period-p2}
y_post <- y_train %>% mutate(treated=treated+10, week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test), times=b1_data$B))

sc_post <- sc_post %>% left_join(y_post, by=c("week", "brand"))

total_sc_data <- sc_data %>% bind_rows(sc_post)

total_sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated, color=as.factor(brand))) + geom_line(aes(y=synthetic_control,  color=as.factor(brand)), linetype="dashed") +
  labs(x="Week", y="Value", color="Brand") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid)") + geom_vline(xintercept=b1_data$N_train) + scale_color_manual(values=c("navyblue", "darkred", "steelblue"))
```

Plot by brand to be able to see post period better:

BRAND 1

```{r levels-brand-01-p2}
total_sc_data %>% filter(brand==1) %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated), color="navyblue") + geom_line(aes(y=synthetic_control),color="navyblue", linetype="dashed") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid): Brand 1") + geom_vline(xintercept=b1_data$N_train)
```

BRAND 2

```{r levels-brand-02-p2}
total_sc_data %>% filter(brand==2) %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated), color="darkred") + geom_line(aes(y=synthetic_control),color="darkred", linetype="dashed") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid): Brand 2") + geom_vline(xintercept=b1_data$N_train)
```

BRAND 3

```{r levels-brand-03-p2}
total_sc_data %>% filter(brand==3) %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treated), color="steelblue") + geom_line(aes(y=synthetic_control),color="steelblue", linetype="dashed") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (dashed) vs Treatment Group (solid): Brand 3") + geom_vline(xintercept=b1_data$N_train)
```


