---
title: "Bayesian Synthetic Control Method with a Hierarchical Weights"
author: "Morgan Bale"
date: "2/11/2022"
output: github_document
---

The purpose of this file is to build off of `02_bscm-intercept`, by adding a hierarchy to the Betas. NO HORESHOE PRIOR AS OF 3/11/22 

```{r opts, echo=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(gtools)

rstan_options(auto_write=TRUE) # writes a compiled Stan program to the disk to avoid recompiling
options(mc.cores = parallel::detectCores()-1) # uses multiple cores for stan

knitr::opts_chunk$set(
  fig.path = "../Figures/bscm/"
)
```

##### DATA #######

Make synthetic data: values picked from simulation studies done in Gupta et al.
```{r}
N_train=N_test=80
p=5                     #num control stores
K=3                     #num of store covariates in beta equation 
mu=c(15, 35, 10, 20, 30) #must be same length as p, mean sales for each store

#X_train, X_test, Z and stan will make the rest
X_train <- matrix(NA, nrow = N_train, ncol = p)       #control unit matrix in pre treatment
  
X_test <- matrix(NA, nrow=N_test, ncol=p)            #control unit matrix in post treatment 
  
for(pp in 1:p) {
  X_train[,pp] <- rnorm(N_train, mean=mu[pp], sd=10)     
  X_test[,pp] <- rnorm(N_test, mean=mu[pp], sd=10)
}
  
  
Z <- matrix(rnorm(K*p), nrow=K, ncol=p)

#put in list for stan
sim_values <- list(N_train=N_train, N_test=N_test, p=p, K=K, X_train=X_train, X_test=X_test, Z=Z)
```

Generate data in stan
```{r}
sim_data <- stan(
  file = here::here("Code", "Model", "gen_hierarchy_data.stan"),
  data = sim_values,
  iter = 1,
  chains = 1,
  seed = 2020,
  algorithm = "Fixed_param"
)

#extract values
sim_beta <- extract(sim_data)$beta       #weights for control stores 
sim_theta <- extract(sim_data)$theta     #effect of store covariates on weights (beta)
sim_ytrain <- extract(sim_data)$y_train  #treat unit in per period
sim_beta0 <- extract(sim_data)$beta_0    #intercept in y 
sim_sigma <- extract(sim_data)$sigma
sim_epsilon <- extract(sim_data)$epsilon
sim_ypost <- extract(sim_data)$y_post  #treat unit in post period

#put data in list for stan model 
b1_data <- list(N_train=N_train, N_test=N_test, p=p, K=K, X_train=X_train, X_test=X_test, Z=Z, beta=sim_beta, theta=sim_theta, y_train=as.vector(sim_ytrain), beta_0=sim_beta0, sigma=sim_sigma, epsilon=sim_epsilon, y_post=as.vector(sim_ypost))
```


###### MODEL: CENTERED PARAMETERIZATION ########

Run model using `bcsm_hierarchy.stan`. This model tries to recreate the model according to the syntax in the paper and the commented out code in the web appendix, we add a new hierarchical prior for Beta instead of horseshoe prior currently. No divergent transitions when horseshoe prior is not present. The weights (beta) are no a function of store characteristics (Z). the treatment effect (alpha) is the difference between Y_treat_post - Y_synth_control. 

```{r}
b1_model <- stan_model(file = here::here("Code", "Model", "bscm_hierarchy.stan"))
#print(b1_model)

draws <- sampling(b1_model, data=b1_data, seed=2020, cores=3)
```

###### RESULTS: CENTERED PARAMETERIZATION ######

Check results: the traceplots look good, the sampler recovers the beta and theta parameters. The synthetic control matches the treatment group in the pre period. 

```{r hierarchy-recovery}
#traceplots
traceplot(draws, pars="beta")
traceplot(draws, pars="beta_0")
traceplot(draws, pars="sigma")
traceplot(draws, pars="theta")
traceplot(draws, pars="epsilon")

mcmc_recover_hist(As.mcmc.list(draws, pars="beta"), true=as.vector(t(b1_data$beta)))
mcmc_recover_hist(As.mcmc.list(draws, pars="beta_0"), true=as.vector(t(b1_data$beta_0)))
mcmc_recover_hist(As.mcmc.list(draws, pars="theta"), true=as.vector(t(b1_data$theta)))
```

Fitted Synthetic Control for pre treatment

```{r}
#synthetic control for pre treatment
y_fit <- summary(draws, pars="y_fit")

sc_pre <- tibble(y_fit[[1]][,1])

lower <- y_fit[[1]][,4]
upper <- y_fit[[1]][,8]

sc_pre <- sc_pre %>% bind_cols(lower, upper)

sc_pre <- sc_pre %>% mutate(week=rep(1:b1_data$N_train))

names(sc_pre) <- c("synthetic_control","lower", "upper", "week")

#sc_pre %>% ggplot(aes(x=week, y=synthetic_control))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Pre Treatment") + labs(x="Week", y="Control Observations") 
```

Treated unit in the pre treatment
```{r hierarchy-pre-treatment}
y_train <- b1_data$y_train

sc_data <- sc_pre %>% bind_cols(y_train)

names(sc_data)[5] <- "treatment_group"

#sc_data %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") + 
  #labs(x="Week", y="Pre Treatment Value") + ggtitle("Pre Treatment Synthetic Control (blue) vs Treatment Group (red)") 
```

Predicted Synthetic Control for post treatment
```{r}
y_test <- summary(draws, pars="y_test")

sc_post <- tibble(y_test[[1]][,1])

lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)

sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

names(sc_post) <- c("synthetic_control", "lower", "upper", "week")

#sc_post %>% ggplot(aes(x=week, y=synthetic_control)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Post Treatment") + labs(x="Week", y="Control Value")
#gray is 95% CI 
```

Make treatment data for post period: this code only works if number of post treatment periods=number pre treatment periods
```{r hierarchy-post-period}
y_post <- b1_data$y_post

y_post <- as_tibble(y_post) %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

sc_post <- sc_post %>% left_join(y_post, by="week")

names(sc_post)[5] <- "treatment_group"

total_sc_data <- sc_data %>% bind_rows(sc_post)

total_sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (blue) vs Treatment Group (red)") + geom_vline(xintercept=b1_data$N_train) 
```
Check treatment effect: alpha=Y_post_treat - Y_synth_control 
```{r}
summary(draws, pars="alpha")[1]

alpha_mean <- as_tibble(summary(draws, pars="alpha")[[1]][,1])
alpha_lower <- as_tibble(summary(draws, pars="alpha")[[1]][,4])
alpha_upper <- as_tibble(summary(draws, pars="alpha")[[1]][,8])

alpha <- cbind(alpha_mean, alpha_lower, alpha_upper)
names(alpha) <-c("mean", "lower", "upper")

alpha <- alpha %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

alpha %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=mean), color="darkred") + labs(x="Week", y="Value") + ggtitle("Treatment effect over time: Y_treat_post - Y_synth_control") + geom_hline(yintercept=0)
```


