---
title: "Synthetic Control Model Testing"
author: "Morgan and Cameron Bale"
date: "4/29/2022"
output: github_document
---

The purpose of this file is to test how including the treatment effect (alpha) influences the model

```{r opts, echo=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(gtools)

rstan_options(auto_write=TRUE, disable_march_warning=TRUE) # writes a compiled Stan program to the disk to avoid recompiling
options(mc.cores = parallel::detectCores()-1) # uses multiple cores for stan

knitr::opts_chunk$set(
  fig.path = "../Figures/bscm/"
)
```

##### DATA #######

Make synthetic data: values picked from simulation studies done in Gupta et al.
```{r}
TT=80
S=5                     #num control stores
#K=3                     #num of store covariates in alpha equation 

#X is the sales for the control stores in all time periods
X <- matrix(rnorm(TT*S), nrow = TT, ncol = S)  

D <- rep(0:1, each=TT/2)
  
#Z <- matrix(rnorm(K*p), nrow=K, ncol=p)

#put in list for stan
sim_values <- list(TT=TT, S=S, X=X, D=D)
```

Generate data in stan
```{r}
sim_data <- stan(
  #file = here::here("Code", "Model", "gen_hierarchy_data_test.stan"),
  file="../Code/Model/gen_hierarchy_data_test.stan",
  data = sim_values,
  iter = 1,
  chains = 1,
  seed = 2020,
  algorithm = "Fixed_param"
)

#extract values
sim_beta <- extract(sim_data)$beta       #weights for control stores 
#sim_theta <- extract(sim_data)$theta     #effect of store covariates on alpha
sim_Y <- extract(sim_data)$Y #treat unit in all time periods
sim_beta0 <- extract(sim_data)$beta_0    #intercept in y 
#sim_sigma <- extract(sim_data)$sigma
sim_epsilon <- extract(sim_data)$epsilon
sim_alpha <- extract(sim_data)$alpha  #treatment effect

#put data in list for stan model 
b1_data <- list(TT=TT, S=S, X=X, beta=sim_beta, Y=as.vector(sim_Y), beta_0=sim_beta0, epsilon=sim_epsilon, alpha=sim_alpha, D=D)
```


###### MODEL: CENTERED PARAMETERIZATION ########

Run model using `bcsm_hierarchy.stan`. This model tries to recreate the model according to the syntax in the paper and the commented out code in the web appendix, we add a new hierarchical prior for Beta instead of horseshoe prior currently. No divergent transitions when horseshoe prior is not present. The weights (beta) are no a function of store characteristics (Z). the treatment effect (alpha) is the difference between Y_treat_post - Y_synth_control. 

```{r}
#b1_model <- stan_model(file = here::here("Code", "Model", "bscm_hierarchy.stan"))
b1_model <- stan_model(file="../Code/Model/bscm_hierarchy_testing.stan")
#print(b1_model)

draws <- sampling(b1_model, data=b1_data, seed=2020, cores=3)
```

###### RESULTS: CENTERED PARAMETERIZATION ######

Check results: the traceplots look good, the sampler recovers the beta and theta parameters. The synthetic control matches the treatment group in the pre period. 

```{r hierarchy-recovery}
#traceplots
traceplot(draws, pars="beta")
traceplot(draws, pars="beta_0")
#traceplot(draws, pars="sigma")
#traceplot(draws, pars="theta")
traceplot(draws, pars="epsilon")
traceplot(draws, pars="alpha")

mcmc_recover_hist(As.mcmc.list(draws, pars="beta"), true=as.vector(t(b1_data$beta)))
mcmc_recover_hist(As.mcmc.list(draws, pars="beta_0"), true=as.vector(t(b1_data$beta_0)))
mcmc_recover_hist(As.mcmc.list(draws, pars="alpha"), true=b1_data$alpha)
#mcmc_recover_hist(As.mcmc.list(draws, pars="theta"), true=as.vector(t(b1_data$theta)))
```

Fitted Synthetic Control for pre treatment

```{r}
Y_hat <- summary(draws, pars="Y_hat")
yhat <- tibble(Y_hat[[1]][,1])

lower <- Y_hat[[1]][,4]
upper <- Y_hat[[1]][,8]

yhat <- yhat %>% bind_cols(lower, upper, b1_data$Y)

yhat <- yhat %>% mutate(week=rep(1:b1_data$TT))

names(yhat) <- c("yhat","lower", "upper", "Y", "week")

yhat %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=yhat, color="Predicted Y"), linetype="dashed") +geom_line(aes(y=Y, color="True Y")) + ggtitle("Predicted Y values compared to actual Y values") + labs(x="Week", y="Control Observations") + geom_vline(xintercept=(b1_data$TT)/2) + labs(x="Week", y="Sales") + scale_color_manual("", breaks=c("Predicted Y", "True Y"), values=c("blue", "red"))
```

Treated unit in the pre treatment
```{r hierarchy-pre-treatment}
y_train <- b1_data$y_train

sc_data <- sc_pre %>% bind_cols(y_train)

names(sc_data)[5] <- "treatment_group"

#sc_data %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") + 
  #labs(x="Week", y="Pre Treatment Value") + ggtitle("Pre Treatment Synthetic Control (blue) vs Treatment Group (red)") 
```

Predicted Synthetic Control for post treatment
```{r}
y_test <- summary(draws, pars="y_test")

sc_post <- tibble(y_test[[1]][,1])

lower <- y_test[[1]][,4]
upper <- y_test[[1]][,8]

sc_post <- sc_post %>% bind_cols(lower, upper)

sc_post <- sc_post %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

names(sc_post) <- c("synthetic_control", "lower", "upper", "week")

#sc_post %>% ggplot(aes(x=week, y=synthetic_control)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line() + ggtitle("Synthetic Control in the Post Treatment") + labs(x="Week", y="Control Value")
#gray is 95% CI 
```

Make treatment data for post period: this code only works if number of post treatment periods=number pre treatment periods
```{r hierarchy-post-period}
y_post <- b1_data$y_post

y_post <- as_tibble(y_post) %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

sc_post <- sc_post %>% left_join(y_post, by="week")

names(sc_post)[5] <- "treatment_group"

total_sc_data <- sc_data %>% bind_rows(sc_post)

total_sc_data %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=treatment_group), color="darkred") + geom_line(aes(y=synthetic_control), color="steelblue") +
  labs(x="Week", y="Value") + ggtitle("Synthetic Control (blue) vs Treatment Group (red)") + geom_vline(xintercept=b1_data$N_train) 
```
Check treatment effect: alpha=Y_post_treat - Y_synth_control 
```{r}
summary(draws, pars="alpha")[1]

alpha_mean <- as_tibble(summary(draws, pars="alpha")[[1]][,1])
alpha_lower <- as_tibble(summary(draws, pars="alpha")[[1]][,4])
alpha_upper <- as_tibble(summary(draws, pars="alpha")[[1]][,8])

alpha <- cbind(alpha_mean, alpha_lower, alpha_upper)
names(alpha) <-c("mean", "lower", "upper")

alpha <- alpha %>% mutate(week=rep((b1_data$N_train+1):(b1_data$N_train+b1_data$N_test)))

alpha %>% ggplot(aes(x=week)) + geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=mean), color="darkred") + labs(x="Week", y="Value") + ggtitle("Treatment effect over time: Y_treat_post - Y_synth_control") + geom_hline(yintercept=0)
```


