---
title: "Synthetic Control Model Testing with Cereal (ND)"
author: "Morgan Bale"
date: "5/13/2022"
output: github_document
---

The purpose of this file is to test how our hierarchical model works with real data. The data was cleaned using the cereal cleaning file. We use ND to test the model, since we are most sure which retailer was treated in ND. The data comes from our Google Drive folder "cleaned data sets" and the model description can be found in `05_bscm-hierarchy-testing.Rmd`. 

```{r opts, echo=FALSE, message=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(gtools)

rstan_options(auto_write=TRUE) # writes a compiled Stan program to the disk to avoid recompiling
options(mc.cores = parallel::detectCores()-1) # uses multiple cores for stan

knitr::opts_chunk$set(
  fig.path = "../Figures/bscm/"
)
```

######## NORTH DAKOTA #########
##### DATA #######

Target reset date: Jan 1st 2012, Data years: 2011-2012, CC: General Mills, Validator: Kellogg, State: ND, Treated Retailer: 903

Load and clean data: there are 4 control stores and 5 treated stores. 
```{r}
load("../Data/nd_cereal_clean.RData")
#select columns we want
nd_cereal <- nd_cereal %>% dplyr::select(store_code_uc, upc, week_end, units, price, year, upc_ver_uc, parent_code, retailer_code, sales, manufacturer)
```

Create higher level store characteristics
```{r}
#standardized number of UPCs --> num_UPC/max(num_UPC)
num_upc <- nd_cereal %>% dplyr::select(store_code_uc, upc) %>% distinct() %>% group_by(store_code_uc) %>% summarise(n=n()) %>% mutate(num_upcs=n/max(n)) #some variation, not a ton...

nd_cereal <- nd_cereal %>% left_join(num_upc, by="store_code_uc")

#variation in prices --> max(price) - min(price) for each store 
price_variation <- nd_cereal %>% dplyr::select(store_code_uc, price) %>% distinct() %>% group_by(store_code_uc) %>% summarise(max_price=max(price), min_price=min(price)) %>% mutate(price_diff=max_price-min_price)

nd_cereal <- nd_cereal %>% left_join(price_variation, by="store_code_uc")
```

There are 53 weeks in 2011 and 52 weeks in 2012. CC is implemented around Jan 1st, 2012. We will use 2012-01-07 as the first post treatment period. Find distinct weeks and order by date. Make treatment and post variable. 
```{r}
weeks <- nd_cereal %>% dplyr::select(week_end) %>% distinct()

weeks <- weeks[order(as.Date(weeks$week_end, format="%d/%m/%Y")),]

weeks <- weeks %>% mutate(week_num=rep(1:nrow(weeks)))

nd_cereal <- nd_cereal %>% left_join(weeks, by="week_end")

nd_cereal <- nd_cereal %>% mutate(treat=if_else(retailer_code==903, 1, 0))

#separate data out by CC, validator, PL, other and treated versus control 
cc_treat <- nd_cereal %>% filter(manufacturer=="GM", treat==1)
cc_control <- nd_cereal %>% filter(manufacturer=="GM", treat==0)

pl_treat <- nd_cereal %>% filter(manufacturer=="PL", treat==1)
pl_control <- nd_cereal %>% filter(manufacturer=="PL", treat==0)

#aggregate sales to store level instead of UPC level 
pl_control_sales <- pl_control %>% group_by(store_code_uc, week_num) %>% summarise(total_sales=sum(sales)) #420 obs, 105 weeks for each of 4 stores

#add store numbers
treat_stores <- unique(pl_treat$store_code_uc)
pl_treat <- pl_treat %>% mutate(store_num=if_else(store_code_uc==790659, 1, if_else(store_code_uc==791868, 2,
                                                                        if_else(store_code_uc==7326857, 3, 
                                                                                if_else(store_code_uc==7329996, 4, 5)))))

#aggregate sales to store level instead of UPC level 
pl_treat_sales <- pl_treat %>% group_by(store_num, week_num) %>% summarise(total_sales=sum(sales)) #525 obs, 105 weeks for each of 5 stores
```

Collect data & test with PL first 
```{r}
TT <- nrow(weeks)  #num of time periods in total 
C <- length(unique(pl_control$store_code_uc))  #num of control stores
N <- length(unique(pl_treat$store_code_uc))  #num of treated stores

#X is a TTxC matrix of control store sales 
X <- matrix(NA, nrow=TT, ncol=C)
control_stores <- unique(pl_control_sales$store_code_uc)
k=1
for(c in control_stores) {
    X[,k] <- pl_control_sales %>% filter(store_code_uc==c) %>% pull(total_sales)
    k=k+1
}

#create Y NxTT matrix
Y <- matrix(NA, nrow=N, ncol=TT)
for(n in 1:N) {
  Y[n,] <- pl_treat_sales %>% filter(store_num==n) %>% pull(total_sales)
}

#create Z KxN matrix 
tZ <- pl_treat %>% dplyr::select(store_num, price_diff, num_upcs) %>% distinct() %>% dplyr::select(price_diff, num_upcs) %>% as.matrix()
Z <- t(tZ)
K <- nrow(Z)

#create D a NxTT matrix for which time periods a treated store is treated in
#week 54 starts post period 
D_prep <- pl_treat_sales %>% mutate(post=if_else(week_num %in% c(1:53), 0, 1)) %>% dplyr::select(store_num, post)
D <- matrix(NA, nrow=N, ncol=TT)
for(n in 1:N) {
  D[n,] <- D_prep %>% filter(store_num==n) %>% pull(post)
}

b1_data <- list(TT=TT, C=C, N=N, X=X, K=K, Z=Z, D=D, Y=Y) #data list for stan
```

##### MODEL #####
This model uses a synthetic control combined with heterogeneous treatment effects to estimate sales for treated stores. The model is restricted to meet the synthetic control requirements in the pre period, so that the difference between the synthetic control and actual sales in the post period can be attributed to alpha, our treatment effect. alpha is described by store/category characteristics making theta our effect of those characteristics on the average treatment effect alpha. Note: alpha is an average treatment effect across all post period weeks. Each treated store gets its own weights determined from the same sample of control stores. In this example, we have 5 treated stores and 4 control stores. So each treated store gets its own synthetic control from the 4 control stores. This form of the model would allow us to still use horseshoe priors on beta, but those are not implemented here yet. 
```{r, echo=FALSE}
#b1_model <- stan_model(file = here::here("Code", "Model", "bscm_hierarchy.stan"))
b1_model <- stan_model(file="../Code/Model/bscm_hierarchy_testing.stan")
print(b1_model)

draws <- sampling(b1_model, data=b1_data, seed=2020, cores=3)
```

###### RESULTS ######

Check results: theta is completely informed by the prior, we can see based on the symmetric distribution. Also, when I turned off theta's prior, the traceplots did not converge anymore. 
```{r hierarchy-recovery, echo=FALSE, message=FALSE}
#traceplots
traceplot(draws, pars=c("beta[1,1]", "beta[2,1]", "beta[3,1]", "beta[4,1]", "beta[1,2]", "beta[2,2]", "beta[3,2]", "beta[4,2]")) #N, C
traceplot(draws, pars="beta_0")
traceplot(draws, pars="sigma")
traceplot(draws, pars="theta")
traceplot(draws, pars="epsilon")
traceplot(draws, pars=c("alpha"))

print(draws, pars=c("alpha", "theta"))
```

Synthetic control v Y: compare the synthetic control for selected treated stores to the actual sales (Y) for those treated stores 

The synthetic controls are not matching Y in the pre period so results are unreliable. 
```{r hierarchy-pre-treatment, echo=FALSE, message=FALSE}
#construct the synthetic control 
beta0 <- summary(draws, pars="beta_0")
beta_0 <- tibble(beta0[[1]][,1])

beta_data <- summary(draws, pars="beta")
beta <- as.matrix(beta_data[[1]][,1])
beta_mat <- matrix(beta, nrow=b1_data$N, ncol=b1_data$C, byrow=TRUE)

sc <- matrix(NA, nrow=b1_data$N, ncol=b1_data$TT)
for(n in 1:N) {
  sc[n,] = as.matrix(beta_0)[1,1] + beta_mat[n,]%*%t(as.matrix(X))  
}

sc_data  <- as.data.frame(t(sc))
sc_data <- stack(sc_data)

sc_data  <- sc_data  %>% mutate(week=rep(1:b1_data$TT, times=b1_data$N), treat_store=rep(1:b1_data$N, each=b1_data$TT))

trueY <- t(Y)
trueY <- stack(as.data.frame(trueY)) %>% mutate(treat_store=rep(1:b1_data$N, each=b1_data$TT)) %>% dplyr::select(-ind)

names(trueY) <- c("y", "treat_store")

sc_data <- sc_data %>% bind_cols(trueY$y)

names(sc_data) <- c("synthetic_control", "ind", "week", "treat_store", "y")

#look at plots
I=54
sc_data %>% filter(treat_store==1) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 1 ") + geom_vline(xintercept=I)

sc_data %>% filter(treat_store==2) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 2 ") + geom_vline(xintercept=I)

sc_data %>% filter(treat_store==3) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 3") + geom_vline(xintercept=I)

sc_data %>% filter(treat_store==4) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 4") + geom_vline(xintercept=I)

sc_data %>% filter(treat_store==5) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 5") + geom_vline(xintercept=I)

#sc_data %>% ggplot(aes(x=week)) + geom_line(aes(y=y, col=as.factor(treat_store))) + geom_line(aes(y=synthetic_control, col=as.factor(treat_store)), linetype="dashed") + ggtitle("SC versus actual treated sales") + facet_wrap(~treat_store)
```

####### MINNESOTA #########

##### DATA #######

Target reset date: Jan 1st 2012, Data years: 2011-2012, CC: General Mills, Validator: Kellogg, State: MN, Treated Retailer: 221

Load and clean data: there are 57 control stores and 43 treated stores. 
```{r}
load("../Data/mn_cereal_clean.RData")
#select columns we want
mn_cereal <- mn_cereal %>% dplyr::select(store_code_uc, upc, week_end, units, price, year, upc_ver_uc, parent_code, retailer_code, sales, manufacturer)
```

Create higher level store characteristics
```{r}
#standardized number of UPCs --> num_UPC/max(num_UPC)
num_upc <- mn_cereal %>% dplyr::select(store_code_uc, upc) %>% distinct() %>% group_by(store_code_uc) %>% summarise(n=n()) %>% mutate(num_upcs=n/max(n)) #some variation, not a ton...

mn_cereal <- mn_cereal %>% left_join(num_upc, by="store_code_uc")

#variation in prices --> max(price) - min(price) for each store 
price_variation <- mn_cereal %>% dplyr::select(store_code_uc, price) %>% distinct() %>% group_by(store_code_uc) %>% summarise(max_price=max(price), min_price=min(price)) %>% mutate(price_diff=max_price-min_price)

mn_cereal <- mn_cereal %>% left_join(price_variation, by="store_code_uc")
```

There are 53 weeks in 2011 and 52 weeks in 2012. CC is implemented around Jan 1st, 2012. We will use 2012-01-07 as the first post treatment period. Find distinct weeks and order by date. Make treatment and post variable. 
```{r}
weeks <- mn_cereal %>% dplyr::select(week_end) %>% distinct()

weeks <- weeks[order(as.Date(weeks$week_end, format="%d/%m/%Y")),]

weeks <- weeks %>% mutate(week_num=rep(1:nrow(weeks)))

mn_cereal <- mn_cereal %>% left_join(weeks, by="week_end")

mn_cereal <- mn_cereal %>% mutate(treat=if_else(retailer_code==221, 1, 0))

#separate data out by CC, validator, PL, other and treated versus control 
cc_treat <- mn_cereal %>% filter(manufacturer=="GM", treat==1)
cc_control <- mn_cereal %>% filter(manufacturer=="GM", treat==0)

pl_treat <- mn_cereal %>% filter(manufacturer=="PL", treat==1)
pl_control <- mn_cereal %>% filter(manufacturer=="PL", treat==0)

#aggregate sales to store level instead of UPC level 
pl_control_sales <- pl_control %>% group_by(store_code_uc, week_num) %>% summarise(total_sales=sum(sales)) #5985 obs, 105 weeks for each of 57 stores

#add store numbers
treat_stores <- unique(pl_treat$store_code_uc)
pl_treat <- pl_treat %>% mutate(store_num=0)
k=1
for(i in treat_stores) {
  pl_treat <- pl_treat %>% mutate(store_num=if_else(store_code_uc==i, k, store_num))
  k=k+1
}

#aggregate sales to store level instead of UPC level 
pl_treat_sales <- pl_treat %>% group_by(store_num, week_num) %>% summarise(total_sales=sum(sales)) #4515 obs, 105 weeks for each of 43 stores

#try sample of treated stores so it will run faster 
pl_treat_sales <- pl_treat_sales %>% filter(store_num %in% c(1:2))
```

Collect data & test with PL first 
```{r}
TT <- nrow(weeks)  #num of time periods in total 
C <- length(unique(pl_control_sales$store_code_uc))  #num of control stores
N <- length(unique(pl_treat_sales$store_num))  #num of treated stores

#X is a TTxC matrix of control store sales 
X <- matrix(NA, nrow=C, ncol=TT)
control_stores <- unique(pl_control_sales$store_code_uc)
k=1
for(c in control_stores) {
    X[k,] <- pl_control_sales %>% filter(store_code_uc==c) %>% pull(total_sales)
    k=k+1
}

#try log sales
X=log(X)

#create Y NxTT matrix
Y <- matrix(NA, nrow=N, ncol=TT)
for(n in 1:N) {
  Y[n,] <- pl_treat_sales %>% filter(store_num==n) %>% pull(total_sales)
}

#try log sales
Y=log(Y)

#create Z KxN matrix 
tZ <- pl_treat %>% filter(store_num %in% c(1:2)) %>% dplyr::select(store_num, price_diff, num_upcs) %>% distinct() %>% dplyr::select(price_diff, num_upcs) %>% as.matrix()
Z <- t(tZ)
K <- nrow(Z)

#create D a NxTT matrix for which time periods a treated store is treated in
#week 54 starts post period 
D_prep <- pl_treat_sales %>% mutate(post=if_else(week_num %in% c(1:53), 0, 1)) %>% dplyr::select(store_num, post)
D <- matrix(NA, nrow=N, ncol=TT)
for(n in 1:N) {
  D[n,] <- D_prep %>% filter(store_num==n) %>% pull(post)
}

b1_data <- list(TT=TT, C=C, N=N, X=X, K=K, Z=Z, D=D, Y=Y) #data list for stan
```

##### MODEL #####
This model uses a synthetic control combined with heterogeneous treatment effects to estimate sales for treated stores. The model is restricted to meet the synthetic control requirements in the pre period, so that the difference between the synthetic control and actual sales in the post period can be attributed to alpha, our treatment effect. alpha is described by store/category characteristics making theta our effect of those characteristics on the average treatment effect alpha. Note: alpha is an average treatment effect across all post period weeks. Each treated store gets its own weights determined from the same sample of control stores. In this example, we have 43 treated stores and 57 control stores. So each treated store gets its own synthetic control from the 57 control stores. This form of the model would allow us to still use horseshoe priors on beta, but those are not implemented here yet. 
```{r, echo=FALSE}
#b1_model <- stan_model(file = here::here("Code", "Model", "bscm_hierarchy.stan"))
b1_model <- stan_model(file="../Code/Model/bscm_hierarchy_testing.stan")
print(b1_model)

draws <- sampling(b1_model, data=b1_data, seed=2020, cores=3)
save(draws, file="../Data/mn_cereal_draws.RData")
#load("../Data/mn_cereal_draws.RData")
```

###### RESULTS ######

Check results: theta is completely informed by the prior, we can see based on the symmetric distribution. Also, when I turned off theta's prior, the traceplots did not converge anymore. 

theta1 = price_diff =max(upc_price)-min(upc_price)
theta2 = num_upcs = upc_count/max(upc_count)
```{r hierarchy-recovery, echo=FALSE, message=FALSE}
#traceplots
traceplot(draws, pars=c("beta[1,1]", "beta[1,2]", "beta[1,2]", "beta[1,4]", "beta[2,1]", "beta[2,2]", "beta[2,3]", "beta[2,4]")) #N, C
traceplot(draws, pars="beta_0")
traceplot(draws, pars="sigma")
traceplot(draws, pars="theta")
traceplot(draws, pars="nu")
traceplot(draws, pars=c("alpha"))
traceplot(draws, pars=c("theta_0"))

print(draws, pars=c("alpha", "theta"))
print(draws, pars="theta_0")
```

Synthetic control v Y: compare the synthetic control for selected treated stores to the actual sales (Y) for those treated stores 

The synthetic controls are not matching Y in the pre period so results are unreliable. 
```{r hierarchy-pre-treatment, echo=FALSE, message=FALSE}
#construct the synthetic control 
beta0 <- summary(draws, pars="beta_0")
beta_0 <- tibble(beta0[[1]][,1])

beta_data <- summary(draws, pars="beta")
beta <- as.matrix(beta_data[[1]][,1])
beta_mat <- matrix(beta, nrow=b1_data$N, ncol=b1_data$C, byrow=TRUE)

sc <- matrix(NA, nrow=b1_data$N, ncol=b1_data$TT)
for(n in 1:N) {
  sc[n,] = as.matrix(beta_0)[1,1] + beta_mat[n,]%*%as.matrix(X)  #fitted synthetic control in entire time period
}

sc_data  <- as.data.frame(t(sc))
sc_data <- stack(sc_data)

sc_data  <- sc_data  %>% mutate(week=rep(1:b1_data$TT, times=b1_data$N), treat_store=rep(1:b1_data$N, each=b1_data$TT))

trueY <- t(Y)
trueY <- stack(as.data.frame(trueY)) %>% mutate(treat_store=rep(1:b1_data$N, each=b1_data$TT)) %>% dplyr::select(-ind)

names(trueY) <- c("y", "treat_store")

sc_data <- sc_data %>% bind_cols(trueY$y)

names(sc_data) <- c("synthetic_control", "ind", "week", "treat_store", "y")

#look at plots
I=54
sc_data %>% filter(treat_store==1) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 1 ") + geom_vline(xintercept=I)

sc_data %>% filter(treat_store==2) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 2 ") + geom_vline(xintercept=I)

# sc_data %>% filter(treat_store==3) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 3") + geom_vline(xintercept=I)
# 
# sc_data %>% filter(treat_store==4) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 4") + geom_vline(xintercept=I)
# 
# sc_data %>% filter(treat_store==5) %>% ggplot(aes(x=week)) + geom_line(aes(y=y)) + geom_line(aes(y=synthetic_control), linetype="dashed") + ggtitle("SC (dashed) versus actual treated sales (solid): store 5") + geom_vline(xintercept=I)

#sc_data %>% ggplot(aes(x=week)) + geom_line(aes(y=y, col=as.factor(treat_store))) + geom_line(aes(y=synthetic_control, col=as.factor(treat_store)), linetype="dashed") + ggtitle("SC versus actual treated sales") + facet_wrap(~treat_store)
```

Check how well Y_hat matches actual y values 
```{r}
Y_hat <- summary(draws, pars="Y_hat")
yhat <- tibble(Y_hat[[1]][,1])

lower <- Y_hat[[1]][,4]
upper <- Y_hat[[1]][,8]

yhat <- yhat %>% bind_cols(lower, upper)

yhat <- yhat %>% mutate(treat_store=rep(1:b1_data$N, each=b1_data$TT), week=rep(1:b1_data$TT, times=b1_data$N))

names(yhat) <- c("yhat","lower", "upper", "treat_store", "week")

trueY <- as.data.frame(t(b1_data$Y))
trueY <- stack(trueY)
trueY <- trueY %>% mutate(treat_store=rep(1:b1_data$N, each=b1_data$TT))

yhat <- bind_cols(yhat, trueY$values)
names(yhat)[6] <- "trueY"

yhat %>% filter(treat_store==1) %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=yhat, color="Predicted Y"), linetype="dashed") +geom_line(aes(y=trueY, color="True Y")) + ggtitle("Predicted Y values compared to actual Y values, store 1") + labs(x="Week", y="Sales") + scale_color_manual("", breaks=c("Predicted Y", "True Y"), values=c("blue", "red")) 

yhat %>% filter(treat_store==2) %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=yhat, color="Predicted Y"), linetype="dashed") +geom_line(aes(y=trueY, color="True Y")) + ggtitle("Predicted Y values compared to actual Y values, store 2") + labs(x="Week", y="Sales") + scale_color_manual("", breaks=c("Predicted Y", "True Y"), values=c("blue", "red")) 

# yhat %>% filter(treat_store==3) %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=yhat, color="Predicted Y"), linetype="dashed") +geom_line(aes(y=trueY, color="True Y")) + ggtitle("Predicted Y values compared to actual Y values, store 3") + labs(x="Week", y="Sales") + scale_color_manual("", breaks=c("Predicted Y", "True Y"), values=c("blue", "red")) 
```

```{r}
Y_fit <- summary(draws, pars="Y_fit")
yfit <- tibble(Y_fit[[1]][,1])

lower <- Y_fit[[1]][,4]
upper <- Y_fit[[1]][,8]

yfit <- yfit %>% bind_cols(lower, upper)

yfit <- yfit %>% mutate(treat_store=rep(1:b1_data$N, each=b1_data$TT), week=rep(1:b1_data$TT, times=b1_data$N))

names(yfit) <- c("yfit","lower", "upper", "treat_store", "week")

trueY <- as.data.frame(t(b1_data$Y))
trueY <- stack(trueY)
trueY <- trueY %>% mutate(treat_store=rep(1:b1_data$N, each=b1_data$TT))

yfit <- bind_cols(yfit, trueY$values)
names(yfit)[6] <- "trueY"

yfit %>% filter(treat_store==1) %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=yfit, color="Synthetic Control"), linetype="dashed") +geom_line(aes(y=trueY, color="True Y")) + ggtitle("Synthetic Control values compared to actual Y values, store 1") + labs(x="Week", y="Sales") + scale_color_manual("", breaks=c("Synthetic Control", "True Y"), values=c("blue", "red"))+ geom_vline(xintercept=I) 

yfit %>% filter(treat_store==2) %>% ggplot(aes(x=week))+ geom_ribbon(aes(ymin=lower, ymax=upper), fill="gray80") + geom_line(aes(y=yfit, color="Synthetic Control"), linetype="dashed")  +geom_line(aes(y=trueY, color="True Y")) + ggtitle("Synthetic Control values compared to actual Y values, store 2") + labs(x="Week", y="Sales") + scale_color_manual("", breaks=c("Synthetic Control", "True Y"), values=c("blue", "red"))+ geom_vline(xintercept=I) 
```

