---
title: "DC Peanut Butter Synthetic Control"
output: github_document
---

Install packages and load library.

```{r, results = 'hide', message = FALSE}
#install.packages('tidyverse')
#install.packages("Synth")
library(tidyverse)
library(lubridate)
library(Synth)
```

Unzip the 'peanutbutter.tgz' file. Read in 2011 movement and store files, merge them based
on the store code, and filter for 'F' (food stores) and states North Dakota, Minnesota,
Missouri, and D.C.

```{r, results = 'hide'}
untar("peanutbutter.tgz")

move_11 <- read_tsv("nielsen_extracts/RMS/2011/Movement_Files/0506_2011/1421_2011.tsv")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F", 
         fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_11, file = 'pb_full_11.RData')

rm(move_11, stores_11, full_11)
```

Perform the previous step for 2012 and 2013.

```{r, results = 'hide'}
move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/0506_2012/1421_2012.tsv")
stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F",
         fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_12, file = 'pb_full_12.RData')

rm(move_12, stores_12, full_12)

move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/0506_2013/1421_2013.tsv")

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", 
                      col_types = list(col_double(), col_double(),
                      col_double(), col_double(), col_character(),
                      col_character(), col_double(), col_character(), 
                      col_double(), col_character(), col_double(), col_character()))

full_13 <- move_13 %>%
  inner_join(stores_13, by = "store_code_uc") %>%
  filter(channel_code == "F",
         fips_state_descr %in% c("ND", "MN", "MO", "DC"))

save(full_13, file = 'pb_full_13.RData')

rm(move_13, stores_13)
```

Bind full_11,12,13 into one tbl, 'full_11_12_13'. Overwrite the variable week_end to be in
year-month-date format. Create sales variable, which is the number of units sold multiplied
by the price.

```{r, results = 'hide'}
load('pb_full_11.RData')
load('pb_full_12.RData')

full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)

rm(full_11, full_12, full_13)
```

Read in products master file.

```{r, results = 'hide'}
products <- read_tsv('products.tsv', quote = "")
```

Merge products file and full_11_12_13.

```{r, results = 'hide'}
full_11_12_13 <- full_11_12_13 %>%
  left_join(products, by = 'upc')

rm(products)
```

Filter the full dataset for data pertaining to the retailers in DC. Display the retailer
codes in DC.

```{r}
dc_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'DC')

treated_stores <- dc_data %>% filter(retailer_code==842) %>% distinct(store_code_uc)

control_stores <- dc_data %>% filter(retailer_code!=842) %>% distinct(store_code_uc)
```

Assign munfacturer for each brand. Organize data by stores and date, add sales across UPCs.  

```{r}
dc_data <- dc_data %>%
  mutate(manuf_name = substr(dc_data$brand_descr, 1, 3)) %>%
  filter(manuf_name %in% c('SKI', "JIF", "SMU", "SIM", "SAN", "ADA", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == 'CTL', 'CTL',
                        if_else(manuf_name == 'SKI', 'UNI', 'SMU'))) %>%
  mutate(store_code_uc=as.numeric(store_code_uc))

dc_data <- dc_data %>% group_by(store_code_uc, week_end) %>% summarize(sales=sum(sales)) %>%
  arrange(store_code_uc, week_end) 

dc_data <- as.data.frame(dc_data)
```

Check store codes to see how many weeks they have. Stores with less than 157 weeks of observations are dropped
from the data. Then we arrange by 'store_code_uc' and 'week_end', then create a 'n_week_end' variable to represent
the date numerically.

```{r}
weeks <- unique(dc_data$week_end)

codes <- unique(dc_data$store_code_uc)

drops <- c()

for (i in seq_along(codes)) {
  
  single_store <- dc_data %>% filter(store_code_uc==codes[i])
  
  single_store_vec <- unique(single_store$week_end)
  
  if (length(single_store_vec) < length(weeks)) {
    
    drops <- c(drops, codes[i])
    
  }

}

dc_data <- dc_data %>% filter(!store_code_uc %in% drops) %>% arrange(store_code_uc, week_end) %>%
  mutate(n_week_end=as.numeric(week_end))

control_stores <- control_stores %>% filter(!store_code_uc %in% drops)
```

Use data prep to create weights for synthetic control.

```{r, fig.width=8, fig.height=5}
dataprep_out <- dataprep(foo=dc_data, predictors="sales", dependent="sales", unit.variable="store_code_uc",
                         time.variable="n_week_end", treatment.identifier=5133302,
                         controls.identifier=control_stores$store_code_uc,
                         time.predictors.prior=seq(14975, 15535, by = 7), time.optimize.ssr=seq(14975, 15535, by = 7),
                         time.plot=seq(14975, 16067, by = 7))

synth_out <-synth(dataprep_out)
```

```{r fig.width = 8, fig.height = 7}
path.plot(dataprep.res = dataprep_out, synth.res = synth_out, Xlab = c('Time'), Ylab = c('Sales'), tr.intake = 15535,
          Main = 'Synthetic Control and Treated Store Sales')
```

```{r, fig.width=8, fig.height=7}
gaps.plot(dataprep.res = dataprep_out, synth.res = synth_out, Ylab = 'Difference', Xlab = 'Weeks', tr.intake = 15535,
          Main = 'Difference Between Treated and Synthetic Sales (Treated - Synthetic)')
```

```{r}
synth_tables <- synth.tab(synth.res = synth_out, dataprep.res = dataprep_out)
synth_tables$tab.w
```

```{r}
synth_tables$tab.pred
```

```{r}
controls <- dataprep_out$Z0
weights <- synth_tables$tab.w$w.weights
colnames(controls) <- NULL
rownames(controls) <- NULL
w_ctrl <- as.vector(weights %*% t(controls), mode = 'numeric')
treat <- as.vector(dataprep_out$Z1)
weighted_data <- tibble(control = w_ctrl,
                           treated = treat,
                           time = 1:length(w_ctrl))
```

```{r}
weighted_data <- weighted_data %>%
  gather(key = 'Store', value = 'Sales', -time)
```

```{r}
weighted_data %>%
  ggplot(aes(x = time, y = Sales, col = Store)) +
  geom_line() +
  labs(x = 'Time',
       y = 'Total Sales',
       title = 'Sales for Treated Store and Synthetic Control Store')

# this is only graphing the pre-treatment period sales
```

