---
title: "Minnesota, Peanut butter, aggregate diff in diff"
output: html_document
---

This initial analysis is performed on the peanut butter data and looks at individual treated store sales compared to
an aggregate of the sales of the other stores in the market (MO Area). As of now this is only for the sales of 
captain, validator, and private label between stores. We believe that the treated retailer is !!!!!. 

Install packages and load library.

```{r, results = 'hide'}
library(tidyverse)
library(lubridate)
```

Unzip the 'peanutbutter.tgz' file. Read in 2011 movement and store files, merge them based
on the store code, and filter for 'F' (food stores) and states North Dakota, Minnesota,
Missouri, and D.C.

```{r, results = 'hide'}
untar("peanutbutter.tgz", list = TRUE)

untar("peanutbutter.tgz")

move_11 <- read_tsv("nielsen_extracts/RMS/2011/Movement_Files/0506_2011/1421_2011.tsv")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F", 
         fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_11, file = 'pb_full_11.RData')

rm(move_11, stores_11, full_11)
```

Perform the previous step for 2012 and 2013.

```{r, results = 'hide'}
move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/0506_2012/1421_2012.tsv")
stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F",
         fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_12, file = 'pb_full_12.RData')

rm(move_12, stores_12, full_12)

move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/0506_2013/1421_2013.tsv")

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", 
                      col_types = list(col_double(), col_double(),
                      col_double(), col_double(), col_character(),
                      col_character(), col_double(), col_character(), 
                      col_double(), col_character(), col_double(), col_character()))

full_13 <- move_13 %>%
  inner_join(stores_13, by = "store_code_uc") %>%
  filter(channel_code == "F",
         fips_state_descr %in% c("ND", "MN", "MO", "DC"))

save(full_13, file = 'pb_full_13.RData')

rm(move_13, stores_13)
```

Bind full_11,12,13 into one tbl, 'full_11_12_13'. Overwrite the variable week_end to be in
year-month-date format. Create sales variable, which is the number of units sold multiplied
by the price.

```{r, results = 'hide'}
load('pb_full_11.RData')
load('pb_full_12.RData')

full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)

rm(full_11, full_12, full_13)
```

Read in products master file.

```{r, results = 'hide'}
products <- read_tsv('products.tsv', quote = "")
```

Merge products file and full_11_12_13.

```{r, results = 'hide'}
full_11_12_13 <- full_11_12_13 %>%
  left_join(products, by = 'upc')

rm(products)
```

Filter the full dataset for data pertaining to the retailers in MN. Display the retailer
codes in MN.

```{r}
mn_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'MN')

treated_stores <- mn_data %>% filter(retailer_code==??) %>% distinct(store_code_uc)
```

















