---
title: "Minnesota Canned Soup Graph Analysis"
output: github_document
---

Install library.
```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```

Load library and increase memory limit.
```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```

Load in the Minnesota canned soup data. Read in `brands` file which contains the parent companies of all brands listed in `full_11_12_13`.
```{r}
load("mn_can_soup_clean.RData")

brands <- read_csv("soup_brands - Sheet1.csv")
```

Create `campbells` and `generalmills` which contain the brands owned by Campbell's and General Mills. Create tbl `main_manuf_sales` which contains movement data for the brands owned by Campbell's, General Mills, and private label. Create a new variable 'actual_manuf' which denotes ownership by either Campbell's, General Mills or private label.
This allows for sales across different brands to be aggregated later to sales by manufacturer.
```{r}
campbells<- brands %>%
  filter(MANUF == "CAMPBELL'S")

generalmills<- brands %>%
  filter(MANUF == "GENERAL MILLS")

main_manuf_sales <- full_11_12_13 %>%
  filter(manuf_name %in% c("CAM", "PRO", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == "CAM", "campbells", if_else(manuf_name=="PRO", "generalmills", "CTL")))
```

Create `retailer_weekly`, which is filtered for retailers in Minnesota, grouped by retailer code, brand_name, and week_end, creating weekly sales and average prices by manufacturer within retailer. `ret_codes` contains each unique retailer code. The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the approximate CC implementation date. Each graph includes year specific regression lines.
```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-07-30"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-07-30"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-07-30")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-07-30")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```

captain: Campbell's
validator: General Mills

notes: 


