---
title: "Minnesota Peanut Butter"
output: word_document
---


Install packages.

```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```


Load library and increase memory limit.

```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```


Unzip file.

```{r}
untar("peanutbutter.tgz", list = TRUE)

untar("peanutbutter.tgz")

move_11 <- read_tsv("nielsen_extracts/RMS/2011/Movement_Files/0506_2011/1421_2011.tsv")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/0506_2012/1421_2012.tsv")

stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/0506_2013/1421_2013.tsv")

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", col_types = list(col_double(), col_double(),
                        col_double(), col_double(), col_character(), col_character(), col_double(), col_character(), col_double(),
                        col_character(), col_double(), col_character()))

products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote = "")
```


  Merge the data from the 'stores' file and the 'products' master file to the movement file for each year. Filter for channel code 'F', which denotes 'Food' and 
for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).

```{r}
full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

full_13 <- move_13 %>%
  inner_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")
```


Combine 'full_11', 'full_12', and 'full_13' into one file, 'full_11_12_13' containing the data for all years.
Change 'week_end' variable to year-month-day format. Create variable 'sales' which is 'units' * 'price'.

```{r}
full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)
```


Create tbls containing each distinct store code ('store_id_11/12/13'). Anti join those tbls to get 6 more tbls containing just the stores that 
only show up in 1 of the years ex: 'in_11_not_12'. Anti join those tbls with the full movement file to remove the stores that only appear in 1
of the years. Create a new variable 'manuf_name' which contains the first 3 characters of the brand_name and allows for easy identification of the 
manufacturers. Save the full movement file and remove unneccesary files from memory.

```{r}
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)
store_id_13 <- distinct(full_13, store_code_uc)

in_11_not_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
in_11_not_13 <- anti_join(store_id_11, store_id_13, by = "store_code_uc")
in_12_not_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")
in_12_not_13 <- anti_join(store_id_12, store_id_13, by = "store_code_uc")
in_13_not_11 <- anti_join(store_id_13, store_id_11, by = "store_code_uc")
in_13_not_12 <- anti_join(store_id_13, store_id_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  anti_join(in_11_not_12, by = "store_code_uc") %>%
  anti_join(in_11_not_13, by = "store_code_uc") %>%
  anti_join(in_12_not_11, by = "store_code_uc") %>%
  anti_join(in_12_not_13, by = "store_code_uc") %>%
  anti_join(in_13_not_11, by = "store_code_uc") %>%
  anti_join(in_13_not_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  mutate(manuf_name = substr(full_11_12_13$brand_descr, 1, 3))

save(full_11_12_13, file = "full_11_12_13.RData")

rm(full_11, full_12, full_13, in_11_not_12, in_11_not_13, in_12_not_11, in_12_not_13, in_13_not_11, in_13_not_12,
   store_id_11, store_id_12, store_id_13, move_11, move_12, move_13, products, stores_11, stores_12, stores_13)
```


Create vector 'stores' that contains each distinct store in the full movement file. Define a vector 'retail_switchers' that will contain the codes
for every store that switches retail codes between 2011, 2012, or 2013. The 'for' loop finds these codes and stores them in 'retail_switchers'.

```{r}
stores <- unique(full_11_12_13$store_code_uc)

retail_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$retailer_code)
  
  if (length(switcher_test) > 1) {
    
    retail_switchers <- append(retail_switchers, stores[i])
    
  }
}
```


Define a vector 'parent_switchers' that will contain the codes for every store that switches parent codes between 2011, 2012, or 2013. The 'for' loop
finds these codes and stores them in 'parent_switchers'.

```{r}
parent_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$parent_code)
  
  if (length(switcher_test) > 1) {
    
    parent_switchers <- append(parent_switchers, stores[i])
    
  }
}
```


Print 'retail_switchers' and 'parent_switchers'.

```{r}
retail_switchers

parent_switchers
```


Create tbl 'switchers' that contains the data for every store that switches retail or parent codes. Filter out these stores from the full movement
file.

```{r}
switchers <- full_11_12_13 %>%
  filter(store_code_uc %in% retail_switchers | store_code_uc %in% parent_switchers)

full_11_12_13 <- full_11_12_13 %>%
  anti_join(switchers, by = "store_code_uc")
```


Read in 'brands' file which contains the parent companies of all brands listed in 'full_11_12'.

```{r}
brands <- read_csv("pb_brands.csv")
```


Create 'uni' and 'smuck'_pb which contains the brands owned by Unilever and Smucker's. Create tbl 'main_manuf_sales' which contains movement data for the brands owned
by Unilever, Smucker's, and the private label. Create a new variable 'actual_manuf' which denotes ownership by either unilver, smucker's,
or private label so that sales across different brands can be aggregated later to sales by manufacturer.

```{r}
uni_pb <- brands %>%
  filter(Manuf == "Unilever")

smuck_pb <- brands %>%
  filter(Manuf == "Smucker")

main_manuf_sales <- full_11_12_13 %>%
  filter(manuf_name %in% c("JIF", "SMU", "SIM", "SAN", "ADA", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == "CTL", "CTL", "SMU"))
```


Filter 'main_manuf_sales' for observations where 'retailer_code' != NA and save as tbl 'retail_no_NA'. 
Filter 'main_manuf_sales' for observations where 'retailer_code' = NA and impute 'parent_code' to replace those values, then recombine with the
observations that originally had a 'retailer_code'.

```{r}
retail_no_NA <- main_manuf_sales %>%
  filter(!is.na(retailer_code))

main_manuf_sales <- main_manuf_sales %>%
  filter(is.na(retailer_code)) %>%
  mutate(retailer_code = parent_code) %>%
  bind_rows(retail_no_NA)

save(main_manuf_sales, file = "main_manuf_sales.RData")
```


Create 'retailer_weekly', which is filtered for retailers in Minnesota, grouped by retailer code, brand_name, and week_end, creating weekly sales
and average prices by manufacturer within retailer. 'ret_codes' contains each unique retailer code. 
The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average
weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the 
approximate CC implementation date. Each graph includes year specific regression lines.

```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-07-16"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-07-16"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-07-16")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-07-16")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```

Captain : Unilever
Validator: Smuckers

notes: Skippy was purchased from Unilever by Hormel Foods in 2013. Also, I couldn't find any brands that were actually owned by
Unilever that had any sales show up in the movement file.