---
title: "minnesota_jams.Rmd"
output: word_document    
---

This code performs the graphical analysis of retailers in the spreads and jams category in minnesota.

Install packages.
```{r eval =FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```

Load packages and increase memory limit.
```{r results='hide'}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```

Load data.
```{r}
load('mn_spreads_jams_clean.RData')
```

Create tbl `main_manuf_sales` which contains movement data for the brands owned
by Smucker's, Welch's, and private label. Create a new variable `actual_manuf` which denotes whether Smucker's, 
Welch's, or private label own a particular brand. This allows for sales across different brands to be aggregated 
later to sales by manufacturer.
```{r}
main_manuf_sales <- full_11_12_13 %>% 
  filter(manuf_name %in% c("SMU","SAN","R W", "DIC", "KIN", "CRO", "WEL", "CTL")) %>% 
  mutate(actual_manuf = if_else(manuf_name == "SMU","SMU",
                        if_else(manuf_name == "SAN", "SMU", 
                        if_else(manuf_name == "R W", "SMU", 
                        if_else(manuf_name == "DIC", "SMU",
                        if_else(manuf_name == "KIN", "SMU", 
                        if_else(manuf_name == "CRO", "SMU",
                        if_else(manuf_name == "WEL", "WEL","CTL"))))))))
```

Create `retailer_weekly`, which is filtered for retailers in Minnesota, grouped by `retailer_code`, `brand_name`, and `week_end`, creating weekly sales and average prices by manufacturer within retailer. `ret_codes` contains each unique retailer code. The loop goes over each unique `retailer_code` and graphs the weekly sales by manufacturer for each `retailer_code`. It also plots the average weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the approximate CC implementation date. Each graph includes year specific regression lines.
```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-07-16"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-07-16"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-07-16")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-07-16")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```

Captain: Smucker's
Validator: Welch's
