---
title: "Hot dog data cleaning"
output: github_document
---

Note: This document contains all the code used to merge and clean data for the hot dog category. 

Install library.
```{r eval=FALSE, include=FALSE}
#install.packages("tidyverse")
```

Load library.
```{r}
library(plyr)
library(tidyverse)
library(lubridate)
library(readxl)
library(foreach)
```

Untar (unzip) the `.tgz` file. Use loop to read in 2014 movement, stores, rms, and the products master file. 
```{r}
hotdog_files <- untar('Hotdogs_2012-14.tgz', list = TRUE)
untar('Hotdogs_2012-14.tgz')
move_14 <- read_tsv("nielsen_extracts/RMS/2014/Movement_Files/3002_2014/3576_2014.tsv")
stores_14 <- read_tsv("nielsen_extracts/RMS/2014/Annual_Files/stores_2014.tsv")
rms_14 <- read_tsv("nielsen_extracts/RMS/2014/Annual_Files/rms_versions_2014.tsv")
products <- read_tsv('nielsen_extracts/RMS/Master_Files/Latest/products.tsv', quote = '')
```

Create `full_14` by joining the 2014 stores file to the movement file on `store_code_uc`. Then filter for `F` (food)
and `ND` (North Dakota) `MN` (Minnesota) `MO` (Missouri) and `IL` (Illinois). Join the 2011 rms file to the movement
file on `upc`, then join the products file to the movement file on `upc` and `upc_ver_uc`. This ensures that no
entries in the movement file are duplicated.
```{r}
full_14 <- move_14 %>%
  left_join(stores_14, by = 'store_code_uc') %>% 
  filter(channel_code == 'F' & fips_state_descr %in% c('ND', 'MN', 'MO', 'IL')) %>%
  left_join(rms_14, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_14, rms_14, stores_14)
```

Read in files for 2012 the same way as for 2014, and create `full_12` the same way as `full_14`.
```{r}
move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/3002_2012/3576_2012.tsv")
stores_12 <- read_tsv('nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv')
rms_12 <- read_tsv('nielsen_extracts/RMS/2012/Annual_Files/rms_versions_2012.tsv')

full_12 <- move_12 %>%
  left_join(stores_12, by = 'store_code_uc') %>% 
  filter(channel_code == 'F' & fips_state_descr %in% c('ND', 'MN', 'MO', 'IL')) %>%
  left_join(rms_12, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_12, stores_12, rms_12)
```

Repeat for 2013. 
```{r}
move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/3002_2013/3576_2013.tsv")
stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", guess_max = 20000)
rms_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2013.tsv")

full_13 <- move_13 %>%
  left_join(stores_13, by = 'store_code_uc') %>% 
  filter(channel_code == 'F' & fips_state_descr %in% c('ND', 'MN', 'MO', 'IL')) %>%
  left_join(rms_13, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_13, stores_13, rms_13, products)
```

Read in file containing the manufacturer upc prefixes. The captain and validator for cereal are General Mills and
Kellogg's, respectively. Create separate vectors with the upc prefixes for both General Mills and Kellogg's called
`gm_prefs` and `kel_prefs`.
```{r}
prefixes <- read_xlsx('Manufacturer UPC Prefixes - From GS1 Company Database.xlsx')

saralee_prefs <- prefixes %>%
  filter(manufacturer == 'Sara Lee (Hillshire Brands)') %>%
  select(prefix) %>%
  pull()

oscar_prefs <- prefixes %>%
  filter(manufacturer == "Oscar Mayer (Kraft Heinz)") %>%
  select(prefix) %>%
  pull()
```

Create `full_hotdog` by combining the data for 2013, 2014 and 2012. Convert `week_end` to be a date variable and create a
numeric version called `n_week_end` which is needed for microsynth. Create `sales` by multiplying `units` and `price`.
Create `manufacturer` by assinging the correct manufacturer based on upc prefixes. We assign General Mills, Kellogg's,
Private Label, and upcs belonging to any other manufacturers fall under 'other'.
```{r}
full_hotdog <- full_14 %>%
  bind_rows(full_12) %>% bind_rows(full_13) %>% 
  mutate(week_end = ymd(week_end),
         sales = units * price,
         manufacturer = if_else(grepl(paste(saralee_prefs, collapse = '|'), upc), 'Sara Lee',
                        if_else(grepl(paste(oscar_prefs, collapse = '|'), upc), "Oscar Mayer",
                        if_else(brand_descr == 'CTL BR', 'Private Label', 'Other', missing = 'Other'))))

rm(full_13, full_14, full_12, prefixes)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than two years, and store those codes in the vector
`missing_stores`.
```{r}
missing_stores <- full_hotdog %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < length(unique(year(full_hotdog$week_end)))) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_hotdog %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_hotdog %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Filter for the store codes that do not switch retailer or parent codes and are not missing from one of the years.
Replace missing `retailer_code` values with the `parent_code`.
```{r}
full_hotdog <- full_hotdog %>%
  filter(!store_code_uc %in% unique(c(parent_switchers, retailer_switchers, missing_stores))) %>%
  mutate(retailer_code = if_else(is.na(retailer_code), parent_code, retailer_code))

rm(parent_switchers, retailer_switchers, missing_stores)
```

Create `multi_brand_descr` which contains the upc codes that have multiple brand descriptions. We assume that upc codes
with one valid brand description and an `NA` value as the other description actually have the same description and are
the same product. Create `non_na_descr` which contains the upc codes that have multiple brand descriptions that don't
include an `NA` value. Filter `full_hotdog` for the upc codes that have multiple valid brand descriptions and compare
them to see if the upc code was used for different products belonging to different manufacturers. All the upc codes in
this category that had multiple brand descriptions were the same product, they just had a slight change in how the
`brand_descr` was entered.
```{r}
multi_brand_descr <- full_hotdog %>%
  distinct(upc, brand_descr) %>%
  group_by(upc) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  select(upc) %>%
  pull()

non_na_descr <- full_hotdog %>%
  filter(upc %in% multi_brand_descr) %>%
  distinct(upc, brand_descr) %>%
  arrange(upc) %>%
  filter(!is.na(brand_descr)) %>%
  group_by(upc) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  select(upc) %>%
  pull()

full_hotdog %>%
  filter(upc %in% non_na_descr) %>%
  distinct(upc, brand_descr) %>%
  arrange(upc)
```

Check if there are private label products with `NA` brand description values, which we should change to `'CTL BR'` so that they are aggregated under the correct manufacturer. Change `NA` brand descriptions for private label products. 
```{r}
full_hotdog %>%
  filter(upc %in% multi_brand_descr) %>%
  distinct(upc, brand_descr) %>%
  arrange(upc)

priv_lab_na <- full_hotdog %>%
  filter(upc %in% multi_brand_descr) %>%
  distinct(upc, brand_descr) %>%
  filter(brand_descr == 'CTL BR') %>%
  select(upc) %>%
  pull()

full_hotdog <- full_hotdog %>%
  mutate(brand_descr = if_else(upc %in% priv_lab_na, 'CTL BR', brand_descr))
```

When a upc has no sales in a given `week_end` it is not recorded in the data. We need to impute the weeks that a given
upc had zero sales. First, create `full_weeks` which contains all values of `week_end`. Split `full_hotdog` into
separate `tibbles`, one for each store and upc combination. Loop over the separated `tibbles` and if the number of
observations for a given upc in a given store is less than the full number of weeks, do an anti-join with `full_weeks`
to get the missing `week_end` values. Create a matrix `missing_data` which will contain the missing observations. Fill
`missing_data` in with the variables that stay constant over time, then change `week_end` to be the missing `week_end` 
values. Change `price` to `NA`, and fill in `units` and `sales` with zero. Use `bind_rows` to add `missing_data` back 
to the original data. Recombine the separate `full_hotdog` data into one `tibble`.
```{r}
full_weeks <- full_hotdog %>%
  distinct(week_end)

full_hotdog <- full_hotdog %>%
  group_split(store_code_uc, upc)

for (i in 1:length(full_hotdog)) {
  
  if(nrow(full_hotdog[[i]]) < length(full_weeks$week_end)) {
  
  vars_vec <- full_hotdog[[i]][1,]
  
  missing_weeks <- full_weeks %>%
      anti_join(full_hotdog[[i]], by = 'week_end') %>%
      pull()

  missing_data <- matrix(nrow = length(missing_weeks),
                         ncol = length(vars_vec)
                         )

  missing_data <- map_df(1:length(missing_weeks), function(y) missing_data[y,] <- vars_vec)

  missing_data['week_end'] <- missing_weeks
  
  missing_data['price'] <- NA

  missing_data[c('units', 'sales')] <- 0
    
  full_hotdog[[i]] <- full_hotdog[[i]] %>%
    bind_rows(missing_data)
  
  }}

full_hotdog <- bind_rows(full_hotdog)
```

Check that all upc codes have observations for the full time period and that none have more observations than they 
should.
```{r}
full_hotdog %>%
  group_by(store_code_uc, upc) %>%
  summarize(n_weeks = n()) %>%
  filter(n_weeks < length(full_weeks$week_end) |
         n_weeks > length(full_weeks$week_end))
```

Create numeric `week_end` variable `n_week_end`.
```{r}
full_hotdog <- full_hotdog %>%
  mutate(n_week_end = as.numeric(week_end))
```

Save the cleaned data and save files for each state. 
```{r}
save(full_hotdog, file = 'hotdog_clean.RData')

mn_hotdog <- full_hotdog %>% filter(fips_state_descr == 'MN')
il_hotdog <- full_hotdog %>% filter(fips_state_descr == 'IL')
mo_hotdog <- full_hotdog %>% filter(fips_state_descr == 'MO')
nd_hotdog <- full_hotdog %>% filter(fips_state_descr == 'ND')

save(mn_hotdog, file="mn_hotdog_clean.RData")
save(il_hotdog, file="il_hotdog_clean.RData")
save(mo_hotdog, file="mo_hotdog_clean.RData")
save(nd_hotdog, file="nd_hotdog_clean.RData")
```



