---
title: "Ice Cream Data Cleaning"
output: github_document
---

This document contains all the code used to merge and clean the data for the ice cream category. 

Load library and increase memory limit.
```{r}
library(tidyverse)
library(lubridate)
```

Read in files for 2011 (and products file). Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code `F`, which denotes `Food` and for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).
```{r}
untar("ice_cream.tgz")

move_11<-read_tsv("nielsen_extracts/RMS/2011/Movement_Files/2005_2011/2672_2011.tsv")
stores_11<-read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")
stores_11 <- stores_11 %>% select(-fips_state_code, -fips_county_code, -dma_code)
stores_11 <- stores_11 %>% filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL"))
move_11 <- move_11 %>% filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL"))

products<-read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote="")
rms_10 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/rms_versions_2011.tsv")

full_11 <- move_11 %>%
  left_join(stores_11, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL"))

%>%
  left_join(rms_11, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_11, rms_11, stores_11)
```

Read in files for 2012. Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code `F`, which denotes `Food` and for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).Remove move/stores files from 2011 and 2012 for memory space. 
```{r}
move_12<-read_tsv("nielsen_extracts/RMS/2012/Movement_Files/2005_2012/2672_2012.tsv")
stores_12<-read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")
rms_12 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2012.tsv")

full_12 <- move_12 %>%
  left_join(stores_12, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_12, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_12, stores_12, rms_12)
```

Read in files for 2013. Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code `F`, which denotes `Food` and for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).
```{r}
move_13<-read_tsv("nielsen_extracts/RMS/2013/Movement_Files/2005_2013/2672_2013.tsv")
stores_13<-read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", guess_max=20000)
rms_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2013.tsv")

full_13 <- move_13 %>%
  left_join(stores_13, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_13, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_13, stores_13, rms_13, products)
```

Combine all three years into one file, `full_data`. Change `week_end` variable to year-month-day format. Create
variable `sales` which is `units` * `price`. Create variable for manufacturer from the first 3 digits of the brand
description.
```{r}
full_data <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), 
         sales = units * price,
         manuf_name = substr(brand_descr, 1, 3))

rm(full_11, full_12, full_13)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than four years, and store those codes in the vector
`missing_stores`.
```{r}
missing_stores <- full_data %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < 3) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_data %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_data %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create one vector with the store codes to remove because they switch retailer or parent codes or they don't show up
in all the years in the data.
```{r}
remove_stores <- unique(c(parent_switchers, retailer_switchers, missing_stores))
```

Using the `remove_stores` vector, filter out the store codes that switch retailer or parent codes or don't show up
in all the years in the data.
```{r}
full_data <- full_data %>%
  filter(!store_code_uc %in% remove_stores)

rm(parent_switchers, retailer_switchers, remove_stores, missing_stores)
```

Use `mutate` to replace missing `retailer_code` values with the `parent_code`.
```{r}
full_data <- full_data %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Save the cleaned data and save files for each state. 
```{r}
save(full_data, file="ice_cream_clean.RData")

mn_data <- full_data %>% filter(fips_state_descr=="MN")
il_data <- full_data %>% filter(fips_state_descr=="IL")
mo_data <- full_data %>% filter(fips_state_descr=="MO")
nd_data <- full_data %>% filter(fips_state_descr=="ND")

save(mn_data, file="mn_ice_cream_clean.RData")
save(il_data, file="il_ice_cream_clean.RData")
save(mo_data, file="mo_ice_cream_clean.RData")
save(nd_data, file="nd_ice_cream_clean.RData")
```



