---
title: "Minnesota Pickles/Olives Graph Analysis"
output: github_document
---

This code reads in the data for the pickles and olives category in Minnesota and performs the graphical analysis
used to determine the treated retailer.

Install packages.
```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```

Load library and increase memory limit.
```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```

Load minnesota data.
```{r}
load('mn_pickles_olives_clean.RData')
```

Create `tbl`, `main_manuf_sales` which contains movement data for the brands owned by Musco, Pinnacle, and private label. Create a new variable `actual_manuf` which denotes ownership by either pinnacle, private label, or musco.
This allows for sales across different brands to be aggregated later to sales by manufacturer.
```{r}
main_manuf_sales <- full_11_12_13 %>%
  filter(manuf_name %in% c("EAR", "PEA", "GRE", "HOM", "BLA", "VLA", "NAL", "CTL") | 
         brand_descr %in% c("FARMER'S GARDEN", "MEDITERRANEAN PEARLS")) %>%
  mutate(actual_manuf = if_else(manuf_name == "EAR", "MUSCO", 
                        if_else(manuf_name == "PEA", "MUSCO", 
                        if_else(manuf_name == "GRE", "MUSCO",
                        if_else(manuf_name == "HOM", "MUSCO", 
                        if_else(manuf_name == "BLA", "MUSCO", 
                        if_else(manuf_name == "VLA", "PIN",
                        if_else(manuf_name == "NAL", "PIN", 
                        if_else(brand_descr == "FARMER'S GARDEN", "PIN",
                        if_else(brand_descr == "MEDITERRANEAN PEARLS", "MUSCO", "CTL"))))))))))
```

Create `retailer_weekly`, which is filtered for retailers in Minnesota, grouped by `retailer_code`, `brand_name`, and `week_end`, creating weekly sales and average prices by manufacturer within retailer. `ret_codes` contains each unique retailer code. The loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the approximate CC implementation date. Each graph includes year specific regression lines.
```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-10-08"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-10-08"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-10-08")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-10-08")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```

captain: pinnacle
validator: musco
