---
title: "DC Peanut Butter Synthetic Retailer Test"
output: github_document
---

Install and load packages. 
```{r}
#install.packages(c("tidyverse", "microsynth"))

library(tidyverse)
library(microsynth)
library(lubridate)
```

Load in the data for DC Peanut Butter category. This data uses 842 as the treated retailer. Create treated_stores and control_stores, which contain the unique store codes for each group. 
```{r}
load("dc_pb_data.RData")

treated_stores <- dc_data %>% filter(retailer_code==842) %>% distinct(store_code_uc)

control_stores <- dc_data %>% filter(retailer_code!=842) %>% distinct(store_code_uc)
```

Assign the manfacturer (Store, Unilever, Smuckers) for each brand. Convert store code to be a numeric. Organize data by retailer, stores and date, then add sales across UPCs.  
```{r}
dc_data <- dc_data %>%
  mutate(manuf_name = substr(dc_data$brand_descr, 1, 3)) %>%
  filter(manuf_name %in% c('SKI', "JIF", "SMU", "SIM", "SAN", "ADA", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == 'CTL', 'CTL',
                        if_else(manuf_name == 'SKI', 'UNI', 'SMU'))) %>%
  mutate(store_code_uc=as.numeric(store_code_uc))

dc_data <- dc_data %>% group_by(retailer_code, store_code_uc, actual_manuf, week_end) %>% summarize(sales=sum(sales)) %>%
  arrange(store_code_uc, week_end) 

```

Check store codes to see how many weeks they have. Stores with less than 157 weeks of observations are dropped
from the data. Then we arrange by `store_code_uc` and `week_end`, then create a `n_week_end` variable to represent
the date numerically. Change manufacter variable to be numeric. 
```{r}
weeks <- unique(dc_data$week_end)

codes <- unique(dc_data$store_code_uc)

drops <- c()

for (i in seq_along(codes)) {
  
  single_store <- dc_data %>% filter(store_code_uc==codes[i])
  
  single_store_vec <- unique(single_store$week_end)
  
  if (length(single_store_vec) < length(weeks)) {
    
    drops <- c(drops, codes[i])
    
  }

}

dc_data <- dc_data %>% filter(!store_code_uc %in% drops) %>% arrange(retailer_code, store_code_uc, week_end) %>%
  mutate(n_week_end=as.numeric(week_end))

control_stores <- control_stores %>% filter(!store_code_uc %in% drops) 

control_stores <- control_stores %>% arrange(store_code_uc)

dc_data <- dc_data %>% mutate(manuf=if_else(actual_manuf=="CTL", 1, if_else(actual_manuf=="SMU", 2, 3)))
```

Create a vector of the unique retailer codes in DC Data. Create a loop that creates a synthetic control for each manufacturer in each store for each retailer. Collect the p values and treatment effects from each synthetic control.
```{r, message=FALSE, warning=FALSE}
ret_codes <- unique(dc_data$retailer_code)
msynth_results <- tibble()

for (i in seq_along(ret_codes)) {
  msynth_pvals <- c()
  msynth_effects <- c()
  t_stores <- dc_data %>% filter(retailer_code==ret_codes[i]) 
  c_stores <- dc_data %>% filter(retailer_code!=ret_codes[i]) %>% mutate(type=0) 
  t_store_codes <- unique(t_stores$store_code_uc)
  for (j in seq_along(t_store_codes)) {
    store <- t_stores %>% filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = 1)
    store_data <- bind_rows(store, c_stores)
    manufs <- unique(dc_data$manuf)
    for (k in seq_along(manufs)) {
      manuf_data <- store_data %>%
        filter(manuf == manufs[k])
      msynth <- microsynth(data = as.data.frame(manuf_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15535, 
                           end.post = 16067,
                           match.out = "sales",
                           match.covar = "sales",
                           result.var="sales", 
                           omnibus.var="sales",
                           test="twosided", 
                           use.survey = FALSE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
  }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = ret_codes[i]
  )
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plotting distributions of p-values and effects at the Manufacturer level.
```{r}
msynth_results %>%
  ggplot(aes(x = pval)) +
  geom_histogram() +
  facet_wrap(~retailer) + labs(x="P-Value", y="Count", title="Manufacturer Level P-Values for DC Peanut Butter Data")
```


```{r}
msynth_results %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  facet_wrap(~retailer) + labs(x="Treatment Effect", y="Count", title="Manufacturer Level Treatment Effects for DC Peanut Butter Data")
```

Aggregate sales across stores. Create a loop that creates a synthetic control for each store in each retailer. Collect the p values and treatment effects from each synthetic control.  
```{r, message=FALSE, warning=FALSE}
dc_store_data <- dc_data %>% group_by(retailer_code, store_code_uc, n_week_end) %>% summarise(sales=sum(sales))

msynth_results <- tibble()
msynth_effects <- c()
msynth_pvals <- c() 
loop_results <- c()

for (i in seq_along(ret_codes)) {
  msynth_pvals <- c()
  msynth_effects <- c()
  t_stores <- dc_store_data %>% filter(retailer_code==ret_codes[i]) 
  c_stores <- dc_store_data %>% filter(retailer_code!=ret_codes[i]) %>% mutate(type=0) 
  t_store_codes <- unique(t_stores$store_code_uc)
  for (j in seq_along(t_store_codes)) {
    store <- t_stores %>% filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = 1)
    store_data <- bind_rows(store, c_stores)
      msynth <- microsynth(data = as.data.frame(store_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15535, 
                           end.post = 16067,
                           match.out = "sales",
                           match.covar = "sales",
                           result.var="sales", 
                           omnibus.var="sales",
                           test="twosided",
                           use.survey = FALSE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = ret_codes[i]
  )
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plotting distributions of p-values and effects at the store level.
```{r}
msynth_results %>%
  ggplot(aes(x = pval)) +
  geom_histogram() +
  facet_wrap(~retailer) + labs(x="P-Value", y="Count", title="Store Level P-Values for Retailers in DC Peanut Butter Data")
```

```{r}
msynth_results %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  facet_wrap(~retailer) + labs(x="Treatment Effect", y="Count", title="Store Level Treatment Effects for DC Peanut Butter Data")
```

Create `ret_code_combo` that pairs each retailer with each other retailer, giving each the possibility to be the treated retailer code. Use `dc_store_data` which is aggregated across stores. Empty the the results, pvals, and effects. 
```{r}
ret_code_combo <- as_tibble(expand.grid(treat=ret_codes, control=ret_codes)) %>% filter(treat!=control)
```

Create a loop that runs microsynth for each retailer combination by row from `ret_code_combo`. Collect p-values and treatment effects for each store in each retailer combination. 
```{r, message=FALSE, warning=FALSE}
msynth_results <- tibble()
loop_results <- tibble()

for (i in 1:9) {
  msynth_pvals <- c()
  msynth_effects <- c()
  loop_rets <- ret_code_combo %>% filter(row_number()==i) %>% as_vector()
  t_stores <- dc_store_data %>% filter(retailer_code==unname(loop_rets[1])) 
  c_stores <- dc_store_data %>% filter(retailer_code==unname(loop_rets[2])) %>% mutate(type=0) 
  t_store_codes <- unique(t_stores$store_code_uc)
  for (j in seq_along(t_store_codes)) {
    store <- t_stores %>% filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = ifelse(n_week_end > 15535, 1, 0))
    store_data <- bind_rows(store, c_stores)
         msynth <- microsynth(data = as.data.frame(store_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15535, 
                           end.post = 16067,
                           match.out = "sales",
                           match.out.min = "sales",
                           result.var="sales", 
                           omnibus.var="sales", 
                           test="twosided", 
                           use.survey = FALSE,
                           use.backup = TRUE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = paste0(unname(loop_rets[1]), ",", unname(loop_rets[2]))
  )
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plot the P-Values for synthetic controls created from every combination of retailers.
```{r}
msynth_results %>%
  ggplot(aes(x = pval)) +
  geom_histogram() +
  facet_wrap(~retailer) +
  labs(x = 'P-Value',
       y = 'Count',
       title = 'P-Values for Retailer Combinations at the Store Level: DC Peanut Butter')
```

```{r}
msynth_results %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  facet_wrap(~retailer) +
  labs(x = 'Effect',
       y = 'Count',
       title = 'Treatment Effects for Retailer Combinations at Store Level: DC Peanut Butter')
```













