---
title: "DC Peanut Butter Synthetic Control"
output: github_document
---

Install packages and load library.

```{r, results = 'hide', message = FALSE}
#install.packages('tidyverse')
#install.packages("Synth")
library(tidyverse)
library(lubridate)
library(Synth)
```

Unzip the 'peanutbutter.tgz' file. Read in 2011 movement and store files, merge them based
on the store code, and filter for 'F' (food stores) and states North Dakota, Minnesota,
Missouri, and D.C.

```{r, results = 'hide'}
untar("peanutbutter.tgz")

move_11 <- read_tsv("nielsen_extracts/RMS/2011/Movement_Files/0506_2011/1421_2011.tsv")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F", 
         fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_11, file = 'pb_full_11.RData')

rm(move_11, stores_11, full_11)
```

Perform the previous step for 2012 and 2013.

```{r, results = 'hide'}
move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/0506_2012/1421_2012.tsv")
stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F",
         fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_12, file = 'pb_full_12.RData')

rm(move_12, stores_12, full_12)

move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/0506_2013/1421_2013.tsv")

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", 
                      col_types = list(col_double(), col_double(),
                      col_double(), col_double(), col_character(),
                      col_character(), col_double(), col_character(), 
                      col_double(), col_character(), col_double(), col_character()))

full_13 <- move_13 %>%
  inner_join(stores_13, by = "store_code_uc") %>%
  filter(channel_code == "F",
         fips_state_descr %in% c("ND", "MN", "MO", "DC"))

save(full_13, file = 'pb_full_13.RData')

rm(move_13, stores_13)
```

Bind full_11,12,13 into one tbl, 'full_11_12_13'. Overwrite the variable week_end to be in
year-month-date format. Create sales variable, which is the number of units sold multiplied
by the price.

```{r, results = 'hide'}
load('pb_full_11.RData')
load('pb_full_12.RData')

full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)

rm(full_11, full_12, full_13)
```

Read in products master file.

```{r, results = 'hide'}
products <- read_tsv('products.tsv', quote = "")
```

Merge products file and full_11_12_13.

```{r, results = 'hide'}
full_11_12_13 <- full_11_12_13 %>%
  left_join(products, by = 'upc')

rm(products)
```

Filter the full dataset for data pertaining to the retailers in DC. Display the retailer
codes in DC.

```{r}
dc_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'DC')

treated_stores <- dc_data %>% filter(retailer_code==842) %>% distinct(store_code_uc)

control_stores <- dc_data %>% filter(retailer_code!=842) %>% distinct(store_code_uc)
```

Assign munfacturer for each brand. Organize data by stores and date, add sales across UPCs.  

```{r}
dc_data <- dc_data %>%
  mutate(manuf_name = substr(dc_data$brand_descr, 1, 3)) %>%
  filter(manuf_name %in% c('SKI', "JIF", "SMU", "SIM", "SAN", "ADA", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == 'CTL', 'CTL',
                        if_else(manuf_name == 'SKI', 'UNI', 'SMU'))) %>%
  mutate(store_code_uc=as.numeric(store_code_uc))

dc_data <- dc_data %>% group_by(store_code_uc, week_end) %>% summarize(sales=sum(sales)) %>%
  arrange(store_code_uc, week_end) 

dc_data <- as.data.frame(dc_data)
```

Check store codes to see how many weeks they have. Stores with less than 157 weeks of observations are dropped
from the data. Then we arrange by 'store_code_uc' and 'week_end', then create a 'n_week_end' variable to represent
the date numerically.

```{r}
weeks <- unique(dc_data$week_end)

codes <- unique(dc_data$store_code_uc)

drops <- c()

for (i in seq_along(codes)) {
  
  single_store <- dc_data %>% filter(store_code_uc==codes[i])
  
  single_store_vec <- unique(single_store$week_end)
  
  if (length(single_store_vec) < length(weeks)) {
    
    drops <- c(drops, codes[i])
    
  }

}

dc_data <- dc_data %>% filter(!store_code_uc %in% drops) %>% arrange(store_code_uc, week_end) %>%
  mutate(n_week_end=as.numeric(week_end))

control_stores <- control_stores %>% filter(!store_code_uc %in% drops) 

control_stores <- control_stores %>% arrange(store_code_uc)
```

Use data prep to create weights for synthetic control.

```{r, fig.width=8, fig.height=5}
dataprep_out <- dataprep(foo=dc_data, predictors="sales", dependent="sales", unit.variable="store_code_uc",
                         time.variable="n_week_end", treatment.identifier=5133302,
                         controls.identifier=control_stores$store_code_uc,
                         time.predictors.prior=seq(14975, 15535, by = 7), time.optimize.ssr=seq(14975, 15535, by = 7),
                         time.plot=seq(14975, 16067, by = 7))

synth_out <-synth(dataprep_out)
```

Plot the synthetic control against the treated store over time. 
```{r fig.width = 8, fig.height = 7}
path.plot(dataprep.res = dataprep_out, synth.res = synth_out, Xlab = c('Time'), Ylab = c('Sales'), tr.intake = 15535,
          Main = 'Synthetic Control and Treated Store Sales')
```

Plot the difference between the treated and synthetic control sales over time. 
```{r, fig.width=8, fig.height=7}
gaps.plot(dataprep.res = dataprep_out, synth.res = synth_out, Ylab = 'Difference', Xlab = 'Weeks', tr.intake = 15535,
          Main = 'Difference Between Treated and Synthetic Sales (Treated - Synthetic)')
```

```{r}
synth_tables <- synth.tab(synth.res = synth_out, dataprep.res = dataprep_out)
synth_tables$tab.w
```

```{r}
synth_tables$tab.pred
```

Create a vector of control sales and weights determined by the data prep. Creat w_ctrl, which is a vector of the weighted control sales. Create a vector of treated sales. Create a tibble with the treated sales and weighted control sales for the pre period. 
```{r}
controls <- dataprep_out$Z0
weights <- synth_tables$tab.w$w.weights
colnames(controls) <- NULL
rownames(controls) <- NULL
w_ctrl <- as.vector(weights %*% t(controls), mode = 'numeric')
treat <- as.vector(dataprep_out$Z1)
weighted_data <- tibble(control = w_ctrl,
                           treated = treat,
                           time = 1:length(w_ctrl))
```

```{r}
weighted_data <- weighted_data %>%
  gather(key = 'Store', value = 'Sales', -time)
```

Create a plot that compares the weighted control sales to the treated sales for the pre period. 
```{r}
weighted_data %>%
  ggplot(aes(x = time, y = Sales, col = Store)) +
  geom_line() +
  labs(x = 'Time',
       y = 'Total Sales',
       title = 'Sales for Treated Store and Synthetic Control Store Pre Treatment')

```

Add the weights for the controls to the dc data frame. Assign a weight of one to the treated store sales. Multiply the weights by the control store sales and sum the sales across the control stores by week. Create a dataframe that has the dates and sales by treated and control store. Add a variable "post" which is a binary variable reporting whether the sales occured pre or post treatment. The implementation date is 7/16/2012. 
```{r}
weight_tibble <- tibble(weight=synth_tables$tab.w$w.weights, store_code_uc=synth_tables$tab.w$unit.names)

dc_data <- dc_data %>% left_join(weight_tibble, "store_code_uc")

dc_data[is.na(dc_data)] <- 1

dc_data <- dc_data %>% mutate(w_sales=sales*weight) %>% 
  mutate(type=if_else(store_code_uc==5133302, 1, 0))

dc_controls <- filter(dc_data, type==0)

dc_controls <- aggregate(dc_controls$w_sales, by=list(dc_controls$week_end),sum)

dc_treats <- filter(dc_data, type==1)

names(dc_controls) <- c("week_end", "w_sales")

dc_controls <- dc_controls %>% mutate(type=0)

dc_treats <- subset(dc_treats, select=c("week_end", "w_sales", "type"))

reg_data <- bind_rows(dc_treats, dc_controls) %>% mutate(post=if_else(week_end > as.Date("2012-07-16"), 1, 0))

names(reg_data) <- c("week_end", "sales", "treat", "post")

```

Run the diff in diff regression. Create a plot for the synthetic control and treated store pre and post category captianship. 
```{r}
did_reg <- lm(sales ~ treat + post + treat * post, data = reg_data)

summary(did_reg)

pre_cc <- reg_data %>%
        filter(week_end <= as.Date("2012-07-16"))
  
post_cc <- reg_data %>%
        filter(week_end > as.Date("2012-07-16"))

did_plot <- ggplot(reg_data, aes(week_end, sales, col = factor(treat))) + 
      geom_line() +
      geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
      geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
      geom_vline(xintercept = as.numeric(as.Date("2012-07-16"))) +
      ggtitle("Synthetic control Diff in Diff for DC Peanut Butter") +labs(x="Time", y="Sales")

print(did_plot)

```

Installl and load microsynth. Create the microsynth weights, plots and results. Save the output as msynth_out. Create a vector of weights called m_weights.  
```{r, fig.width=9, fig.height=4}
#install.packages("microsynth")
library(microsynth)

msynth <- microsynth(dc_data, 
                   idvar="store_code_uc", timevar="n_week_end", intvar="type", 
                   start.pre=14975, end.pre=15535, end.post=16067, 
                   match.out="sales", result.var="sales", omnibus.var="sales", plot.var="sales",
                   test="lower", sep = TRUE)

summary(msynth)

msynth_out <- msynth$w

m_weights <- msynth_out$Weights


```





















