---
title: "Aseptic Juice Data Cleaning"
author: "Cameron Bale"
date: "8/28/2019"
output: github_document
---

Load library.
```{r}
library(plyr)
library(tidyverse)
library(lubridate)
library(readxl)
```

Create `juice_files`, which contains a list of all files contained in the `AsepticJuice_2011-13.tgz` file. Untar the
`.tgz` file. Read in the stores and rms files for 2011, and the products master file. Loop over the file names in
`juice_files` and if it is a 2011 movement file, join it to the stores file on `store_code_uc`, filter for channel code
`'F'` (food) and for the states North Dakota, Minnesota, Missouri, and Illinois (`'ND', 'MN', 'MO', 'IL'`). Then join
the file to the rms versions file on the upc code, and then join it to the products file on the upc code and the upc
version. Bind each individual 2011 movement file together into one file.
```{r}
juice_files <- untar('AsepticJuice_2011-13.tgz', list = TRUE)

untar('AsepticJuice_2011-13.tgz')

stores_11 <- read_tsv('nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv')

rms_11 <- read_tsv('nielsen_extracts/RMS/2011/Annual_Files/rms_versions_2011.tsv')

products <- read_tsv('nielsen_extracts/RMS/Master_Files/Latest/products.tsv', quote = '')

full_11 <- tibble()

for (i in seq_along(juice_files)) {
  
  if (substr(juice_files[i], 22, 40) == "2011/Movement_Files") {
    
    temp_move_11 <- read_tsv(juice_files[i]) %>%
      left_join(stores_11, by = 'store_code_uc') %>%
      filter(channel_code == 'F' & fips_state_descr %in% c('ND', 'MN', 'MO', 'IL')) %>%
      left_join(rms_11, by = 'upc') %>%
      left_join(products, by = c('upc', 'upc_ver_uc'))
    
    full_11 <- full_11 %>%
      bind_rows(temp_move_11)
      
    rm(temp_move_11)
      
  }
  
}

save(full_11, file = 'full_11.RData')

rm(full_11, rms_11, stores_11)
```

Read in files for 2012 the same way as for 2011, and create `full_12` the same way as `full_11`.
```{r}
stores_12 <- read_tsv('nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv')

rms_12 <- read_tsv('nielsen_extracts/RMS/2012/Annual_Files/rms_versions_2012.tsv')

full_12 <- tibble()

for (i in seq_along(juice_files)) {
  
  if (substr(juice_files[i], 22, 40) == "2012/Movement_Files") {
    
    temp_move_12 <- read_tsv(juice_files[i]) %>%
      left_join(stores_12, by = 'store_code_uc') %>%
      filter(channel_code == 'F' & fips_state_descr %in% c('ND', 'MN', 'MO', 'IL')) %>%
      left_join(rms_12, by = 'upc') %>%
      left_join(products, by = c('upc', 'upc_ver_uc'))
    
    full_12 <- full_12 %>%
      bind_rows(temp_move_12)
      
    rm(temp_move_12)
      
  }
  
}

save(full_12, file = 'full_12.RData')

rm(full_12, rms_12, stores_12)
```

Read in files for 2013 the same way as for 2011 and 2012, and create `full_13` the same way as `full_12` and `full_11`.
```{r}
stores_13 <- read_tsv('nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv', guess_max = 20000)

rms_13 <- read_tsv('nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2013.tsv')

full_13 <- tibble()

for (i in seq_along(juice_files)) {
  
  if (substr(juice_files[i], 22, 40) == "2013/Movement_Files") {
    
    temp_move_13 <- read_tsv(juice_files[i]) %>%
      left_join(stores_13, by = 'store_code_uc') %>%
      filter(channel_code == 'F' & fips_state_descr %in% c('ND', 'MN', 'MO', 'IL')) %>%
      left_join(rms_13, by = 'upc') %>%
      left_join(products, by = c('upc', 'upc_ver_uc'))
    
    full_13 <- full_13 %>%
      bind_rows(temp_move_13)
      
    rm(temp_move_13)
      
  }
  
}

rm(products, rms_13, stores_13, juice_files)
```

Read in file containing the manufacturer upc prefixes. The captain and validator for juice are Kraft Heinz and
Coca-Cola, respectively. Create separate vectors with the upc prefixes for both Kraft Heinz and Coca-Cola called
`kraft_prefs` and `coke_prefs`.
```{r}
prefixes <- read_xlsx('Manufacturer UPC Prefixes - From GS1 Company Database.xlsx')

kraft_prefs <- prefixes %>%
  filter(manufacturer == 'Kraft Heinz') %>%
  select(prefix) %>%
  pull()

coke_prefs <- prefixes %>%
  filter(manufacturer == 'Coca-Cola') %>%
  select(prefix) %>%
  pull()
```

Create `full_juice` by combining the data for 2011, 2012, 2013. Convert `week_end` to be a date variable. Create
`sales` by multiplying `units` and `price`. Create `manufacturer` by assigning the correct manufacturer based on upc
prefixes. We assign Kraft Heinz, Coca-Cola, Private Label, and upcs belonging to any other manufacturers fall under 
'other'.
```{r}
load(file = 'full_11.RData')
load(file = 'full_12.RData')

full_juice <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end),
         sales = units * price,
         manufacturer = if_else(grepl(paste(kraft_prefs, collapse = '|'), upc), 'Kraft Heinz',
                        if_else(grepl(paste(coke_prefs, collapse = '|'), upc), 'Coca-Cola',
                        if_else(brand_descr == 'CTL BR', 'Private Label', 'Other', missing = 'Other'))))

rm(full_11, full_12, full_13, prefixes, coke_prefs, kraft_prefs)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than the number of years in the data, and store those
codes in the vector `missing_stores`.
```{r}
missing_stores <- full_juice %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < length(unique(year(full_juice$week_end)))) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_juice %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_juice %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Filter for the store codes that do not switch retailer or parent codes and are not missing from one of the years.
Replace missing `retailer_code` values with the `parent_code`.
```{r}
full_juice <- full_juice %>%
  filter(!store_code_uc %in% unique(c(parent_switchers, retailer_switchers, missing_stores))) %>%
  mutate(retailer_code = if_else(is.na(retailer_code), parent_code, retailer_code))

rm(parent_switchers, retailer_switchers, missing_stores)
```

Create `multi_brand_descr` which contains the upc codes that have multiple brand descriptions. We assume that upc codes
with one valid brand description and an `NA` value as the other description actually have the same description and are
the same product. Create `non_na_descr` which contains the upc codes that have multiple brand descriptions that don't
include an `NA` value. Filter `full_juice` for the upc codes that have multiple valid brand descriptions and compare
them to see if the upc code was used for different products belonging to different manufacturers. All the upc codes in
this category that had multiple brand descriptions were the same product, they just had a slight change in how the
`brand_descr` was entered.
```{r}
multi_brand_descr <- full_juice %>%
  distinct(upc, brand_descr) %>%
  group_by(upc) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  select(upc) %>%
  pull()

non_na_descr <- full_juice %>%
  filter(upc %in% multi_brand_descr) %>%
  distinct(upc, brand_descr) %>%
  arrange(upc) %>%
  filter(!is.na(brand_descr)) %>%
  group_by(upc) %>%
  summarize(n = n()) %>%
  filter(n > 1) %>%
  select(upc) %>%
  pull()

full_juice %>%
  filter(upc %in% non_na_descr) %>%
  distinct(upc, brand_descr) %>%
  arrange(upc)
```

Check if there are private label products with `NA` brand description values, which we should change to `'CTL BR'` so
that they are aggregated under the correct manufacturer. Change `NA` brand descriptions for private label products. 
```{r}
full_juice %>%
  filter(upc %in% multi_brand_descr) %>%
  distinct(upc, brand_descr) %>%
  arrange(upc)

# there are no private label upcs with `na` brand descriptions so we don't need to run the rest of this chunk

#priv_lab_na <- full_juice %>%
#  filter(upc %in% multi_brand_descr) %>%
#  distinct(upc, brand_descr) %>%
#  filter(brand_descr == 'CTL BR') %>%
#  select(upc) %>%
#  pull()

#full_juice <- full_juice %>%
#  mutate(brand_descr = if_else(upc %in% priv_lab_na, 'CTL BR', brand_descr))
```

Split `full_juice` into separate `tibbles` for each state and save the `tibble` for each state.
```{r}
states <- c('ND', 'MN', 'MO', 'IL')

for (state in seq_along(states)) {
  
  state_df <- full_juice %>%
    filter(fips_state_descr == states[state])
  
  save(state_df, file = paste0(states[state], '_data.RData'))
  
  rm(state_df)
  
}
```

Due to the size of the data, we impute the weeks with zero sales for each state `tibble` separately. Create `full_weeks`
which contains each unique `week_end` value. Remove `full_juice` to free up memory. For each state, the loop reads in
the state's `tibble`, splits it at the store and upc level, then for each upc in each store adds observations showing 
the weeks that a given upc had zero sales. Then, bind all the separate store and upc `tibbles` back into one.
```{r}
full_weeks <- full_juice %>%
  distinct(week_end)

rm(full_juice)

for (state in seq_along(states)) {
  
  load(paste0(states[state], '_data.RData'))

  state_df <- state_df %>%
    group_split(store_code_uc, upc)

  for (i in 1:length(state_df)) {
  
    if(nrow(state_df[[i]]) < length(full_weeks$week_end)) {
  
    vars_vec <- state_df[[i]][1,]
  
    missing_weeks <- full_weeks %>%
        anti_join(state_df[[i]], by = 'week_end') %>%
        pull()
  
    missing_data <- matrix(nrow = length(missing_weeks),
                           ncol = length(vars_vec)
                           )
  
    missing_data <- map_df(1:length(missing_weeks), function(y) missing_data[y,] <- vars_vec)
  
    missing_data['week_end'] <- missing_weeks
  
    missing_data['price'] <- NA
  
    missing_data[c('units', 'sales')] <- 0
    
    state_df[[i]] <- state_df[[i]] %>%
      bind_rows(missing_data)
  
    }
    
  }
    
  state_df <- bind_rows(state_df)
  
  save(state_df, file = paste0(states[state], '_data_zeros.RData'))
  
  rm(state_df)
  
}

rm(list = ls())
```

Read in and combine each state `tibble` back into one `tibble`.
```{r}
states <- c('ND', 'MN', 'MO', 'IL')

full_juice <- tibble()

for (state in seq_along(states)) {
  
  load(file = paste0(states[state], '_data_zeros.RData'))
  
  full_juice <- full_juice %>%
    bind_rows(state_df)
  
  rm(state_df)
  
}
```

Check that all upc codes have observations for the full time period and that none have more observations than they 
should.
```{r}
full_juice %>%
  group_by(store_code_uc, upc) %>%
  summarize(n_weeks = n()) %>%
  filter(n_weeks < length(unique(full_juice$week_end)) |
         n_weeks > length(unique(full_juice$week_end)))
```

Create numeric `week_end` variable `n_week_end`.
```{r}
full_juice <- full_juice %>%
  mutate(n_week_end = as.numeric(week_end))
```

Save the cleaned data and save files for each state. 
```{r}
save(full_juice, file = 'juice_clean.RData')

mn_juice <- full_juice %>% filter(fips_state_descr == 'MN')

full_juice <- full_juice %>%
  filter(fips_state_descr %in% c('ND', 'IL', 'MO'))

save(mn_juice, file="mn_juice_clean.RData")

rm(mn_juice)

mo_juice <- full_juice %>% filter(fips_state_descr == 'MO')

full_juice <- full_juice %>%
  filter(fips_state_descr %in% c('ND', 'IL'))

save(mo_juice, file = 'mo_juice_clean.RData')

rm(mo_juice)

nd_juice <- full_juice %>% filter(fips_state_descr == 'ND')

save(nd_juice, file="nd_juice_clean.RData")

rm(nd_juice)

il_juice <- full_juice %>% filter(fips_state_descr == 'IL')

save(il_juice, file="il_juice_clean.RData")

rm(list = ls())
```