---
title: "Minnesota Pickles/Olives"
output: word_document
---


Note: This document contains all the code used to merge and clean data, and then produce graphs. Documents in the Pickles and Olives category for the
North Dakota, Missouri, and DC areas only contain the code used to produce the graphs.

Install library.

```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```


Load library and increase memory limit.

```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```


Unzip file, then read in files for 2011 using a for loop which reads in a file if it is a 2011 movement file and binds each of the separate files
into one.

```{r}
pick_olive_files <- untar("Pickles_Olives.tgz", list = TRUE)

untar("Pickles_Olives.tgz")

move_11 <- tibble()

for (i in seq_along(pick_olive_files)) {
  
  if (substr(pick_olive_files[i], 22, 40) == "2011/Movement_Files") {
    
    temp_move_11 <- read_tsv(pick_olive_files[i])
    
      move_11 <- move_11 %>%
      
        bind_rows(temp_move_11)
      
      rm(temp_move_11)
  }
  
}
```


Read in files for 2012 using a for loop which reads in a file if it is a 2012 movement file and binds each of the separate files
into one.

```{r}
move_12 <- tibble()

for (i in seq_along(pick_olive_files)) {
  
  if (substr(pick_olive_files[i], 22, 40) == "2012/Movement_Files") {
    
    temp_move_12 <- read_tsv(pick_olive_files[i])
    
      move_12 <- move_12 %>%
      
        bind_rows(temp_move_12)
      
      rm(temp_move_12)
  }
}
```


Read in files for 2013 using a for loop which reads in a file if it is a 2013 movement file and binds each of the separate files
into one.

```{r}
move_13 <- tibble()

for (i in seq_along(pick_olive_files)) {
  
  if (substr(pick_olive_files[i], 22, 40) == "2013/Movement_Files") {
    
    temp_move_13 <- read_tsv(pick_olive_files[i])
    
      move_13 <- move_13 %>%
      
        bind_rows(temp_move_13)
      
      rm(temp_move_13)
  }
}
```


Read in stores file for each year and the products file.

```{r}
stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", col_types = list(col_double(), col_double(),
                        col_double(), col_double(), col_character(), col_character(), col_double(), col_character(), col_double(),
                        col_character(), col_double(), col_character()))

products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote = "")
```


Merge the data from the 'stores' files and the 'products' master file to the movement files. Filter for channel code
'F', which denotes 'Food' and 
for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).
Save as 'full_11/12/13'.

```{r}
full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

full_13 <- move_13 %>%
  inner_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")
```


Merge 'full_11/12/13' into one file 'full_11_12_13' and change the 'week_end' variable to 'year-month-day' format 
and create sales variable which is units * price.

```{r}
full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)
```


Create tbls containing each distinct store code ('store_id_11/12/13'). Anti join those three tbls to get 6 tbls containing just the stores that 
only show up in 1 of the 2 years ex:'in_11_not_12'. Anti join those  tbls with the full movement file to remove the stores that only appear in 1
of 2 years. Create a new variable 'manuf_name' which contains the first 3 characters of the brand_name and allows for easy identification of the 
manufacturers. Save the full movement file and clear unnecessary files from memory.

```{r}
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)
store_id_13 <- distinct(full_13, store_code_uc)

in_11_not_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
in_11_not_13 <- anti_join(store_id_11, store_id_13, by = "store_code_uc")
in_12_not_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")
in_12_not_13 <- anti_join(store_id_12, store_id_13, by = "store_code_uc")
in_13_not_11 <- anti_join(store_id_13, store_id_11, by = "store_code_uc")
in_13_not_12 <- anti_join(store_id_13, store_id_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  anti_join(in_11_not_12, by = "store_code_uc") %>%
  anti_join(in_11_not_13, by = "store_code_uc") %>%
  anti_join(in_12_not_11, by = "store_code_uc") %>%
  anti_join(in_12_not_13, by = "store_code_uc") %>%
  anti_join(in_13_not_11, by = "store_code_uc") %>%
  anti_join(in_13_not_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  mutate(manuf_name = substr(full_11_12_13$brand_descr, 1, 3))

rm(full_11, full_12, full_13, in_11_not_12, in_11_not_13, in_12_not_11, in_12_not_13, in_13_not_11, in_13_not_12, move_11,
   move_12, move_13, store_id_11, store_id_12, store_id_13, stores_11, stores_12, stores_13, products, i, pick_olive_files)
```


Create vector 'stores' that contains each distinct store in the full movement file (containing data for all years). Define a vector 'retail_switchers' that will contain the codes
for every store that switches retail codes between 2011, 2012, or 2013. The 'for' loop finds these codes and stores them in 'retail_switchers'.

```{r}
stores <- unique(full_11_12_13$store_code_uc)

retail_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$retailer_code)
  
  if (length(switcher_test) > 1) {
    
    retail_switchers <- append(retail_switchers, stores[i])
    
  }
}
```


Define a vector 'parent_switchers' that will contain the codes for every store that switches parent codes between 2011, 2012, or 2013. The 'for' loop
finds these codes and stores them in 'parent_switchers'.

```{r}
parent_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$parent_code)
  
  if (length(switcher_test) > 1) {
    
    parent_switchers <- append(parent_switchers, stores[i])
    
  }
}
```


Print 'retail_switchers' and 'parent_switchers'.

```{r}
retail_switchers

parent_switchers
```


Create tbl 'switchers' that contains the data for every store that switches retail or parent codes. Filter out these stores from the full movement file.

```{r}
switchers <- full_11_12_13 %>%
  filter(store_code_uc %in% retail_switchers | store_code_uc %in% parent_switchers)

full_11_12_13 <- full_11_12_13 %>%
  anti_join(switchers, by = "store_code_uc")

save(full_11_12_13, file = "full_11_12_13.RData")

rm(switchers, i, parent_switchers, retail_switchers, stores, switcher_test, ind_store_sales)
```


Read in 'brands' file which contains the parent companies of all brands listed in 'full_11_12_13'.

```{r}
brands <- read_csv("pick_olive_brands.csv")
```


Create 'pin' and 'musco_foods' which contain the brands owned by pinnacle and musco. Create tbl 'main_manuf_sales' which contains movement data for the brands owned
by Musco, Pinnacle, and private label. Create a new variable 'actual_manuf' which denotes ownership by either pinnacle or private label, since there are no sales in the file for musco.
This allows for sales across different brands to be aggregated later to sales by manufacturer.

```{r}
pin_foods <- brands %>%
  filter(Manuf == "Pinnacle")

musco_foods <- brands %>%
  filter(Manuf == "Musco")

main_manuf_sales <- full_11_12_13 %>%
  filter(manuf_name %in% c("EAR", "PEA", "GRE", "HOM", "BLA", "VLA", "NAL", "CTL") | 
         brand_descr %in% c("FARMER'S GARDEN", "MEDITERRANEAN PEARLS")) %>%
  mutate(actual_manuf = if_else(manuf_name == "EAR", "MUSCO", if_else(manuf_name == "PEA", "MUSCO", if_else(manuf_name == "GRE", "MUSCO",
                        if_else(manuf_name == "HOM", "MUSCO", if_else(manuf_name == "BLA", "MUSCO", if_else(manuf_name == "VLA", "PIN",
                        if_else(manuf_name == "NAL", "PIN", if_else(brand_descr == "FARMER'S GARDEN", "PIN",
                        if_else(brand_descr == "MEDITERRANEAN PEARLS", "MUSCO", "CTL"))))))))))
```


Filter 'main_manuf_sales' for observations where 'retailer_code' != NA and save as tbl 'retail_no_NA'. 
Filter 'main_manuf_sales' for observations where 'retailer_code' = NA and impute 'parent_code' to replace those values, then recombine with the
observations that originally had a 'retailer_code'.

```{r}
retail_no_NA <- main_manuf_sales %>%
  filter(!is.na(retailer_code))

main_manuf_sales <- main_manuf_sales %>%
  filter(is.na(retailer_code)) %>%
  mutate(retailer_code = parent_code) %>%
  bind_rows(retail_no_NA)

rm(retail_no_NA)

save(main_manuf_sales, file = "main_manuf_sales.RData")
```


Create 'retailer_weekly', which is filtered for retailers in Minnesota, grouped by retailer code, brand_name, and week_end, creating weekly sales
and average prices by manufacturer within retailer. 'ret_codes' contains each unique retailer code. 
The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average
weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the 
approximate CC implementation date. Each graph includes year specific regression lines.


```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-10-08"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-10-08"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-10-08")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-10-08")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```


captain: pinnacle
validator: musco