---
title: "Minnesota Cereal Sales Retailer Test"
author: "Morgan Bale"
date: "5/13/2019"
output: github_document
---

Install and load packages. 
```{r}
#install.packages(c("tidyverse", "microsynth"))
library(tidyverse)
library(microsynth)
library(lubridate)
```

Load in the data for Minnesota cereal category.  
```{r}
load("../../../../mn_cereal_clean.RData")
```

Assign the manfacturer (Private Label, General Mills, Kellogs) for each brand. Convert store code to be a numeric. Organize data by retailer, stores and date, then sum sales across UPCs, giving us weekly sales for each manufacturer in each store in each retailer.
```{r}
mn_data <- mn_data %>%
  mutate(long_brand_descr = substr(mn_data$brand_descr, 1, 6))

mn_data <- mn_data %>%
  filter(manuf_name %in% c("G M", "ANN", "CAS", "KEL", "KAS", "CTL") | long_brand_descr == "BEAR N") %>%
  mutate(actual_manuf = if_else(manuf_name == "G M", "G M", if_else(manuf_name == "ANN", "G M", if_else(manuf_name == "CAS", "G M", 
                        if_else(manuf_name == "KEL", "KEL", if_else(manuf_name == "KAS", "KEL", if_else(manuf_name == "BEA", "KEL", "CTL")))))))

mn_data <- mn_data %>% 
  group_by(retailer_code, store_code_uc, actual_manuf, week_end) %>% 
  summarize(sales=sum(sales)) %>%
  arrange(store_code_uc, week_end) 
```

Check store codes to see how many weeks they have. Stores with less than 157 weeks of observations are dropped
from the data. Then we arrange by `store_code_uc` and `week_end`, then create a `n_week_end` variable to represent
the date numerically. Change manufacter variable to be numeric. 
```{r}
weeks <- unique(mn_data$week_end)

codes <- unique(mn_data$store_code_uc)

drops <- c()

for (i in seq_along(codes)) {
  
  single_store <- mn_data %>% filter(store_code_uc==codes[i])
  
  single_store_vec <- unique(single_store$week_end)
  
  if (length(single_store_vec) < length(weeks)) {
    
    drops <- c(drops, codes[i])
    
  }

}

mn_data <- mn_data %>% 
  filter(!store_code_uc %in% drops) %>% 
  arrange(retailer_code, store_code_uc, week_end) %>%
  mutate(n_week_end=as.numeric(week_end))

mn_data <- mn_data %>% 
  mutate(manuf=if_else(actual_manuf=="CTL", 1, 
               if_else(actual_manuf=="KEL", 2, 3)))
```

To analyze at the manufacturer level, we need to remove manufacturers that don't have sales in the full time period
because it causes an error in Microsynth. This code loops over every store, and for every store it loops over each
manufacturer and removes that manufacturer in that store if it doesn't have sales for the full time period.
```{r}
manuf_codes <- unique(mn_data$manuf)
store_codes <- unique(mn_data$store_code_uc)
mn_cleaned_manufs <- tibble()

for (i in seq_along(store_codes)) {
  
  manuf_drops <- c()
  
  one_store <- mn_data %>%
    filter(store_code_uc == store_codes[i])
  
  for (j in seq_along(manuf_codes)) {
    
    single_manuf <- one_store %>%
      filter(manuf == manuf_codes[j])
    
    manuf_weeks <- unique(single_manuf$week_end)
    
    if (length(manuf_weeks) < length(weeks)) {
      
      manuf_drops <- c(manuf_drops, manuf_codes[j])
      
    }
    
  }
  
  one_store <- one_store %>%
    filter(!manuf %in% manuf_drops)
  
  mn_cleaned_manufs <- mn_cleaned_manufs %>%
    bind_rows(one_store)
  
}
```

Create a vector of the unique retailer codes in MN Data. Create a loop that creates a synthetic control for each manufacturer in each store for each retailer. Collect the p values and treatment effects from each synthetic control. The target reset date was 01/01/2012, we chose the implementation date for the week after (since 01/01 isn't an option), which was 01/07/2012.
```{r message=FALSE, warning=FALSE}
ret_codes <- unique(mn_cleaned_manufs$retailer_code)
msynth_results <- tibble()

for (i in seq_along(ret_codes)) {
  
  msynth_pvals <- c()
  
  msynth_effects <- c()
  
  t_stores <- mn_cleaned_manufs %>% 
    filter(retailer_code==ret_codes[i]) 
  
  c_stores <- mn_cleaned_manufs %>% 
    filter(retailer_code!=ret_codes[i]) %>% 
    mutate(type = 0) 
  
  t_store_codes <- unique(t_stores$store_code_uc)
  
  for (j in seq_along(t_store_codes)) {
    
    store <- t_stores %>% 
      filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = 1)
    
    store_data <- store %>% 
      bind_rows(c_stores)
    
    manufs <- unique(store$manuf)
    
    for (k in seq_along(manufs)) {
      
      manuf_data <- store_data %>%
        filter(manuf == manufs[k])
      
      msynth <- microsynth(data = as.data.frame(manuf_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15346, 
                           end.post = 16067,
                           match.out = "sales",
                           match.covar = "sales",
                           result.var="sales", 
                           omnibus.var="sales",
                           test="twosided", 
                           use.survey = FALSE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
    
  }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = ret_codes[i])
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plotting distributions of p-values and effects at the Manufacturer level.
```{r}
msynth_results %>%
  ggplot(aes(x = pval)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) + labs(x="P-Value", y="Count", title="Manufacturer Level P-Values for MN Cereal")
```

Plot the distribution of treatment effects at the manufacturer level.
```{r}
msynth_results %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) + labs(x="Treatment Effect", y="Count", title="Manufacturer Level Treatment Effects for MN Cereal")
```

Aggregate sales across stores. Create a loop that creates a synthetic control for each store in each retailer. Collect the p values and treatment effects from each synthetic control.  
```{r, message=FALSE, warning=FALSE}
mn_store_data <- mn_data %>% group_by(retailer_code, store_code_uc, n_week_end) %>% summarise(sales=sum(sales))

msynth_results <- tibble()
loop_results <- c()

for (i in seq_along(ret_codes)) {
  msynth_pvals <- c()
  msynth_effects <- c()
  t_stores <- mn_store_data %>% filter(retailer_code==ret_codes[i]) 
  c_stores <- mn_store_data %>% filter(retailer_code!=ret_codes[i]) %>% mutate(type=0) 
  t_store_codes <- unique(t_stores$store_code_uc)
  for (j in seq_along(t_store_codes)) {
    store <- t_stores %>% filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = 1)
    store_data <- bind_rows(store, c_stores)
      msynth <- microsynth(data = as.data.frame(store_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15346, 
                           end.post = 16067,
                           match.out = "sales",
                           match.covar = "sales",
                           result.var="sales", 
                           omnibus.var="sales",
                           test="twosided",
                           use.survey = FALSE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = ret_codes[i]
  )
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plotting distributions of p-values and effects at the store level.
```{r}
msynth_results %>%
  ggplot(aes(x = pval)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) + labs(x="P-Value", y="Count", title="Store Level P-Values for Retailers in MN Cereal")
```

```{r}
msynth_results %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) + labs(x="Treatment Effect", y="Count", title="Store Level Treatment Effects for MN Cereal")
```

Plot only statistically significant effects for stores.
```{r}
msynth_results %>%
  filter(pval < 0.05) %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) + labs(x="Treatment Effect", y="Count", title="Store Level Treatment Effects for MN Cereal", subtitle = "Statistically Significant")
```

Check for retailers that only have one store, as this produces as error in Microsynth.
```{r}
retailers <- unique(mn_store_data$retailer_code)
small_rets <- c()
n_stores <- c()

for (i in seq_along(retailers)) {
  
  single_retailer <- mn_store_data %>%
    filter(retailer_code == retailers[i])
  
  n_stores <- c(n_stores, length(unique(single_retailer$store_code_uc)))
    
}

(num_stores <- tibble(
  Number_Stores = n_stores,
  Retailer = retailers
))
```

Create `ret_code_combo` that pairs each retailer with each other retailer, giving each the possibility to be the treated retailer code. Use `mn_store_data` which is aggregated across stores. Empty the the results, pvals, and effects. Remove the cases where the control retailer only has one store.
```{r}
ret_code_combo <- as_tibble(expand.grid(treat=ret_codes, control=ret_codes)) %>% filter(treat!=control)

ret_code_combo <- ret_code_combo %>%
  filter(!control %in% c(864, 903))
```

Create a loop that runs microsynth for each retailer combination by row from `ret_code_combo`. Collect p-values and treatment effects for each store in each retailer combination. 
```{r, message=FALSE, warning=FALSE}
msynth_results <- tibble()
loop_results <- tibble()

for (i in 1:nrow(ret_code_combo)) {
  msynth_pvals <- c()
  msynth_effects <- c()
  loop_rets <- ret_code_combo %>% filter(row_number()==i) %>% as_vector()
  t_stores <- mn_store_data %>% filter(retailer_code==unname(loop_rets[1])) 
  c_stores <- mn_store_data %>% filter(retailer_code==unname(loop_rets[2])) %>% mutate(type=0) 
  t_store_codes <- unique(t_stores$store_code_uc)
  for (j in seq_along(t_store_codes)) {
    store <- t_stores %>% filter(store_code_uc==t_store_codes[j]) %>% 
      mutate(type = ifelse(n_week_end > 15430, 1, 0))
    store_data <- bind_rows(store, c_stores)
         msynth <- microsynth(data = as.data.frame(store_data),
                           idvar = "store_code_uc",
                           intvar = "type",
                           timevar = "n_week_end",
                           start.pre = 14975, 
                           end.pre = 15346, 
                           end.post = 16067,
                           match.out = "sales",
                           match.out.min = "sales",
                           result.var="sales", 
                           omnibus.var="sales", 
                           test="twosided", 
                           use.survey = FALSE,
                           use.backup = TRUE)
  
  msynth_pvals <- c(msynth_pvals, msynth[[2]]$`16067`[1,4])
  msynth_effects <- c(msynth_effects, msynth[[2]]$`16067`[1,3])
  
    }
  
  loop_results <- tibble(
    pval = msynth_pvals,
    effect = msynth_effects,
    retailer = paste0(unname(loop_rets[1]), ",", unname(loop_rets[2]))
  )
  
  msynth_results <- msynth_results %>%
    bind_rows(loop_results)

}
```

Plot the P-Values for synthetic controls created from every combination of retailers.
```{r fig.width=8, fig.height=7}
msynth_results %>%
  ggplot(aes(x = pval)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) +
  labs(x = 'P-Value',
       y = 'Count',
       title = 'P-Values for Retailer Combinations at the Store Level: MN Cereal')
```

Plot the treatment effects for synthetic controls created from every combination of retailers.
```{r fig.width=9, fig.height=7}
msynth_results %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) +
  labs(x = 'Effect',
       y = 'Count',
       title = 'Treatment Effects for Retailer Combinations at Store Level: MN Cereal')
```

Plot the treatment effects for synthetic controls created from every combination of retailers, but only plot the
treatment effects that are statistically significant.
```{r fig.width=9, fig.height=7}
msynth_results %>%
  filter(pval < 0.05) %>%
  ggplot(aes(x = effect)) +
  geom_histogram() +
  geom_vline(xintercept = 0, col = 'blue') +
  facet_wrap(~retailer) +
  labs(x = 'Effect',
       y = 'Count',
       title = 'Treatment Effects for Retailer Combinations at Store Level: MN Cereal',
       subtitle = 'Statistically Significant Effects')
```


