---
title: "Minnesota Lunch Meat"
output: github_document
---

Note: This document contains all the code used to produce graphs for Minnesota in the lunch meat category. The code for cleaning the data is located in the Lunch Meat Data Cleaning markdown. 

Load the Minnesota lunch meat data file. Read in 'brands' file which contains the parent companies of all brands listed in 'mn_data'.
```{r}
load("mn_lunch_meat_clean.RData")

brands <- read_csv("Lunchmeat Brands - Sheet1.csv")
```


Create 'oscar_mayer' and 'sara_lee' which contain the brands owned by Oscar Mayer and Sara lee. Create tbl 'main_manuf_sales' which contains movement data for the brands owned
by Oscar Mayer, Sara Lee, and Private label. Create a new variable 'actual_manuf' which denotes ownership by either Oscar mayer, Sara Lee, or Private Label.
This allows for sales across different brands to be aggregated later to sales by manufacturer.

```{r}
oscar_mayer <- brands %>%
  filter(Manuf == "Oscar Mayer")

sara_lee <- brands %>%
  filter(Manuf == "Sara Lee")

main_manuf_sales <- full_11_12_13 %>%
  filter(manuf_name %in% c("SAR", "OSC", "CTL") | brand_descr %in% c("HILLSHIRE FARM", "HILLSHIRE FARM GOURMET CREATIN", 
                                                                     "HILLSHIRE FARM DELI SELECT", "HILLSHIRE FARM DELI CARVERS", 
                                                                     "HILLSHIRE FARM LIT'L WIENERS", "HILLSHIRE FARM LIT'L SMOKIES",
                                                                     "HILLSHIRE FARM LIT'L POLSKAS", "HILLSHIRE FARM LIT'L BEEF FRNK",
                                                                     "HILLSHIRE FARM YARD-O-BEEF")) %>%
  mutate(actual_manuf = if_else(manuf_name == "OSC", "OSCMAYER", if_else(manuf_name == "CTL", "CTL", "SARALEE")))
```


Filter 'main_manuf_sales' for observations where 'retailer_code' != NA and save as tbl 'retail_no_NA'. 
Filter 'main_manuf_sales' for observations where 'retailer_code' = NA and impute 'parent_code' to replace those values, then recombine with the
observations that originally had a 'retailer_code'.

```{r}
retail_no_NA <- main_manuf_sales %>%
  filter(!is.na(retailer_code))

main_manuf_sales <- main_manuf_sales %>%
  filter(is.na(retailer_code)) %>%
  mutate(retailer_code = parent_code) %>%
  bind_rows(retail_no_NA)

rm(retail_no_NA)

save(main_manuf_sales, file = "main_manuf_sales.RData")
```


Create 'retailer_weekly', which is filtered for retailers in Minnesota, grouped by retailer code, brand_name, and week_end, creating weekly sales
and average prices by manufacturer within retailer. 'ret_codes' contains each unique retailer code. 
The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average
weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the 
approximate CC implementation date. Each graph includes year specific regression lines.


```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-07-16"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-07-16"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-07-16")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-07-16")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```

Reset Date: July 16, 2012
Captain: Oscar Mayer
Validator: Sara Lee