---
title: "Cereal Data Cleaning"
author: "Morgan Bale"
date: "5/13/2019"
output: github_document
---

Note: This document contains all the code used to merge and clean data for the cereal category. 

Install library.
```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```

Load library and increase memory limit.
```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```

Read in files for 2011.
```{r}
move_11 <- read_tsv("1344_2011.tsv")
stores_11 <- read_tsv("stores_2011.tsv")
products <- read_tsv("products.tsv", quote = "")
#prodex_11 <- read_tsv("products_extra_2011.tsv")
#rms_11 <- read_tsv("rms_versions_2011.tsv")
```

Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code
'F', which denotes 'Food' and for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.). Save as `full_11`.
```{r}
full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

save(full_11, file = "full_11.RData")

rm(move_11, stores_11, full_11)
```

Read in files for 2012.
```{r}
move_12 <- read_tsv("1344_2012.tsv")
stores_12 <- read_tsv("stores_2012.tsv")
#prodex_12 <- read_tsv("products_extra_2012.tsv")
#rms_12 <- read_tsv("rms_versions_2012.tsv")
```

Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code 
'F', which denotes 'Food' and for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.). Save as `full_12`.
```{r}
full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

save(full_12, file = "full_12.RData")

rm(move_12, stores_12)
```

Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code 
'F', which denotes 'Food' and for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.). Save as `full_13`.
```{r}
move_13 <- read_tsv("1344_2013.tsv")
stores_13 <- read_tsv("stores_2013.tsv", col_types = list(col_double(), col_double(),
                                                          col_double(), col_double(), col_character(), col_character(), col_double(), col_character(), col_double(),
                                                          col_character(), col_double(), col_character()))

full_13 <- move_13 %>%
  inner_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

rm(stores_13, products, move_13)
```

Load the `full_11` data file. Combine all three years into one file, `full_11_12_13` containing the data for both years. Change `week_end` variable to year-month-day format. Create variable `sales` which is `units` * `price`.
Create variable for manufacturer from the first 3 digits of the brand description in full combined movement file. Save `full_11_12_13`.
```{r}
load("full_11.RData")

full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)
```

Create tbls containing each distinct store code (`store_id_11/12`). Anti join those two tbls to get two more tbls containing just the stores that only show up in 1 of the 2 years (`not_in_11/12`). Anti join those two tbls with the full movement file to remove the stores that only appear in 1 of 2 years. Create a new variable `manuf_name` which contains the first 3 characters of the brand_name and allows for easy identification of the manufacturers. Save the full movement file.
```{r}
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)
store_id_13 <- distinct(full_13, store_code_uc)

in_11_not_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
in_11_not_13 <- anti_join(store_id_11, store_id_13, by = "store_code_uc")
in_12_not_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")
in_12_not_13 <- anti_join(store_id_12, store_id_13, by = "store_code_uc")
in_13_not_11 <- anti_join(store_id_13, store_id_11, by = "store_code_uc")
in_13_not_12 <- anti_join(store_id_13, store_id_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  anti_join(in_11_not_12, by = "store_code_uc") %>%
  anti_join(in_11_not_13, by = "store_code_uc") %>%
  anti_join(in_12_not_11, by = "store_code_uc") %>%
  anti_join(in_12_not_13, by = "store_code_uc") %>%
  anti_join(in_13_not_11, by = "store_code_uc") %>%
  anti_join(in_13_not_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  mutate(manuf_name = substr(full_11_12_13$brand_descr, 1, 3))

rm(full_11, full_12, full_13, in_11_not_12, in_11_not_13, in_12_not_11, in_12_not_13, in_13_not_11, in_13_not_12,
   store_id_11, store_id_12, store_id_13, i)
```

Create vector `stores` that contains each distinct store in the full movement file. Define a vector `retail_switchers` that will contain the codes for every store that switches retail codes between 2011 and 2012. The 'for' loop finds these codes and stores them in `retail_switchers`.
```{r}
stores <- unique(full_11_12_13$store_code_uc)

retail_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$retailer_code)
  
  if (length(switcher_test) > 1) {
    
    retail_switchers <- append(retail_switchers, stores[i])
    
  }
}
```

Define a vector `parent_switchers` that will contain the codes for every store that switches parent codes between 2011 and 2012. The 'for' loop finds these codes and stores them in `parent_switchers`.
```{r}
parent_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$parent_code)
  
  if (length(switcher_test) > 1) {
    
    parent_switchers <- append(parent_switchers, stores[i])
    
  }
}

```

Print `retail_switchers` and `parent_switchers`.
```{r}
retail_switchers

parent_switchers
```

Create tbl `switchers` that contains the data for every store that switches retail or parent codes. Filter out these stores from the full movement file.
```{r}
switchers <- full_11_12_13 %>%
  filter(store_code_uc %in% retail_switchers | store_code_uc %in% parent_switchers)

full_11_12_13 <- full_11_12_13 %>%
  anti_join(switchers, by = "store_code_uc")
```

Filter `full_11_12_13` for observations where `retailer_code` != NA and save as tbl `retail_no_NA`. 
Filter `full_11_12_13` for observations where `retailer_code` = NA and impute `parent_code` to replace those values, then recombine with the observations that originally had a `retailer_code`.
```{r}
retail_no_NA <- full_11_12_13 %>%
  filter(!is.na(retailer_code))

full_11_12_13 <- full_11_12_13 %>%
  filter(is.na(retailer_code)) %>%
  mutate(retailer_code = parent_code) %>%
  bind_rows(retail_no_NA)
```

Save the cleaned data and save files for each state. 
```{r}
save(full_11_12_13, file="cereal_clean.RData")

mn_data <- full_11_12_13 %>% filter(fips_state_descr=="MN")
dc_data <- full_11_12_13 %>% filter(fips_state_descr=="DC")
mo_data <- full_11_12_13 %>% filter(fips_state_descr=="MO")
nd_data <- full_11_12_13 %>% filter(fips_state_descr=="ND")

save(mn_data, file="mn_cereal_clean.RData")
save(dc_data, file="dc_cereal_clean.RData")
save(mo_data, file="mo_cereal_clean.RData")
save(nd_data, file="nd_cereal_clean.RData")
```

