---
title: "Cereal Data Cleaning"
output: github_document
---

Note: This document contains all the code used to merge and clean data for the cereal category. 

Install library.
```{r eval=FALSE, include=FALSE}
#install.packages("tidyverse")
#install.packages("lubridate")
```

Load library.
```{r}
library(tidyverse)
library(lubridate)
```

Read in files for 2011.
```{r}
move_11 <- read_tsv("1344_2011.tsv")
stores_11 <- read_tsv("stores_2011.tsv")
products <- read_tsv("products.tsv", quote = "")
rms_11 <- read_tsv("rms_versions_2011.tsv")
```

Create `full_11` by joining the data in the stores file to the movement file, filtering for channel code `F` (Food)
and states North Dakota, Minnesota, Missouri, and Illinois. Create `panel_year` variable to merge the rms versions
file to the movement file. Then join the correct upc attributes from the products file to the movement file based on
the upc code and the version from the rms file.
```{r}
full_11 <- move_11 %>%
  left_join(stores_11, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_11, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_11, rms_11, stores_11)
```

Read in files for 2012 and create `full_12` the same way as `full_11`.
```{r}
move_12 <- read_tsv("1344_2012.tsv")
stores_12 <- read_tsv("stores_2012.tsv")
rms_12 <- read_tsv("rms_versions_2012.tsv")

full_12 <- move_12 %>%
  left_join(stores_12, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_12, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_12, stores_12, rms_12)
```

Read in the files for 2013 and create `full_13` the same way as `full_12` and `full_11`.
```{r}
move_13 <- read_tsv("1344_2013.tsv")
stores_13 <- read_tsv("stores_2013.tsv", guess_max = 20000)
rms_13 <- read_tsv("rms_versions_2013.tsv")

full_13 <- move_13 %>%
  left_join(stores_13, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_13, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_13, stores_13, rms_13, products)
```

Combine all three years into one file, `full_data`. Change `week_end` variable to year-month-day format. Create
variable `sales` which is `units` * `price`. Create variable for manufacturer from the first 3 digits of the brand
description.
```{r}
full_data <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), 
         sales = units * price,
         manuf_name = substr(brand_descr, 1, 3))

rm(full_11, full_12, full_13)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than four years, and store those codes in the vector
`missing_stores`.
```{r}
missing_stores <- full_data %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < 3) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_data %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_data %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create one vector with the store codes to remove because they switch retailer or parent codes or they don't show up
in all the years in the data.
```{r}
remove_stores <- unique(c(parent_switchers, retailer_switchers, missing_stores))
```

Using the `remove_stores` vector, filter out the store codes that switch retailer or parent codes or don't show up
in all the years in the data.
```{r}
full_data <- full_data %>%
  filter(!store_code_uc %in% remove_stores)

rm(parent_switchers, retailer_switchers, remove_stores, missing_stores)
```

Use `mutate` to replace missing `retailer_code` values with the `parent_code`.
```{r}
full_data <- full_data %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Save the cleaned data and save files for each state. 
```{r}
save(full_data, file="cereal_clean.RData")

mn_data <- full_data %>% filter(fips_state_descr=="MN")
il_data <- full_data %>% filter(fips_state_descr=="IL")
mo_data <- full_data %>% filter(fips_state_descr=="MO")
nd_data <- full_data %>% filter(fips_state_descr=="ND")

save(mn_data, file="mn_cereal_clean.RData")
save(il_data, file="il_cereal_clean.RData")
save(mo_data, file="mo_cereal_clean.RData")
save(nd_data, file="nd_cereal_clean.RData")
```

