---
title: "Illinois Cereal Data Cleaning"
author: "Cameron Bale"
date: "6/25/2019"
output: html_document
---

Load libraries.
```{r}
library(tidyverse)
library(lubridate)
```

Read in files for 2010.
```{r}
move_10 <- read_tsv("1344_2010.tsv")

stores_10 <- read_tsv("stores_2010.tsv")

products <- read_tsv("products.tsv", quote = "")
```

Merge the data from the `stores` file and the `products` master file to the movement file. Filter for channel code
`F`, which denotes 'Food' and for `fips_state_descr 'IL'` (Illinois).
```{r}
full_10 <- move_10 %>%
  left_join(stores_10, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr == 'IL') %>%
  left_join(products, by ="upc")

rm(move_10, stores_10)
```

Read in files for 2011.
```{r}
move_11 <- read_tsv("1344_2011.tsv")

stores_11 <- read_tsv("stores_2011.tsv")
```

Create `full_11` the same way as `full_10`.
```{r}
full_11 <- move_11 %>%
  left_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr == 'IL') %>%
  left_join(products, by ="upc")

rm(move_11, stores_11)
```

Read in files for 2012.
```{r}
move_12 <- read_tsv("1344_2012.tsv")

stores_12 <- read_tsv("stores_2012.tsv")
```

Create `full_12` the same way as `full_11` and `full_10`.
```{r}
full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr == 'IL') %>%
  inner_join(products, by ="upc")

rm(move_12, stores_12)
```

Create `full_13` the same way as `full_12`, `full_11`, and `full_10`.
```{r}
move_13 <- read_tsv("1344_2013.tsv")

stores_13 <- read_tsv("stores_2013.tsv", guess_max = 20000)

full_13 <- move_13 %>%
  inner_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr == 'IL') %>%
  inner_join(products, by ="upc")

rm(stores_13, products, move_13)
```

Combine `full_10`, `full_11`, `full_12`, and `full_13` into one file, `full_data` containing the data for all years.
Change `week_end` variable to year-month-day format. Create variable `sales` which is `units` * `price`. Create 
variable `manuf_name` from the first three characters of the `brand_descr` (brand description).
```{r}
full_data <- full_10 %>%
  bind_rows(full_11,
            full_12,
            full_13) %>%
  mutate(week_end = ymd(week_end), 
         sales = units * price,
         manuf_name = substr(brand_descr, 1, 3))
```

Create tbls containing each distinct store code (`store_id_11/12/13`). Anti join those three tbls to get 6 tbls containing just the stores that only show up in 1 of the 2 years ex:`in_11_not_12`. Anti join those  tbls with the full movement file to remove the stores that only appear in 1 of 2 years. Create a new variable `manuf_name` which contains the first 3 characters of the brand_name and allows for easy identification of the manufacturers. Clear unnecessary files from memory.
```{r}
store_id_10 <- distinct(full_10, store_code_uc)
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)
store_id_13 <- distinct(full_13, store_code_uc)

in_10_not_11 <- anti_join(store_id_10, store_id_11, by = "store_code_uc")
in_10_not_12 <- anti_join(store_id_10, store_id_12, by = "store_code_uc")
in_10_not_13 <- anti_join(store_id_10, store_id_13, by = "store_code_uc")
in_11_not_10 <- anti_join(store_id_11, store_id_10, by = "store_code_uc")
in_11_not_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
in_11_not_13 <- anti_join(store_id_11, store_id_13, by = "store_code_uc")
in_12_not_10 <- anti_join(store_id_12, store_id_10, by = "store_code_uc")
in_12_not_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")
in_12_not_13 <- anti_join(store_id_12, store_id_13, by = "store_code_uc")
in_13_not_10 <- anti_join(store_id_13, store_id_10, by = "store_code_uc")
in_13_not_11 <- anti_join(store_id_13, store_id_11, by = "store_code_uc")
in_13_not_12 <- anti_join(store_id_13, store_id_12, by = "store_code_uc")

full_data <- full_data %>%
  anti_join(in_10_not_11, by = "store_code_uc") %>%
  anti_join(in_10_not_12, by = "store_code_uc") %>%
  anti_join(in_10_not_13, by = "store_code_uc") %>%
  anti_join(in_11_not_10, by = "store_code_uc") %>%
  anti_join(in_11_not_12, by = "store_code_uc") %>%
  anti_join(in_11_not_13, by = "store_code_uc") %>%
  anti_join(in_12_not_10, by = "store_code_uc") %>%
  anti_join(in_12_not_11, by = "store_code_uc") %>%
  anti_join(in_12_not_13, by = "store_code_uc") %>%
  anti_join(in_13_not_10, by = "store_code_uc") %>%
  anti_join(in_13_not_11, by = "store_code_uc") %>%
  anti_join(in_13_not_12, by = "store_code_uc")

rm(full_10, full_11, full_12, full_13, 
   in_10_not_11, in_10_not_12, in_10_not_13,
   in_11_not_10, in_11_not_12, in_11_not_13, 
   in_12_not_10, in_12_not_11, in_12_not_13, 
   in_13_not_10, in_13_not_11, in_13_not_12,
   store_id_10, store_id_11, store_id_12, store_id_13)
```

Create `retailer_switchers` by getting the distinct combinations of `store_code_uc` and `retailer_code`, grouping by
`store_code_uc`, counting the number of `retailer_code` per `store_code_uc` and filtering for the `store_code_uc`
with more than one `retailer_code`.
```{r}
retailer_switchers <- full_data %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create `parent_switchers` the same way as `retailer_switchers`, except to find the `store_code_uc` that have multiple
`parent_code` values.
```{r}
parent_switchers <- full_data %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parents = n()) %>%
  filter(n_parents > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create `switchers` vector, which contains each unique `store_code_uc` from `parent_switchers` and `retailer_switchers`.
```{r}
switchers <- unique(c(parent_switchers, retailer_switchers))
```

Using the `switchers` vector, filter out the store codes that switch retailer or parent codes.
```{r}
full_data <- full_data %>%
  filter(!store_code_uc %in% switchers)

rm(parent_switchers, retailer_switchers, switchers)
```

Use `mutate` to replace the missing `retailer_code` values with the `parent_code`.
```{r}
full_data <- full_data %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Save the `full_data` file for future use.
```{r}
save(full_data, file = 'il_cereal_clean.RData')
```
