---
title: "Missouri Cereal Graph Analysis"
output: github_document
---

Note: This document contains only the code necessary to produce the graphs. For full code used to merge and clean the data see the cereal cleaning markdown. 

Load library and increase memory limit.
```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```

Load in the data. Read in `brands` file which contains the parent companies of all brands listed in `full_11_12`.
```{r}
load("mo_cereal_clean.RData")

brands <- read_csv("Brands.csv")
```

Create `gm_cereals` and `kel_cereals` which contains the brands owned by General Mills and Kellogg's. Create variable `long_brand_descr` which allows for differentiation between the two brands that both start with `BEAR`. Create tbl `main_manuf_sales` which contains movement data for the brands owned by Kellogg's, General Mills, and the private label. Create a new variable `actual_manuf` which denotes ownership by either General Mills, Kellogg's,
or private label so that sales across different brands can be aggregated later to sales by manufacturer.
```{r}
gm_cereals <- brands %>%
  filter(Manuf == "General Mills")

kel_cereals <- brands %>%
  filter(Manuf == "Kellogg's")

full_11_12 <- full_11_12 %>%
  mutate(long_brand_descr = substr(full_11_12$brand_descr, 1, 6))

main_manuf_sales <- full_11_12 %>%
  filter(manuf_name %in% c("G M", "ANN", "CAS", "KEL", "KAS", "CTL") | long_brand_descr == "BEAR N") %>%
  mutate(actual_manuf = if_else(manuf_name == "G M", "G M", if_else(manuf_name == "ANN", "G M", if_else(manuf_name == "CAS", "G M", 
                        if_else(manuf_name == "KEL", "KEL", if_else(manuf_name == "KAS", "KEL", if_else(manuf_name == "BEA", "KEL", "CTL")))))))
```

Create `retailer_weekly`, which is filtered for retailers in Minnesota, grouped by retailer code, brand_name, and week_end, creating weekly sales and average prices by manufacturer within retailer. `ret_codes` contains each unique retailer code. The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the approximate CC implementation date. Each graph includes year specific regression lines.
```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MO") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(year(week_end) == 2011)
  
  post_cc <- single_ret %>%
        filter(year(week_end) == 2012)
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-01-01")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-01-01")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```