---
title: "Canned Soup Data Cleaning"
output: github_document
---

Note: This document contains all the code used to merge and clean data for the canned soup category. 

Install library.
```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("lubridate")
```

Load library and increase memory limit.
```{r}
library(tidyverse)
library(lubridate)
```

Untar the `canned_soup.tgz` file. Read in the movement, stores, and rms versions files, and the products master file.
```{r}
untar("canned_soup.tgz")

move_11 <- read_tsv("nielsen_extracts/RMS/2011/Movement_Files/0513_2011/1290_2011.tsv")
stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")
products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv" , quote="")
rms_11 <- read_tsv('nielsen_extracts/RMS/2011/Annual_Files/rms_versions_2011.tsv')
```

Create `full_11` by joining the data in the stores file to the movement file, filtering for channel code `F` (Food)
and states North Dakota, Minnesota, Missouri, and Illinois. Create `panel_year` variable to merge the rms versions
file to the movement file. Then join the correct upc attributes from the products file to the movement file based on
the upc code and the version from the rms file.
```{r}
full_11 <- move_11 %>%
  left_join(stores_11, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_11, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_11, rms_11, stores_11)
```

Create `full_12` the same way as `full_11`.
```{r}
move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/0513_2012/1290_2012.tsv" )
stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")
rms_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/rms_versions_2012.tsv")

full_12 <- move_12 %>%
  left_join(stores_12, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_12, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_12, stores_12, rms_12)
```

Create `full_13` the same way as `full_12` and `full_11`.
```{r}
move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/0513_2013/1290_2013.tsv" )
stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", guess_max = 20000)
rms_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2013.tsv")

full_13 <- move_13 %>%
  left_join(stores_13, by = "store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"IL")) %>%
  left_join(rms_13, by = 'upc') %>%
  left_join(products, by = c('upc', 'upc_ver_uc'))

rm(move_13, stores_13, rms_13, products)
```

Combine `full_11`, `full_12`, and `full_13` into one file, `full_11_12_13` containing the data for all years.
Change `week_end` variable to year-month-day format. Create variable `sales` which is `units` * `price`.
```{r}
full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), 
         sales = units * price,
         manuf_name = substr(brand_descr, 1, 3))

rm(full_11, full_12, full_13)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than three years, and store those codes in the vector
`missing_stores`.
```{r}
missing_stores <- full_11_12_13 %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < 3) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_11_12_13 %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_11_12_13 %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create one vector with the store codes to remove because they switch retailer or parent codes.
```{r}
switchers <- unique(c(parent_switchers, retailer_switchers, missing_stores))
```

Using the `switchers` vector, filter out the store codes that switch retailer or parent codes.
```{r}
full_11_12_13 <- full_11_12_13 %>%
  filter(!store_code_uc %in% switchers)

rm(parent_switchers, retailer_switchers, switchers, missing_stores)
```

Use `mutate` to replace the missing `retailer_code` values with the `parent_code`.
```{r}
full_11_12_13 <- full_11_12_13 %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Save the cleaned canned soup data. Filter for each state and save the cleaned state files. 
```{r}
save(full_11_12_13, file="can_soup_clean.RData")

mn_data <- full_11_12_13 %>% filter(fips_state_descr=="MN")
il_data <- full_11_12_13 %>% filter(fips_state_descr=="IL")
mo_data <- full_11_12_13 %>% filter(fips_state_descr=="MO")
nd_data <- full_11_12_13 %>% filter(fips_state_descr=="ND")

save(mn_data, file="mn_can_soup_clean.RData")
save(il_data, file="dc_can_soup_clean.RData")
save(mo_data, file="mo_can_soup_clean.RData")
save(nd_data, file="nd_can_soup_clean.RData")
```

