---
title: "UPC Analysis for Peanut Butter"
author: "Cameron Bale"
date: "August 13, 2018"
output: github_document
---

Install relevant packages.
```{r}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("DT")
```

Load library.
```{r}
library(tidyverse)
library(tibbletime)
library(lubridate)
library(DT)
```

Load in the data set. 
```{r}
load("pb_clean.RData")
```


Create tbl `switchers` that contains the data for every store that switches retail or parent codes. Filter out these stores from the full movement file.
```{r}
switchers <- full_11_12_13 %>%
  filter(store_code_uc %in% retail_switchers | store_code_uc %in% parent_switchers)

full_11_12_13 <- full_11_12_13 %>%
  anti_join(switchers, by = "store_code_uc")

save(full_11_12_13, file = "full_11_12_13.RData")
```

Create vector 'state_abbrevs' containing the FIPS state descriptions for the states where supervalue operates. The for loop creates 'sales', which contains data for an individual state, and 'rets' which contains all distinct retailer codes in that state. The next for loop creates 'ret_sales', which contains weekly sales for an individual retailer. 'avg_sales' takes the individual sales for a retailer and creates a new variable, avg_sales, which is the mean sales amount for each upc sold by that retailer. The loop joins 'ret_sales' and 'avg_sales' by upc and creates scaled_sales, which is the sales amount for each week divided by the products avg_sales. This creates a scaled variable that we can compare across upcs. 'chart_data' is a matrix with weeks as columns, individual upcs as rows, with the inside of the matrix containing the scaled sales for each upc in a given week. The third for loop creates 'single_upc_sales' which contains all the sales for a single upc. 'no_sales' takes all the weeks we have sales data for and anti-joins those weeks with the 'single_upc_sales' to get the weeks where the upc did not sell. It fills in the upc variable with the upc and the scaled sales variable with zero. The loop then binds the weeks where the upc did not sell to the weeks where the upc did sell to create data for the upc over all weeks of interest. It then places the scaled sales for each upc into the 'chart_data' matrix. Round the sales in 'chart_data' to two decimals. Create 'brks' and 'colors' which define _______________________________
Convert 'chart_data' to a tibble and specify to keep the rownames. 'sales_table' places a gradient of color onto 'chart_data' and creates a table we can save as an html file for easy access. All of this is done for every retailer in every state of interest.
```{r}
state_abbrevs <- c("MN", "MO", "ND", "DC")

for (i in seq_along(state_abbrevs)) {
  
  sales <- full_11_12_13 %>%
    filter(fips_state_descr == state_abbrevs[i])
  
  rets <- unique(sales$retailer_code)
  
  for (j in seq_along(rets)) {
    
    ret_sales <- sales %>%
      filter(retailer_code == rets[j]) %>%
      group_by(retailer_code, upc, week_end) %>%
      summarize(total_sales = sum(sales))
    
    avg_sales <- ret_sales %>%
      group_by(retailer_code, upc) %>%
      summarize(avg_sales = mean(total_sales))
    
    ret_sales <- ret_sales %>%
      inner_join(avg_sales, by = c("upc", "retailer_code")) %>%
      mutate(scaled_sales = total_sales / avg_sales) %>%
      ungroup() %>%
      arrange(week_end)
    
    chart_data <- matrix(nrow = n_distinct(ret_sales$upc), ncol = n_distinct(ret_sales$week_end))
    
    colnames(chart_data) <- as.character(paste("week", unique(ret_sales$week_end)))
    
    rownames(chart_data) <- unique(ret_sales$upc)
    
    ind_upcs <- unique(ret_sales$upc)
    
    for (k in seq_along(ind_upcs)) {
      
      single_upc_sales <- ret_sales %>%
        select(upc, week_end, scaled_sales) %>%
        filter(upc == ind_upcs[k])
      
      no_sales <- ret_sales %>%
        distinct(week_end) %>%
        anti_join(single_upc_sales, by = "week_end") %>%
        mutate(upc = ind_upcs[k], scaled_sales = 0)
      
      single_upc_sales <- single_upc_sales %>%
        bind_rows(no_sales) %>%
        arrange(week_end)
      
      chart_data[ind_upcs[k],] <- single_upc_sales$scaled_sales
      
    }
    
    chart_data <- round(chart_data, 2)
    
    brks <- quantile(chart_data, probs = seq(.05, .95, .05), na.rm = TRUE)
    
    clrs <- round(seq(255, 40, length.out = length(brks) + 1), 0) %>% 
    {paste0("rgb(255,", ., ",", ., ")")}
    
    chart_data <- as_tibble(chart_data, rownames = NA)
    
    sales_table <- datatable(chart_data, caption = paste("Peanut Butter Sales for Retailer", rets[j], "in", state_abbrevs[i])) %>% 
      formatStyle(names(chart_data), backgroundColor = styleInterval(brks, clrs))
    
    print(sales_table)
    
  }
  
}
```












