---
title: "Minnesota RTE Cereal"
output: word_document
---


Note: This document contains all the code used to merge and clean data, and then produce graphs. Documents in the RTE cereal category for the
North Dakota, Missouri, and DC areas only contain the code used to produce the graphs.

Install library.

```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```


Load library and increase memory limit.

```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```


Read in files for 2011.

```{r}
move_11 <- read_tsv("1344_2011.tsv")
stores_11 <- read_tsv("stores_2011.tsv")
products <- read_tsv("products.tsv", quote = "")
#prodex_11 <- read_tsv("products_extra_2011.tsv")
#rms_11 <- read_tsv("rms_versions_2011.tsv")
```


Merge the data from the 'stores' file and the 'products' master file to the movement file. Filter for channel code
'F', which denotes 'Food' and 
for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).
Save as 'full_11'.

```{r}
full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

save(full_11, file = "full_11.RData")

rm(move_11, stores_11, full_11)
```


Read in files for 2012.

```{r}
move_12 <- read_tsv("1344_2012.tsv")
stores_12 <- read_tsv("stores_2012.tsv")
#prodex_12 <- read_tsv("products_extra_2012.tsv")
#rms_12 <- read_tsv("rms_versions_2012.tsv")
```


Merge the data from the 'stores' file and the 'products' master file to the movement file. Filter for channel code 
'F', which denotes 'Food' and 
for the 4 states where supervalue operates (North Dakota, Minnesota, Missouri, and D.C.).
Save as 'full_12'.

```{r}
full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

save(full_12, file = "full_12.RData")

rm(move_12, stores_12, products)
```


Load the 'full_11' data file. Combining 'full_11' and 'full_12' into one file, 'full_11_12' containing the data for both years.
Change 'week_end' variable to year-month-day format. Create variable 'sales' which is 'units' * 'price'.
Create variable for manufacturer from the first 3 digits of the brand description in full combined movement file. Save 'full_11_12'.

```{r}
load("full_11.RData")

full_11_12 <- full_11 %>%
  bind_rows(full_12) %>%
  mutate(week_end = ymd(week_end), sales = units * price)
```


Create tbls containing each distinct store code ('store_id_11/12'). Anti join those two tbls to get two more tbls containing just the stores that 
only show up in 1 of the 2 years ('not_in_11/12'). Anti join those two tbls with the full movement file to remove the stores that only appear in 1
of 2 years. Create a new variable 'manuf_name' which contains the first 3 characters of the brand_name and allows for easy identification of the 
manufacturers. Save the full movement file.

```{r}
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)

not_in_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
not_in_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")

full_11_12 <- full_11_12 %>%
  anti_join(not_in_11, by = "store_code_uc") %>%
  anti_join(not_in_12, by = "store_code_uc")

full_11_12 <- full_11_12 %>%
  mutate(manuf_name = substr(full_11_12$brand_descr, 1, 3))

save(full_11_12, file = "full_11_12.RData")

rm(full_11, full_12, not_in_11, not_in_12, store_id_11, store_id_12)
```


Create vector 'stores' that contains each distinct store in the full movement file. Define a vector 'retail_switchers' that will contain the codes
for every store that switches retail codes between 2011 and 2012. The 'for' loop finds these codes and stores them in 'retail_switchers'.

```{r}
stores <- unique(full_11_12$store_code_uc)

retail_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$retailer_code)
  
  if (length(switcher_test) > 1) {
    
    retail_switchers <- append(retail_switchers, stores[i])
    
  }
}
```


Define a vector 'retail_switchers' that will contain the codes for every store that switches parent codes between 2011 and 2012. The 'for' loop
finds these codes and stores them in 'parent_switchers'.

```{r}
parent_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$parent_code)
  
  if (length(switcher_test) > 1) {
    
    parent_switchers <- append(parent_switchers, stores[i])
    
  }
}
```


Print 'retail_switchers' and 'parent_switchers'.

```{r}
retail_switchers

parent_switchers
```


Create tbl 'switchers' that contains the data for every store that switches retail or parent codes. Filter out these stores from the full movement
file.

```{r}
switchers <- full_11_12 %>%
  filter(store_code_uc %in% retail_switchers | store_code_uc %in% parent_switchers)

full_11_12 <- full_11_12 %>%
  anti_join(switchers, by = "store_code_uc")
  
```


Read in 'brands' file which contains the parent companies of all brands listed in 'full_11_12'.

```{r}
brands <- read_csv("Brands.csv")
```


Create 'gm' and 'kel'_cereals which contains the brands owned by General Mills and Kellogg's. Create variable 'long_brand_descr' which allows for 
differentiation between the two brands that both start with 'BEAR'. Create tbl 'main_manuf_sales' which contains movement data for the brands owned
by Kellogg's, General Mills, and the private label. Create a new variable 'actual_manuf' which denotes ownership by either General Mills, Kellogg's,
or private label so that sales across different brands can be aggregated later to sales by manufacturer.

```{r}
gm_cereals <- brands %>%
  filter(Manuf == "General Mills")

kel_cereals <- brands %>%
  filter(Manuf == "Kellogg's")

full_11_12 <- full_11_12 %>%
  mutate(long_brand_descr = substr(full_11_12$brand_descr, 1, 6))

main_manuf_sales <- full_11_12 %>%
  filter(manuf_name %in% c("G M", "ANN", "CAS", "KEL", "KAS", "CTL") | long_brand_descr == "BEAR N") %>%
  mutate(actual_manuf = if_else(manuf_name == "G M", "G M", if_else(manuf_name == "ANN", "G M", if_else(manuf_name == "CAS", "G M", 
                        if_else(manuf_name == "KEL", "KEL", if_else(manuf_name == "KAS", "KEL", if_else(manuf_name == "BEA", "KEL", "CTL")))))))
```


Filter 'main_manuf_sales' for observations where 'retailer_code' != NA and save as tbl 'retail_no_NA'. 
Filter 'main_manuf_sales' for observations where 'retailer_code' = NA and impute 'parent_code' to replace those values, then recombine with the
observations that originally had a 'retailer_code'.

```{r}
retail_no_NA <- main_manuf_sales %>%
  filter(!is.na(retailer_code))

main_manuf_sales <- main_manuf_sales %>%
  filter(is.na(retailer_code)) %>%
  mutate(retailer_code = parent_code) %>%
  bind_rows(retail_no_NA)

save(main_manuf_sales, file = "main_manuf_sales.RData")
```


Create 'retailer_weekly', which is filtered for retailers in Minnesota, grouped by retailer code, brand_name, and week_end, creating weekly sales
and average prices by manufacturer within retailer. 'ret_codes' contains each unique retailer code. 
The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average
weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the 
approximate CC implementation date. Each graph includes year specific regression lines.

```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MN") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(year(week_end) == 2011)
  
  post_cc <- single_ret %>%
        filter(year(week_end) == 2012)
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-01-01")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-01-01")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```