---
title: "Missouri Pickles/Olives"
author: "Cameron Bale + Samuel Sorensen"
date: "August 9, 2018"
output: word_document
---

Load library and increase memory limit.

```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```


Load 'main_manuf_sales' file.

```{r}
load("main_manuf_sales.RData")
```


Create 'retailer_weekly', which is filtered for retailers in Missouri, grouped by retailer code, brand_name, and week_end, creating weekly sales
and average prices by manufacturer within retailer. 'ret_codes' contains each unique retailer code. 
The 'for' loop goes over each unique retailer code and graphs the weekly sales by manufacturer for each retailer code. It also plots the average
weekly price by manufacturer by retailer. It places these graphs next to each other for easy comparison. There is a verticle line at the 
approximate CC implementation date. Each graph includes year specific regression lines.

```{r}
retailer_weekly <- main_manuf_sales %>%
  filter(fips_state_descr == "MO") %>%
  group_by(retailer_code, actual_manuf, week_end) %>%
  summarize(sales = sum(sales), av_price = mean(price))

ret_codes <- unique(retailer_weekly$retailer_code)

for (i in seq_along(ret_codes)) {
  
  single_ret <- retailer_weekly %>%
    filter(retailer_code == ret_codes[i])
  
  pre_cc <- single_ret %>%
        filter(week_end <= as.Date("2012-10-08"))
  
  post_cc <- single_ret %>%
        filter(week_end > as.Date("2012-10-08"))
  
  graph_1 <- ggplot(single_ret, aes(week_end, sales, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + theme(plot.title = element_text(size = 10), legend.position = "bottom", axis.text.y = element_blank(), 
                            axis.ticks.y = element_blank(), 
                            axis.title = element_text(size = 7), axis.text = element_text(size = 7), legend.title = element_text(size = 6),
                            legend.text = element_text(size = 6)) + 
    
    xlab("Date") + ylab("Sales") + labs(color = 'Manuf') + ggtitle(paste("Weekly Sales for Retailer", ret_codes[i])) + 
    
    geom_vline(xintercept = as.numeric(as.Date("2012-10-08")))
  
  graph_2 <- ggplot(single_ret, aes(week_end, av_price, color = actual_manuf)) + geom_line() + 
    
    geom_smooth(aes(week_end, av_price), data = pre_cc, method = 'lm', se = FALSE) +
    
    geom_smooth(aes(week_end, av_price), data = post_cc, method = 'lm', se = FALSE) +
    
    scale_y_log10() + xlab("Date") + ylab("Avg Price") + labs(color = 'Manuf') + 
    
    theme(plot.title = element_text(size = 10), axis.text = element_text(size = 7), 
          axis.title = element_text(size = 7), legend.text = element_text(size = 6), legend.title = element_text(size = 6), 
          
          legend.position = "bottom") +
    ggtitle(paste("Avg Weekly Price for Retailer", ret_codes[i])) + geom_vline(xintercept = as.numeric(as.Date("2012-10-08")))
  
  paired_graph <- plot_grid(graph_1, graph_2)
  
  print(paired_graph)
  
}
```


captain: pinnacle
validator: musco