---
title: "Lunch Meat Data Cleaning"
output: github_document
---

This document contains all the code used to merge and clean data for the Lunch Meat category. It then saves the cleaned lunch meat data file, filters for each state and saves the individual cleaned state data as well.

Load library and increase memory limit.
```{r}
library(tidyverse)
library(lubridate)
```

Unzip file, then read in files for 2011 using a for loop which reads in a file if it is a 2011 movement file and binds each of the separate files into one.
```{r}
lmeat_files <- untar("lunchmeat.tgz", list = TRUE)

untar("lunchmeat.tgz")

move_11 <- tibble()

for (i in seq_along(lmeat_files)) {
  
  if (substr(lmeat_files[i], 22, 40) == "2011/Movement_Files") {
    
    temp_move_11 <- read_tsv(lmeat_files[i])
    
      move_11 <- move_11 %>%
      
        bind_rows(temp_move_11)
      
      rm(temp_move_11)
  }
  
}

products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote = "")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

rms_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/rms_versions_2011.tsv")

full_11 <- move_11 %>%
  left_join(stores_11, by ="store_code_uc") %>%
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO", "IL")) %>%
  left_join(rms_11, by = "upc") %>%
  left_join(products, by = c("upc", "upc_ver_uc"))

rm(move_11, stores_11, rms_11)
```

Read in files for 2012 using a for loop which reads in a file if it is a 2012 movement file and binds each of the separate files into one.
```{r}
move_12 <- tibble()

for (i in seq_along(lmeat_files)) {
  
  if (substr(lmeat_files[i], 22, 40) == "2012/Movement_Files") {
    
    temp_move_12 <- read_tsv(lmeat_files[i])
    
      move_12 <- move_12 %>%
      
        bind_rows(temp_move_12)
      
      rm(temp_move_12)
  }
}

stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

rms_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/rms_versions_2012.tsv")

full_12 <- move_12 %>%
  left_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND","MN","MO","IL")) %>%
  left_join(rms_12, by = "upc") %>%
  left_join(products, by = c("upc", "upc_ver_uc"))

rm(move_12, stores_12, rms_12)
```

Read in files for 2013 using a for loop which reads in a file if it is a 2013 movement file and binds each of the separate files into one.
```{r}
move_13 <- tibble()

for (i in seq_along(lmeat_files)) {
  
  if (substr(lmeat_files[i], 22, 40) == "2013/Movement_Files") {
    
    temp_move_13 <- read_tsv(lmeat_files[i])
    
      move_13 <- move_13 %>%
      
        bind_rows(temp_move_13)
      
      rm(temp_move_13)
  }
}

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", guess_max = 20000)

rms_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2013.tsv")

full_13 <- move_13 %>%
  left_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND","MN","MO","IL")) %>%
  left_join(rms_13, by = "upc") %>%
  left_join(products, by = c("upc", "upc_ver_uc"))

rm(move_13, stores_13, rms_13, products)
```

Combine all three years into one file, `full_data`. Change `week_end` variable to year-month-day format. Create
variable `sales` which is `units` * `price`. Create variable for manufacturer from the first 3 digits of the brand
description.
```{r}
full_data <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), 
         sales = units * price,
         manuf_name = substr(brand_descr, 1, 3))

rm(full_11, full_12, full_13)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than three years, and store those codes in the vector
`missing_stores`.
```{r}
missing_stores <- full_data %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < 3) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_data %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_data %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create one vector with the store codes to remove because they switch retailer or parent codes or they don't show up
in all the years in the data.
```{r}
remove_stores <- unique(c(parent_switchers, retailer_switchers, missing_stores))
```

Using the `remove_stores` vector, filter out the store codes that switch retailer or parent codes or don't show up
in all the years in the data.
```{r}
full_data <- full_data %>%
  filter(!store_code_uc %in% remove_stores)

rm(parent_switchers, retailer_switchers, remove_stores, missing_stores)
```

Use `mutate` to replace missing `retailer_code` values with the `parent_code`.
```{r}
full_data <- full_data %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Save the cleaned lunch meat data file. Filter for each state and save the cleaned data files for each state. 
```{r}
save(full_data, file="lunchmeat_clean.RData")

mn_data <- filter(full_data, fips_state_descr=="MN")
il_data <- filter(full_data, fips_state_descr=="IL")
mo_data <- filter(full_data, fips_state_descr=="MO")
nd_data <- filter(full_data, fips_state_descr=="ND")

save(mn_data, file="mn_lunchmeat_clean.RData")
save(il_data, file="il_lunchmeat_clean.RData")
save(mo_data, file="mo_lunchmeat_clean.RData")
save(nd_data, file="nd_lunchmeat_clean.Rdata")
```


