---
title: "Lunch Meat Data Cleaning"
output: github_document
---

This document contains all the code used to merge and clean data for the Lunch Meat category. It then saves the cleaned lunch meat data file, filters for each state and saves the individual cleaned state data as well. 

Install library.
```{r eval=FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
install.packages("tsoutliers")
install.packages("forecast")
install.packages("rmarkdown")
install.packages("purrr")
install.packages("plyr")
install.packages("cowplot")
```

Load library and increase memory limit.
```{r}
library(cowplot)
library(plyr)
library(tidyverse)
library(tibbletime)
library(lubridate)
library(tsoutliers)
library(forecast)
memory.limit(size = 50000)
```

Unzip file, then read in files for 2011 using a for loop which reads in a file if it is a 2011 movement file and binds each of the separate files into one.
```{r}
lmeat_files <- untar("lunchmeat.tgz", list = TRUE)

untar("lunchmeat.tgz")

move_11 <- tibble()

for (i in seq_along(lmeat_files)) {
  
  if (substr(lmeat_files[i], 22, 40) == "2011/Movement_Files") {
    
    temp_move_11 <- read_tsv(lmeat_files[i])
    
      move_11 <- move_11 %>%
      
        bind_rows(temp_move_11)
      
      rm(temp_move_11)
  }
  
}

products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote = "")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

rm(move_11, stores_11)
```

Read in files for 2012 using a for loop which reads in a file if it is a 2012 movement file and binds each of the separate files into one.
```{r}
move_12 <- tibble()

for (i in seq_along(lmeat_files)) {
  
  if (substr(lmeat_files[i], 22, 40) == "2012/Movement_Files") {
    
    temp_move_12 <- read_tsv(lmeat_files[i])
    
      move_12 <- move_12 %>%
      
        bind_rows(temp_move_12)
      
      rm(temp_move_12)
  }
}

stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

rm(move_12, stores_12)
```

Read in files for 2013 using a for loop which reads in a file if it is a 2013 movement file and binds each of the separate files into one.
```{r}
move_13 <- tibble()

for (i in seq_along(lmeat_files)) {
  
  if (substr(lmeat_files[i], 22, 40) == "2013/Movement_Files") {
    
    temp_move_13 <- read_tsv(lmeat_files[i])
    
      move_13 <- move_13 %>%
      
        bind_rows(temp_move_13)
      
      rm(temp_move_13)
  }
}

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", col_types = list(col_double(), col_double(),
                        col_double(), col_double(), col_character(), col_character(), col_double(), col_character(), col_double(),
                        col_character(), col_double(), col_character()))

full_13 <- move_13 %>%
  inner_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC")) %>%
  inner_join(products, by ="upc")

rm(move_13, stores_13, products)
```

Merge `full_11/12/13` into one file `full_11_12_13` and change the `week_end` variable to `year-month-day` format 
and create sales variable which is units * price.
```{r}
full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)
```

Create tbls containing each distinct store code (`store_id_11/12/13`). Anti join those three tbls to get 6 tbls containing just the stores that only show up in 1 of the 2 years ex:`in_11_not_12`. Anti join those  tbls with the full movement file to remove the stores that only appear in 1 of 2 years. Create a new variable `manuf_name` which contains the first 3 characters of the brand_name and allows for easy identification of the 
manufacturers. Save the full movement file and clear unnecessary files from memory.
```{r}
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)
store_id_13 <- distinct(full_13, store_code_uc)

in_11_not_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
in_11_not_13 <- anti_join(store_id_11, store_id_13, by = "store_code_uc")
in_12_not_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")
in_12_not_13 <- anti_join(store_id_12, store_id_13, by = "store_code_uc")
in_13_not_11 <- anti_join(store_id_13, store_id_11, by = "store_code_uc")
in_13_not_12 <- anti_join(store_id_13, store_id_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  anti_join(in_11_not_12, by = "store_code_uc") %>%
  anti_join(in_11_not_13, by = "store_code_uc") %>%
  anti_join(in_12_not_11, by = "store_code_uc") %>%
  anti_join(in_12_not_13, by = "store_code_uc") %>%
  anti_join(in_13_not_11, by = "store_code_uc") %>%
  anti_join(in_13_not_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  mutate(manuf_name = substr(full_11_12_13$brand_descr, 1, 3))

rm(full_11, full_12, full_13, in_11_not_12, in_11_not_13, in_12_not_11, in_12_not_13, in_13_not_11,
   in_13_not_12, store_id_11, store_id_12, store_id_13, lmeat_files)
```


Create vector `stores` that contains each distinct store in the full movement file (containing data for all years). Define a vector 'retail_switchers' that will contain the codes for every store that switches retail codes between 2011, 2012, or 2013. The `for` loop finds these codes and stores them in `retail_switchers`.
```{r}
stores <- unique(full_11_12_13$store_code_uc)

retail_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$retailer_code)
  
  if (length(switcher_test) > 1) {
    
    retail_switchers <- append(retail_switchers, stores[i])
    
  }
}
```

Define a vector `parent_switchers` that will contain the codes for every store that switches parent codes between 2011, 2012, or 2013. The `for` loop finds these codes and stores them in `parent_switchers`.
```{r}
parent_switchers <- vector("numeric", length = 0)

for (i in seq_along(stores)) {
  
  ind_store_sales <- full_11_12_13 %>%
    filter(store_code_uc == stores[i])
  
  switcher_test <- unique(ind_store_sales$parent_code)
  
  if (length(switcher_test) > 1) {
    
    parent_switchers <- append(parent_switchers, stores[i])
    
  }
}
```

Print `retail_switchers` and `parent_switchers`.
```{r}
retail_switchers

parent_switchers
```

Create tbl `switchers` that contains the data for every store that switches retail or parent codes. Filter out these stores from the full movement file.
```{r}
switchers <- full_11_12_13 %>%
  filter(store_code_uc %in% retail_switchers | store_code_uc %in% parent_switchers)

full_11_12_13 <- full_11_12_13 %>%
  anti_join(switchers, by = "store_code_uc")

save(full_11_12_13, file = "full_11_12_13.RData")

rm(switchers, i, parent_switchers, retail_switchers, stores, switcher_test, ind_store_sales)
```

Filter `main_manuf_sales` for observations where `retailer_code` != NA and save as tbl `retail_no_NA`. Filter `main_manuf_sales` for observations where `retailer_code` = NA and impute `parent_code` to replace those values, then recombine with the observations that originally had a `retailer_code`.
```{r}
retail_no_NA <- full_11_12_13 %>%
  filter(!is.na(retailer_code))

full_11_12_13 <- full_11_12_13 %>%
  filter(is.na(retailer_code)) %>%
  mutate(retailer_code = parent_code) %>%
  bind_rows(retail_no_NA)

rm(retail_no_NA)
```

Save the cleaned lunch meat data file. Filter for each state and save the cleaned data files for each state. 
```{r}
save(full_11_12_13, file="lunchmeat_clean.RData")

mn_data <- filter(full_11_12_13, fips_state_descr=="MN")
dc_data <- filter(full_11_12_13, fips_state_descr=="DC")
mo_data <- filter(full_11_12_13, fips_state_descr=="MO")
nd_data <- filter(full_11_12_13, fips_state_descr=="ND")

save(mn_data, file="mn_lunchmeat_clean.RData")
save(dc_data, file="dc_lunchmeat_clean.RData")
save(mo_data, file="mo_lunchmeat_clean.RData")
save(nd_data, file="nd_lunchmeat_clean.Rdata")
```


