---
title: "Minnesota Frozen Dinners Cleaning"
author: "Cameron Bale"
date: "August 13, 2018"
output: github_document
---


Install packages.
```{r eval =FALSE, include=FALSE}
install.packages("tidyverse")
install.packages("tibbletime")
install.packages("lubridate")
```

Load libraries.
```{r results='hide'}
library(tidyverse)
library(tibbletime)
library(lubridate)
```

Read in the files from the frozen_dinners_entries.tgz for 2011.
```{r}
frozen_dinners_files <- untar("frozen_dinners_entries.tgz", list = TRUE)

untar("frozen_dinners_entries.tgz")

move_11 <- tibble()

for (i in seq_along(frozen_dinners_files)) {
    
    if (substr(frozen_dinners_files[i], 22, 40) == "2011/Movement_Files") {
        
        temp_move_11 <- read_tsv(frozen_dinners_files[i])
        
        move_11 <- move_11 %>%
            
            bind_rows(temp_move_11)
        
        rm(temp_move_11)
    }
    
}

products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote = "")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv") %>%
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO", "IL"))

full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>%
  inner_join(products, by ="upc")

save(full_11, file = 'full_11.RData')

rm(move_11, stores_11, full_11)
```

Read in the files for 2012.
```{r}
move_12 <- tibble()

for (i in seq_along(frozen_dinners_files)) {
    
    if (substr(frozen_dinners_files[i], 22, 40) == "2012/Movement_Files") {
        
        temp_move_12 <- read_tsv(frozen_dinners_files[i])
        
        move_12 <- move_12 %>%
            
            bind_rows(temp_move_12)
        
        rm(temp_move_12)
    }
    
}

stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND","MN","MO","IL"))

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  inner_join(products, by ="upc")

save(full_12, file = 'full_12.RData')

rm(move_12, stores_12, full_12)
```

Read in the files for 2013.
```{r}
move_13 <- tibble()

for (i in seq_along(frozen_dinners_files)) {
    
    if (substr(frozen_dinners_files[i], 22, 40) == "2013/Movement_Files") {
        
        temp_move_13 <- read_tsv(frozen_dinners_files[i])
        
        move_13 <- move_13 %>%
            
            bind_rows(temp_move_13)
        
        rm(temp_move_13)
    }
    
}

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", guess_max = 20000) %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND","MN","MO","DC"))

full_13 <- move_13 %>%
  inner_join(stores_13, by ="store_code_uc") %>% 
  inner_join(products, by ="upc")

rm(move_13, stores_13, products)

load('full_11.RData')
load('full_12.RData')
```

Merge the full file for each year into one file `full_11_12_13` and change the `week_end` variable to `year-month-day` format. Create sales variable which is `units` * `price`.
```{r}
full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)
```

Create tbls containing each distinct store code (ex: `store_id_11`). Anti-join those three tbls to get 6 tbls
containing the stores that don't show up in all of the years ex:`in_11_not_12`. Anti join those  tbls with the full movement file to remove the stores that don't show up in all of the years. Create a new variable `manuf_name` which contains the first 3 characters of the `brand_descr` and allows for easy identification of the manufacturers.
```{r}
store_id_11 <- distinct(full_11, store_code_uc)
store_id_12 <- distinct(full_12, store_code_uc)
store_id_13 <- distinct(full_13, store_code_uc)

rm(full_11, full_12, full_13)

in_11_not_12 <- anti_join(store_id_11, store_id_12, by = "store_code_uc")
in_11_not_13 <- anti_join(store_id_11, store_id_13, by = "store_code_uc")
in_12_not_11 <- anti_join(store_id_12, store_id_11, by = "store_code_uc")
in_12_not_13 <- anti_join(store_id_12, store_id_13, by = "store_code_uc")
in_13_not_11 <- anti_join(store_id_13, store_id_11, by = "store_code_uc")
in_13_not_12 <- anti_join(store_id_13, store_id_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  anti_join(in_11_not_12, by = "store_code_uc") %>%
  anti_join(in_11_not_13, by = "store_code_uc") %>%
  anti_join(in_12_not_11, by = "store_code_uc") %>%
  anti_join(in_12_not_13, by = "store_code_uc") %>%
  anti_join(in_13_not_11, by = "store_code_uc") %>%
  anti_join(in_13_not_12, by = "store_code_uc")

full_11_12_13 <- full_11_12_13 %>%
  mutate(manuf_name = substr(full_11_12_13$brand_descr, 1, 3))

rm(full_11, full_12, full_13, in_11_not_12, in_11_not_13, in_12_not_11, in_12_not_13, in_13_not_11, in_13_not_12,
   store_id_11, store_id_12, store_id_13)
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_11_12_13 %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_11_12_13 %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create one vector with the store codes to remove because they switch retailer or parent codes.
```{r}
switchers <- unique(c(parent_switchers, retailer_switchers))
```

Using the `switchers` vector, filter out the store codes that switch retailer or parent codes.
```{r}
full_11_12_13 <- full_11_12_13 %>%
  filter(!store_code_uc %in% switchers)

rm(parent_switchers, retailer_switchers, switchers)
```

Use `mutate` to replace the missing `retailer_code` values with the `parent_code`.
```{r}
full_11_12_13 <- full_11_12_13 %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Create a tbl for each location of interest.
```{r}
nd_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'ND')

mn_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'MN')

mo_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'MO')

il_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'IL')
```

Save `.RData` files for each of the locations of interest as well as the `full_11_12_13` file.
```{r}
save(full_11_12_13, file = 'frozen_dinners_clean.RData')
save(nd_data, file = 'nd_frozen_dinners_clean.RData')
save(mn_data, file = 'mn_frozen_dinners_clean.RData')
save(mo_data, file = 'mo_frozen_dinners_clean.RData')
save(il_data, file = 'il_frozen_dinners_clean.RData')
```

Captain: Nestle
Validator: Conagra