---
title: "Minnesota Frozen Dinners Cleaning"
author: "Cameron Bale"
date: "August 13, 2018"
output: github_document
---

Install packages.
```{r eval =FALSE, include=FALSE}
#install.packages("tidyverse")
#install.packages("lubridate")
```

Load libraries.
```{r results='hide'}
library(tidyverse)
library(lubridate)
```

Read in the files from the frozen_dinners_entries.tgz for 2011.
```{r}
frozen_dinners_files <- untar("frozen_dinners_entries.tgz", list = TRUE)

#untar("frozen_dinners_entries.tgz")

move_11 <- tibble()

for (i in seq_along(frozen_dinners_files)) {
    
    if (substr(frozen_dinners_files[i], 22, 40) == "2011/Movement_Files") {
        
        temp_move_11 <- read_tsv(frozen_dinners_files[i])
        
        move_11 <- move_11 %>%
            
            bind_rows(temp_move_11)
        
        rm(temp_move_11)
    }
    
}

products <- read_tsv("nielsen_extracts/RMS/Master_Files/Latest/products.tsv", quote = "")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

rms_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/rms_versions_2011.tsv")

full_11 <- move_11 %>%
  left_join(stores_11, by ="store_code_uc") %>%
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO", "IL")) %>%
  left_join(rms_11, by = "upc") %>%
  left_join(products, by = c("upc", "upc_ver_uc"))

save(full_11, file = "full_11.RData")

rm(move_11, stores_11, rms_11, full_11)
```

Read in the files for 2012.
```{r}
move_12 <- tibble()

for (i in seq_along(frozen_dinners_files)) {
    
    if (substr(frozen_dinners_files[i], 22, 40) == "2012/Movement_Files") {
        
        temp_move_12 <- read_tsv(frozen_dinners_files[i])
        
        move_12 <- move_12 %>%
            
            bind_rows(temp_move_12)
        
        rm(temp_move_12)
    }
    
}

stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

rms_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/rms_versions_2012.tsv")

full_12 <- move_12 %>%
  left_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND","MN","MO","IL")) %>%
  left_join(rms_12, by = "upc") %>%
  left_join(products, by = c("upc", "upc_ver_uc"))

save(full_12, file = "full_12.RData")

rm(move_12, stores_12, rms_12, full_12)
```

Read in the files for 2013.
```{r}
move_13 <- tibble()

for (i in seq_along(frozen_dinners_files)) {
    
    if (substr(frozen_dinners_files[i], 22, 40) == "2013/Movement_Files") {
        
        temp_move_13 <- read_tsv(frozen_dinners_files[i])
        
        move_13 <- move_13 %>%
            
            bind_rows(temp_move_13)
        
        rm(temp_move_13)
    }
    
}

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", guess_max = 20000)

rms_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/rms_versions_2013.tsv")

full_13 <- move_13 %>%
  left_join(stores_13, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND","MN","MO","IL")) %>%
  left_join(rms_13, by = "upc") %>%
  left_join(products, by = c("upc", "upc_ver_uc"))

rm(move_13, stores_13, rms_13, products)
```

Combine all three years into one file, `full_data`. Change `week_end` variable to year-month-day format. Create
variable `sales` which is `units` * `price`. Create variable for manufacturer from the first 3 digits of the brand
description.
```{r}
load('full_11.RData')
load('full_12.RData')

full_data <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), 
         sales = units * price,
         manuf_name = substr(brand_descr, 1, 3))

rm(full_11, full_12, full_13)
```

Create `missing_stores` vector which contains the store codes that don't show up in all years in the data. First,
get each distinct combination of `store_code_uc` and `panel_year`, then summarize by counting the number of years
for each store, filter for the `store_code_uc` that have less than three years, and store those codes in the vector
`missing_stores`.
```{r}
missing_stores <- full_data %>%
  distinct(store_code_uc, panel_year) %>%
  group_by(store_code_uc) %>%
  summarize(n_years = n()) %>%
  filter(n_years < 3) %>%
  select(store_code_uc) %>%
  pull()
```

Create a vector that contains the `store_code_uc` codes that are assigned to multiple retailer codes. First, generate
unique conbinations of `store_code_uc` and `retailer_code`, then group by `store_code_uc` and count the number of
observations - this is the number of `retailer_code` values for the given `store_code_uc`. Then, filter for the 
`store_code_uc` that have more than one retailer code and pull them into a vector.
```{r}
retailer_switchers <- full_data %>%
  distinct(store_code_uc, retailer_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_rets = n()) %>%
  filter(n_rets > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Using a similar approach as the previous chunk explains, create a tbl that contains the `store_code_uc` that have
multiple `parent_code` values.
```{r}
parent_switchers <- full_data %>%
  distinct(store_code_uc, parent_code) %>%
  group_by(store_code_uc) %>%
  summarize(n_parent = n()) %>%
  filter(n_parent > 1) %>%
  select(store_code_uc) %>%
  pull()
```

Create one vector with the store codes to remove because they switch retailer or parent codes or they don't show up
in all the years in the data.
```{r}
remove_stores <- unique(c(parent_switchers, retailer_switchers, missing_stores))
```

Using the `remove_stores` vector, filter out the store codes that switch retailer or parent codes or don't show up
in all the years in the data.
```{r}
full_data <- full_data %>%
  filter(!store_code_uc %in% remove_stores)

rm(parent_switchers, retailer_switchers, remove_stores, missing_stores)
```

Use `mutate` to replace missing `retailer_code` values with the `parent_code`.
```{r}
full_data <- full_data %>%
  mutate(retailer_code = ifelse(is.na(retailer_code), parent_code, retailer_code))
```

Save the cleaned data and save files for each state. 
```{r}
save(full_data, file="frozen_dinners_clean.RData")

mn_data <- full_data %>% filter(fips_state_descr=="MN")
il_data <- full_data %>% filter(fips_state_descr=="IL")
mo_data <- full_data %>% filter(fips_state_descr=="MO")
nd_data <- full_data %>% filter(fips_state_descr=="ND")

save(mn_data, file="mn_frozen_dinners_clean.RData")
save(il_data, file="il_frozen_dinners_clean.RData")
save(mo_data, file="mo_frozen_dinners_clean.RData")
save(nd_data, file="nd_frozen_dinners_clean.RData")
```

Captain: Nestle
Validator: Conagra