---
title: "Initial Diff-in-Diff Analysis"
output: word_document
---

Install packages and load library.

```{r, results = 'hide'}
library(tidyverse)
library(lubridate)
library(brms)
```

Unzip the 'peanutbutter.tgz' file. Read in 2011 movement and store files, merge them based
on the store code, and filter for 'F' (food stores) and states North Dakota, Minnesota,
Missouri, and D.C.

```{r, results = 'hide'}
untar("peanutbutter.tgz", list = TRUE)

untar("peanutbutter.tgz")

move_11 <- read_tsv("nielsen_extracts/RMS/2011/Movement_Files/0506_2011/1421_2011.tsv")

stores_11 <- read_tsv("nielsen_extracts/RMS/2011/Annual_Files/stores_2011.tsv")

full_11 <- move_11 %>%
  inner_join(stores_11, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_11, file = 'pb_full_11.RData')

rm(move_11, stores_11, full_11)
```

Perform the previous step for 2012 and 2013.

```{r, results = 'hide'}
move_12 <- read_tsv("nielsen_extracts/RMS/2012/Movement_Files/0506_2012/1421_2012.tsv")
stores_12 <- read_tsv("nielsen_extracts/RMS/2012/Annual_Files/stores_2012.tsv")

full_12 <- move_12 %>%
  inner_join(stores_12, by ="store_code_uc") %>% 
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO" ,"DC"))

save(full_12, file = 'pb_full_12.RData')

rm(move_12, stores_12, full_12)

move_13 <- read_tsv("nielsen_extracts/RMS/2013/Movement_Files/0506_2013/1421_2013.tsv")

stores_13 <- read_tsv("nielsen_extracts/RMS/2013/Annual_Files/stores_2013.tsv", 
                      col_types = list(col_double(), col_double(),
                      col_double(), col_double(), col_character(),
                      col_character(), col_double(), col_character(), 
                      col_double(), col_character(), col_double(), col_character()))

full_13 <- move_13 %>%
  inner_join(stores_13, by = "store_code_uc") %>%
  filter(channel_code == "F" & fips_state_descr %in% c("ND", "MN", "MO", "DC"))

save(full_13, file = 'pb_full_13.RData')

rm(move_13, stores_13)
```

Bind full_11,12,13 into one tbl, 'full_11_12_13'. Overwrite the variable week_end to be in
year-month-date format. Create sales variable, which is the number of units sold multiplied
by the price.

```{r, results = 'hide'}
load('pb_full_11.RData')
load('pb_full_12.RData')

full_11_12_13 <- full_11 %>%
  bind_rows(full_12) %>%
  bind_rows(full_13) %>%
  mutate(week_end = ymd(week_end), sales = units * price)

rm(full_11, full_12, full_13)
```

Read in products master file.

```{r, results = 'hide'}
products <- read_tsv('products.tsv', quote = "")
```

Merge products file and full_11_12_13.

```{r, results = 'hide'}
full_11_12_13 <- full_11_12_13 %>%
  left_join(products, by = 'upc')

rm(products)
```

Filter the full dataset for data pertaining to the retailers in DC. Display the retailer
codes in DC.

```{r}
dc_data <- full_11_12_13 %>%
  filter(fips_state_descr == 'DC')

distinct(dc_data, retailer_code)
```

Using dc_data, create variable manuf_name, which is the first three characters of the brand
description. Filter for observations for brands owned by captain (unilever), validator, 
(smuckers), and private label (CTL). Create variable actual_manuf, which denotes the 
manufacturing company for their brands. Summarize by aggregating sales for each manufacturer
in each week in each retailer. Create dummy variable 'treat' which is 1 for observations
for our supervalue retailer 842, and 0 otherwise. Create dummy variable post, which is 1 for
observations after category captainship implementation, and 0 for observations before.

```{r}
dc_data <- dc_data %>%
  mutate(manuf_name = substr(dc_data$brand_descr, 1, 3)) %>%
  filter(manuf_name %in% c('SKI', "JIF", "SMU", "SIM", "SAN", "ADA", "CTL")) %>%
  mutate(actual_manuf = if_else(manuf_name == 'CTL', 'CTL',
                        if_else(manuf_name == 'SKI', 'UNI', 'SMU'))) %>%
  group_by(retailer_code, week_end, actual_manuf) %>%
  summarize(sales = sum(sales)) %>%
  mutate(treat = if_else(retailer_code == 842, 1, 0),
         post = if_else(week_end > "2012-01-02", 1, 0))
```

Loop creates a graph comparing sales trends for retailer 842 and the chosen control, and
performs a basic diff-in-diff regression. Returns graph and regression results. Do this for
every retail code that could serve as a control in DC.

```{r}
dc_rets <- unique(dc_data$retailer_code)[-4]
manufs <- c('UNI', 'SMU', 'CTL')

for (i in seq_along(dc_rets)) {
  for (j in seq_along(manufs)) {  
    did_data <- dc_data %>%
    filter(retailer_code %in% c(842, dc_rets[i]) & actual_manuf == manufs[j])
  
    pre_cc <- did_data %>%
        filter(week_end <= as.Date("2012-07-16"))
  
    post_cc <- did_data %>%
        filter(week_end > as.Date("2012-07-16"))

    plot <- ggplot(did_data, aes(week_end, sales, col = factor(retailer_code))) + 
      geom_line() +
      geom_smooth(aes(week_end, sales), data = pre_cc, method = 'lm', se = FALSE) +
      geom_smooth(aes(week_end, sales), data = post_cc, method = 'lm', se = FALSE) +
      geom_vline(xintercept = as.numeric(as.Date("2012-07-16"))) +
      ggtitle(paste('Sales for', manufs[j], 'in retail code', dc_rets[i]))
    
    did_reg <- brm(sales ~ treat + post + treat * post, data = did_data)
    
    print(paste('Diff-in-Diff Regression Results for manufacturer', manufs[j],
                'for Retailer 842 with Retailer', dc_rets[i], 
                'Functioning as a Control'))
    
    print(plot)
    
    print(did_reg)

  }
}
```













